### 2021-10-21 methods.tex
some edits

\subsection*{\sffamily \large The implicit solvent model}

The implicit solvent model can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_X$ in Figure XX), and the Poisson equation in the solute region ($\Omega_Y$ in Figure XX). These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous. 
%
\begin{align}\label{eq:pbe}
\nabla^2\phi_1(\mathbf{x}) &= \frac{1}{\epsilon}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
\left(\nabla^2 - \kappa^2\right)\phi_2 &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
\phi_1 = \phi_2 &\quad \epsilon_1\frac{\partial\phi_1}{\partial\mathbf{n}} = \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}} \quad \mathbf{x}\in \Gamma. 
\end{align}
%
where $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively, $\kappa$ is the inverse of the Debye length, related with the salt concentration, and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.

The electrostatic potential in $\Omega_1$ can be further decomposed into singular and regular components as $\phi_1 = \phi_c + \phi_R$, where $\phi_c$ is the solution to
%
\begin{align}\label{eq:phic}
\nabla^2\phi_c(\mathbf{x}) &= \frac{1}{\epsilon_1}\sum_{k=1}^{N_q}q_k\delta(\mathbf{x},\mathbf{x}_k) \quad \mathbf{x}\in\Omega_1\cup\Omega_2\nonumber\\
\phi_c(\mathbf{x})&=0 \quad \text{ as } |\mathbf{x}|\to\infty
\end{align}

Physically, $\phi_c$ can be interpreted as the Coulomb-type potential from the point charges, whereas $\phi_R$, also known as reaction potential, is originated by the polarization of the solvent. 
Usually, $\epsilon_1$ is considered a constant value, yielding an analytical expression for $\phi_c$, however, this is not the general case.

There are regularized versions of Equation \eqref{eq:pbe} [HolstETal2008,GengZhao2020] which are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods.
However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permitivitties.

A common quantity of interest in implicit solvent models is the solvation free energy, which the change in Gibbs free energy as the molecule moves from vacuum into the solvent. Considering the charge distribution $\rho$ consists of point charges, this can be calculated as
%
\begin{equation}\label{eq:dG}
\Delta G_{solv} = \frac{1}{2}\int_{\Omega_1} \rho(\mathbf{x})\phi_{r}(\mathbf{x}) = \frac{1}{2}\sum_{k=1}^{N_q} q_k\phi_r(\mathbf{x_k})
\end{equation}

\subsection*{\sffamily \large Numerical solution of the Poisson-Boltzmann equation}

\subsection*{\sffamily \large BEM-BEM coupling}
\begin{itemize}
    \item Direct formulation
\end{itemize}

\subsection*{\sffamily \large FEM-BEM coupling}

\begin{itemize}
    \item Description with constant and variable permittivity 
    \item Standard BEM-BEM and FEM-BEM coupling approach
    \item Hybrid FEM-BEM coupling
\end{itemize}

### 2021-10-21 results.tex
some edits

\section*{\sffamily \Large Results with constant permitivitty}

\subsection*{\sffamily \large Convergence of a spherical cavity}
\begin{itemize}
    \item Show convergence to analytical solution for
    \begin{itemize}
        \item BEM-BEM
        \item Standard FEM-BEM
        \item Hybrid FEM-BEM
    \end{itemize}
\end{itemize}

\subsection*{\sffamily \large Performance for a molecular geometry}
\begin{itemize}
    \item Use arginine 
    \item Compare computer time and iterations for FEM-BEM with standard and hybrid approaches, without preconditioner. 
    \item Show performance of hybrid and standard methods with preconditioner.
    \item Show scaling for larger molecules for hybrid and standard (or the best-performing one)
\end{itemize}

\section*{\sffamily \Large Results with variable permittivity}

\subsection*{\sffamily \large Validation for a spherical cavity}

Compare solvation energy results of hybrid and standard FEM-BEM with APBS

\subsection*{\sffamily \large Convergence and performance for a molecular geometry}
\begin{itemize}
    \item Mesh refinement study using hybrid and standard FEM-BEM and APBS on arginine or small protein. Check if they are converging to same result.
    \item Compare timings for equivalent error
\end{itemize}

\subsection*{\sffamily \large Performance analysis for larger structures}

For a given mesh refinement, show solvation energy and timings using preconditioned hybrid FEM-BEM up to the biggest problem we can do on whatever computer we're using.

### 2022-03-02 results.tex
added text to results

@@
+This section presents verification and performance results of the standard and hybrid FEM-BEM coupling schemes, for molecules modeled as cavities with constant and varying permittivity.
+When the permittivity inside the molecule was constant, we tested convergence against the available analytical expression of the solvation energy of a sphere [Kirkwood1934], and then compared a more realistic geometry (arginine) with a purely BEM implementation.
+On the other hand, we considered a Gaussian-varying permittivity [Alexov and earlier] inside arginine, and used APBS [Baker2001] to verify.
+The final result of this section shows the scaling of the standard and hybrid FEM-BEM coupling, as the molecule size grows.
+
+All runs were done on XX computer with YY specifications.
+
 \section*{\sffamily \Large Results with constant permitivitty}
 
+In implicit-solvent models, the molecule is usually considered as a region with constant permittivity, in this case, with $\epsilon_1=4$.
+In the solvent region, we used the permittivity of water ($\epsilon_2$=80) and an inverse of the Debye length of $\kappa=0.125$ \AA$^{-1}$.
+
 \subsection*{\sffamily \large Convergence of a spherical cavity}
-\begin{itemize}
-    \item Show convergence to analytical solution for
-    \begin{itemize}
-        \item BEM-BEM
-        \item Standard FEM-BEM
-        \item Hybrid FEM-BEM
-    \end{itemize}
-\end{itemize}
 
-\subsection*{\sffamily \large Performance for a molecular geometry}
-\begin{itemize}
-    \item Use arginine 
-    \item Compare computer time and iterations for FEM-BEM with standard and hybrid approaches, without preconditioner. 
-    \item Show performance of hybrid and standard methods with preconditioner.
-    \item Show scaling for larger molecules for hybrid and standard (or the best-performing one)
-\end{itemize}
+The Kirkwood sphere [Kirkwood1934] is a standard benchmarck for the Poisson-Boltzmann equation in molecular electrostatics. 
+Here, we considered a spherical cavity with radius $R=X$ \AA, with three charges ($q_1$=a, $q_2$=b, and $q_3$=c) placed at $\mathbf{x}_1=(x_1,y_1,z_1)$, $\mathbf{x}_2=(x_2,y_2,z_2)$, and $\mathbf{x}_3=(x_3,y_3,z_3)$.
+Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}=XX$ kcal/mol).
+In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
+For the hybrid FEM-BEM coupling approach, we used $\tau$=XX.
+
+The error in Figure \ref{fig:error_sphere} decays linearly with the surface area, which agrees with the expected convergence for P1 elements, indicating a correct implementation of the numerical scheme.
+We can see that the purely BEM implementation outperforms (or not?) FEM-BEM coupling in terms of accuracy for equivalent meshes, and also that the hybrid approach does not (or does?) influence accuracy.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\linewidth]{BEM_BEM_Sphere_const_coeff_error.png}
+  \includegraphics[width=0.45\linewidth]{FEM_BEM_Sphere_const_coeff_error.png}
+  \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_error.png}
+  \caption{Error for the Kirkwood sphere. Can we put all these in a single plot and in log-log? No need for percentage, I think.}
+  \label{fig:error_sphere}
+\end{figure}
+
+%\begin{itemize}
+%    \item Show convergence to analytical solution for
+%    \begin{itemize}
+%        \item BEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.32\textwidth}
+%  \includegraphics[width=\linewidth]{BEM_BEM_Sphere_const_coeff_error.png}
+%  \caption{Error}
+%\endminipage\hfill
+%\minipage{0.32\textwidth}
+%  \includegraphics[width=\linewidth]{BEM_BEM_Sphere_const_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.32\textwidth}%
+%  \includegraphics[width=\linewidth]{BEM_BEM_Sphere_const_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%        \item Standard FEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.32\textwidth}
+%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_const_coeff_error.png}
+%  \caption{Error}
+%\endminipage\hfill
+%\minipage{0.32\textwidth}
+%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_const_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.32\textwidth}%
+%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_const_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%        \item Hybrid FEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.32\textwidth}
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_error.png}
+%  \caption{Error}
+%\endminipage\hfill
+%\minipage{0.32\textwidth}
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.32\textwidth}%
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%    \end{itemize}
+%\end{itemize}
+
+\subsection*{\sffamily \large Performance for arginine}
+
+As a more realistic test, we assessed the performance of the standard and hybrid FEM-BEM coupling techniques against a purely BEM implementation for arginine [cite arg]. 
+We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper [Rocchia].
+These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], invoking \texttt{tetgen} with the string \texttt{abcd}.
+For the hybrid FEM-BEM coupling approach, we used $\tau$=XX.
+
+Figure \ref{fig:arg_constant_time} compares the time-to-solution with the three schemes, and shows that using only BEM outperforms both coupled FEM-BEM approaches.
+Even though hybrid FEM-BEM is slower than standard FEM-BEM in Figure \ref{fig:arg_constant_time}, the iteration count in Figure \ref{fig:arg_constant_iter} shows that hybrid FEM-BEM needs less iterations (can we compare them?).
+This behavior is promising going towards larger problems, specially since the hybrid approach allows for more flexibility in the choice of preconditioner.
+We can also see that accuracy is not affected (or is?) by considering a FEM region inside the molecule (need fig to check this).
+
+Do we really need to compute the vacuum case numerically? We should be able to do it analytically, right?
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\linewidth]{BEM_BEM_Arginine_const_coeff_time.png}
+\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_const_coeff_time.png}
+\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_time.png}
+\caption{Time-to-solution for arginine with a constant permittivity.
+(1) fix title, (2) can we put them in a single plot, (3) maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
+\label{fig:arg_contant_time}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\linewidth]{BEM_BEM_Arginine_const_coeff_iter.png}
+\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_const_coeff_iter.png}
+\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_iter.png}
+\caption{Iteration count for arginine with a constant permittivity.
+(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations?
+maybe we should present the total count?}
+\label{fig:arg_contant_iter}
+\end{figure}
+
+%\begin{itemize}
+%    \item Use arginine or a small protein (1PGB?)
+%    \begin{itemize}
+%        \item BEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{BEM_BEM_Arginine_const_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.45\textwidth}%
+%  \includegraphics[width=\linewidth]{BEM_BEM_Arginine_const_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%        \item Standard FEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_const_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.45\textwidth}%
+%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_const_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%        \item Hybrid FEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.45\textwidth}%
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%    \end{itemize}
+%    \item Compare computer time and iterations for FEM-BEM with standard and hybrid approaches, without preconditioner. Choose hybrid.
+%    \item Show performance of hybrid method with preconditioner.
+%\end{itemize}
 
@@
 
-\subsection*{\sffamily \large Validation for a spherical cavity}
+In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
+A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom [earlier papers], which has shown enhanced accuracy in some applications, like binding energy calculations (check) [Alexov].
+In this setting, we define a density function $\rho$ as
+%
+\begin{equation}
+\rho
+\end{equation}
+%
+where the sum is over the atoms of the solute, and we used $\sigma$=1. Then, we can compute the permittivity as
+%
+\begin{equation}
+\epsilon
+\end{equation}
+%
 
-Compare solvation energy results of hybrid and standard FEM-BEM with APBS
+We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS for comparison. 
+It is important to note that in this case, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum has to be computed numerically.
+For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, however, the solvent permittivity was set to $\epsilon$=2. 
+Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff [Alexov]. 
+We did not consider a cutoff in our calculations, but this does not affect our validation exercise.
 
-\subsection*{\sffamily \large Convergence and performance for a molecular geometry}
-\begin{itemize}
-    \item Mesh refinement study using hybrid and standard FEM-BEM and APBS on arginine or small protein. Check if they are converging to same result.
-    \item Compare timings for equivalent error
-\end{itemize}
+\subsection*{\sffamily \large Convergence and performance for arginine}
+
+Table \ref{table:} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approaches. We can see that they are both converging to equivalent values of solvation energy.
+
+\begin{table}
+\centering
+\begin{tabular}{c|c|c}
+&Mesh size & $\Delta G_{solv}$\\
+&\AA       &  kcal/mol \\
+\hline
+\multirow{3}{*}{APBS}& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
+&0.26$\times$0.26$\times$0.26 & -32.3375\\ 
+&0.17$\times$0.17$\times$0.17 & -32.3413\\ 
+\hline
+&Mesh dens. & \\
+&vert/\AA$^2$ & \\
+\hline
+%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
+    & 2 & -36.239\\
+Standard    & 4  & -33.129 \\
+FEM-BEM    & 8  & -32.674 \\
+    & 12 & -32.648 \\
+    & 16 & -32.293 \\
+\hline
+%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
+    & 2 & -29.554\\
+Hybrid    & 4  & -33.766 \\
+FEM-BEM    & 8  & -32.586 \\
+    & 12 & -32.891 \\
+    & 16 & -32.528 \\
+\hline
+\end{tabular}
+\caption{}
+\end{table}
+%
+%    \begin{itemize}
+%        \item Standard FEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_varying_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.45\textwidth}%
+%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_varying_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%        \item Hybrid FEM-BEM
+%\begin{figure}[!htb]
+%\minipage{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_varying_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.45\textwidth}%
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_varying_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+
+\begin{figure}[!htb]
+\minipage{0.45\textwidth}
+  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_iter.png}
+  \caption{Iterations}
+\endminipage\hfill
+\minipage{0.45\textwidth}%
+  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_time.png}
+  \caption{Computational time}
+\endminipage
+\end{figure}
+\begin{figure}[!htb]
+\minipage{0.45\textwidth}
+  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
+  \caption{Iterations}
+\endminipage\hfill
+\minipage{0.45\textwidth}%
+  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
+  \caption{Computational time}
+\endminipage
+\end{figure}
 

### 2022-03-02 results.tex
added text in results

@@
 We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS for comparison. 
-It is important to note that in this case, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum has to be computed numerically.
+As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
 For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, however, the solvent permittivity was set to $\epsilon$=2. 
@@
 
-Table \ref{table:} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approaches. We can see that they are both converging to equivalent values of solvation energy.
+Table \ref{table:arg_variable} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approaches.
+We can see that they are both converging to equivalent values of solvation energy, where the finest meshes agree up to the third significant figure.
+
+Figure \ref{fig:arg_variable} contains performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states. 
+Similar to the case with constant permittivity, although the hybrid approach requires less iterations (are we counting them appropriately?
+meaning there are external and internal iterations), the total time to solution is less for the standard approach.
+This means that each iteration of hybrid FEM-BEM is slower than the standard counterpart.
 
@@
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
-    & 2 & -29.554\\
-Hybrid    & 4  & -33.766 \\
-FEM-BEM    & 8  & -32.586 \\
-    & 12 & -32.891 \\
-    & 16 & -32.528 \\
+    & 2 & -35.333\\
+Hybrid    & 4  & -33.079 \\
+FEM-BEM    & 8  & -32.660 \\
+    & 12 & -32.587 \\
+    & 16 & -32.359 \\
 \hline
 \end{tabular}
-\caption{}
+\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS.}
+\label{table:arg_variable}
 \end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_varying_coeff_iter.png}
+\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_varying_coeff_time.png}
+\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
+\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
+\caption{Time-to-solution and iteration count to compute the solvation energy of arginine with a variable permittivity, using standard and hybrid FEM-BEM coupling. Can we make this only two plots?}
+\label{fig:arg_variable}
+\end{figure}
+
 %
@@
 
-\begin{figure}[!htb]
-\minipage{0.45\textwidth}
-  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_iter.png}
-  \caption{Iterations}
-\endminipage\hfill
-\minipage{0.45\textwidth}%
-  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_time.png}
-  \caption{Computational time}
-\endminipage
-\end{figure}
-\begin{figure}[!htb]
-\minipage{0.45\textwidth}
-  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
-  \caption{Iterations}
-\endminipage\hfill
-\minipage{0.45\textwidth}%
-  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
-  \caption{Computational time}
-\endminipage
-\end{figure}
+%\begin{figure}[!htb]
+%\minipage{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.45\textwidth}%
+%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
+%\begin{figure}[!htb]
+%\minipage{0.45\textwidth}
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
+%  \caption{Iterations}
+%\endminipage\hfill
+%\minipage{0.45\textwidth}%
+%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
+%  \caption{Computational time}
+%\endminipage
+%\end{figure}
 
@@
 
-For a given mesh refinement, show solvation energy and timings using preconditioned hybrid FEM-BEM up to the biggest problem we can do on whatever computer we're using.
+So far, in all the small structures that we have tested, the standard approach has been more efficient than the hybrid one.
+However, the fact that there are better preconditioning strategies for the hybrid approach indicates that it may become faster for larger test cases, where conditioning of the linear system is usually more important.
+In this section, we compare both approaches for larger structures.

### 2022-03-04 main.tex
Numerical methods - Update
I filled the gaps and put the plots in one as requested.

% Modified for use with JCC - Madhusudan Singh Copyright (C) (2012). All rights reserved.
\documentclass[12pt]{article}

\setlength{\oddsidemargin}{0in}  %left margin position, reference is one inch
\setlength{\textwidth}{6.5in}    %width of text=8.5-1in-1in for margin
\setlength{\topmargin}{-0.5in}    %reference is at 1.5in, -.5in gives a start of about 1in from top
\setlength{\textheight}{9in}     %length of text=11in-1in-1in (top and bot. marg.) 
\newenvironment{wileykeywords}{\textsf{Keywords:}\hspace{\stretch{1}}}{\hspace{\stretch{1}}\rule{1ex}{1ex}}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}% Include figure files
%\usepackage{caption}
\usepackage{color}% Include colors for document elements
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[numbers,super,comma,sort&compress]{natbib}
\usepackage{multirow}
%\usepackage[nolists, nomarkers, figuresfirst]{endfloat}

\definecolor{background-color}{gray}{0.98}

\title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
\author{Author A\thanks{Department of Biology, University 1, ...}, Author B\thanks{Department of Chemistry, University 2, ...}, Author C \thanks{Department of Physics, University 3, ...} Author D\thanks{Department of Mathematics, University College London, ...}}

\begin{document}

\maketitle

\begin{abstract}
Abstract
\end{abstract}

\begin{wileykeywords}
Finite element method, Boundary element method, Poisson-Boltzmann, Implicit solvent model, Electrostatics.
\end{wileykeywords}

\clearpage

%*****************Graphical Table of Contents******************** THIS IS MANDATORY *******************

\begin{figure}[h]
\centering
\colorbox{background-color}{
\fbox{
\begin{minipage}{1.0\textwidth}
\includegraphics[width=50mm,height=50mm]{adaptive_mesh_fig.pdf} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
%\includegraphics[width=110mm,height=20mm]{cc.eps}
\\
(75 words.) Images for the graphical Table of Contents should capture the essence of a paper, displaying a figure, plot, or scheme that is central to the theme of the manuscript. The text of the graphical Table of Contents is meant for the non-specialist and should ideally contain no obscure jargon or mathematical symbols / equations, but should attempt to convey the gist of the paper in everyday terms, while remaining consistent with accepted standards of scientific literature.
\end{minipage}
}}
\end{figure}

% makes references listed with 1., 2., etc.  
  \makeatletter
  \renewcommand\@biblabel[1]{#1.}
  \makeatother

\bibliographystyle{apsrev}

\renewcommand{\baselinestretch}{1.5}
\normalsize

\clearpage

\section*{\sffamily \Large INTRODUCTION} % Not needed for rapid communications

\input{intro}

% The opening sentence of the manuscript should summarize the reasons for the undertaking of the work and the main conclusions that can be drawn.

%((Place Introduction here))

%((Main text paragraphs should be 12 point font, double-spaced. Reviews are comprehensive survey of recent progress in a topic of broad interest in quantum chemistry, providing the readership with an appreciation of the importance of the work, a summary of recent developments, and a guide to the relevant literature. Perspective are short discussions of an important emerging topics in quantum chemistry, usually focused on no more than a few recently published papers, and including the authors' vision for the future of the topics, identifying important problems that should be addressed next. Perspective should be limited to 3000 words, 4 display items (figures and/or tables), and 30 references.))

%((Full Papers are comprehensive reports of important recent advances in the development of basic theory, quantum mechanical computational methodologies and their relevant applications that provide significant insight to problems of broad interest in chemistry, physics, biology, and materials science. The opening sentence of the manuscript should summarize the reasons for the undertaking of the work and the main conclusions that can be drawn. The main text should be contain sections with brief subheadings, a summary of the major conclusions of the paper, and a Method section containing sufficient detail to reproduce the work. Main text paragraphs should be 12 point font, double-spaced.))

%((Rapid communications should be limited to 1500 words, 3 display items (figure and/or tables), 20 references. Main text paragraphs should be 12 point font, double-spaced. There are NO headings in the main text.))

\section*{\sffamily \Large METHODOLOGY}
\input{methods}

%((Place Computational Methods here. Not needed for review articles))

%((Computational results should be prepared following the IUPAC guidelines (See Journal of Computational Chemistry, 20: 1587-1590 and 20:1591-1592). In particular, it is required that the level of theory employed is appropriate to the problem at hand, and that the sufficient details about methodology are provided to allow the work to be reproduced.)

%((In full papers, this section appears immediately after the introduction. In Rapid Communications, this section appears just before the Acknowledgments.))

\section*{\sffamily \Large RESULTS}
\input{results}
%((Place Results here. Not needed for review articles.))

\section*{\sffamily \Large First-order heading}

%((Equations should be inserted using standard LaTeX equation and eqnarray environments, not as graphics, and should be set in the main text))
%Equation											(1)
%((References should be superscripted and appear after punctuation.1,2 Please define all acronyms at their first usage except IR, UV, NMR, and DNA or similar commonly understood terms.))

\subsection*{\sffamily \large Second-order heading}

\subsubsection*{\sffamily \normalsize Third-order heading}

{\sffamily \small Fourth-order heading}\\

\section*{\sffamily \Large DISCUSSION}

%((Place Discussion here. Not needed for review articles.))

\section*{\sffamily \Large CONCLUSIONS}

%((Place Conclusions here.))

\subsection*{\sffamily \large ACKNOWLEDGMENTS}

%((Place Acknowledgments here))

%((Additional Supporting Information may be found in the online version of this article.))

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BIBLIOGRAPHY

%\bibliography{bibtexrefs}   % Produces the bibliography via BibTeX.

\begin{thebibliography}{99}

\bibitem{Coulson}
Coulson, C. A., Rev. Mod. Phys., \textbf{1960}, 32,170-177.
\bibitem{Malrieu}
Malrieu, J.-P., J. Mol. Struct., \textbf{1998}, 424, 1-2,83-91.
\bibitem{Shaik}
Shaik, S., New. J. Chem., \textbf{2007}, 31,2015-2028.
\bibitem{Hoffmann}
Hoffman, R., Schleyer, P. v. R., Schaefer III, H. F., \textbf{2008}, 47, 7164-7167.
\bibitem{Perdew}
Perdew, J. P., Ruzsinszky, A., Constantin, L., Sun, J., Csonka, G., J. Chem. Theory Comput., \textbf{2009}, 5, 902-908.
\bibitem{Koros}
Koros, W. J.; Chern, R. T. In Handbook of Separation Process Technology; Rousseau, E. D.; Russell, B., Eds.; Wiley: New York, \textbf{1987}; Vol. 2, Chapter 20, pp 34-45.
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE CAPTIONS

%%%%% FIGURE ---- cc.eps
\begin{figure}
\caption{\label{cc} Place Figure 1 caption here. In the case of reproduced figures in review articles, you must obtain the publisher's permission and state a suitable notice here along with a citation.}
\end{figure}

\begin{figure}
\caption{\label{fig2} Place Figure 2 caption here. Figures should be uploaded as individual files, preferably .tif or .eps files, at high enough resolution (600 to 1200 dpi) to ensure clarity. Please see the author’s guide for more details and specifications. For high quality illustrations, we highly recommend the use of the TikZ package.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE FILES

\clearpage

%\vspace*{0.1in}   %%% FIGURE 1
%\begin{center}
%\includegraphics[width=0.2\columnwidth,keepaspectratio=true]{cc.eps}
%\end{center}
\vspace{0.25in}
\hspace*{3in}
{\Large
\begin{minipage}[t]{3in}
\baselineskip = .5\baselineskip
Figure 1 \\
Author A, Author B, Author C, Author D \\
J.\ Comput.\ Chem.
\end{minipage}
}

\clearpage

\begin{table}
\begin{tabular}{|c|c|c|c|}\hline
\textbf{Quantity} & \textbf{Calculated} & \textbf{Observed} & \textbf{Error} \\ \hline
  Density & 5.3 & 6.3 & Within limits \\ \hline
  Optical magnification & 8.3 & 90.9 & Utterly unacceptable\! \\ \hline
\end{tabular}
\caption{\label{tbl1} Place table caption here.}
\end{table}

\end{document}

### 2022-03-04 results.tex
Numerical methods - Update
I filled the gaps and put the plots in one as requested.

@@
 The Kirkwood sphere [Kirkwood1934] is a standard benchmarck for the Poisson-Boltzmann equation in molecular electrostatics. 
-Here, we considered a spherical cavity with radius $R=X$ \AA, with three charges ($q_1$=a, $q_2$=b, and $q_3$=c) placed at $\mathbf{x}_1=(x_1,y_1,z_1)$, $\mathbf{x}_2=(x_2,y_2,z_2)$, and $\mathbf{x}_3=(x_3,y_3,z_3)$.
-Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}=XX$ kcal/mol).
+Here, we considered a spherical cavity with radius $R=2$ \AA, with three charges ($q_1$=1, $q_2$=1, and $q_3$=0.75) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
+Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.33752347454015$ kcal/mol).
 In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
-For the hybrid FEM-BEM coupling approach, we used $\tau$=XX.
+For the hybrid FEM-BEM coupling approach, we used $\tau$=10.
 
@@
   \centering
-  \includegraphics[width=0.45\linewidth]{BEM_BEM_Sphere_const_coeff_error.png}
-  \includegraphics[width=0.45\linewidth]{FEM_BEM_Sphere_const_coeff_error.png}
-  \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_error.png}
-  \caption{Error for the Kirkwood sphere. Can we put all these in a single plot and in log-log? No need for percentage, I think.}
+  \includegraphics[width=0.6\linewidth]{Sphere_const_coeff_error.png}
+%   \includegraphics[width=0.45\linewidth]{Sphere_const_coeff_iter.png}
+%   \includegraphics[width=0.45\linewidth]{Sphere_const_coeff_time.png}
+  \caption{Error for the Kirkwood sphere.}
   \label{fig:error_sphere}
@@
 These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], invoking \texttt{tetgen} with the string \texttt{abcd}.
-For the hybrid FEM-BEM coupling approach, we used $\tau$=XX.
+For the hybrid FEM-BEM coupling approach, we used $\tau$=10.
 
@@
 \centering
-\includegraphics[width=0.45\linewidth]{BEM_BEM_Arginine_const_coeff_time.png}
-\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_const_coeff_time.png}
-\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_time.png}
-\caption{Time-to-solution for arginine with a constant permittivity.
-(1) fix title, (2) can we put them in a single plot, (3) maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
+%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
+%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
+  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_time.png}
+\caption{Time-to-solution for arginine with a constant permittivity. %(1) fix title, (2) can we put them in a single plot, (3) 
+maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
 \label{fig:arg_contant_time}
@@
 \centering
-\includegraphics[width=0.45\linewidth]{BEM_BEM_Arginine_const_coeff_iter.png}
-\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_const_coeff_iter.png}
-\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_iter.png}
+%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
+  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_iter.png}
+%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
 \caption{Iteration count for arginine with a constant permittivity.
-(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations?
-maybe we should present the total count?}
+%(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations?
+maybe we should present the total count?
+}
 \label{fig:arg_contant_iter}
@@
 A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom [earlier papers], which has shown enhanced accuracy in some applications, like binding energy calculations (check) [Alexov].
-In this setting, we define a density function $\rho$ as
+In this setting, we define a density function $\rho$ depending on position $r$ as
 %
 \begin{equation}
-\rho
+\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|r-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right)
 \end{equation}
 %
-where the sum is over the atoms of the solute, and we used $\sigma$=1. Then, we can compute the permittivity as
+where the product is over the atoms of the solute, $R_i$ is the vdW
+radius of atom i and we used $\sigma$=1. Then, we can compute the permittivity as
 %
 \begin{equation}
-\epsilon
+\epsilon := \left(1-\rho \right) \epsilon_1 + \rho\epsilon_2
 \end{equation}

### 2022-03-04 results.tex
Update of plots
I have added updated plots and removed the one that we are not using since they would create confusion on the repository.

@@
 \centering
-\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_varying_coeff_iter.png}
-\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_varying_coeff_time.png}
-\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
-\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
-\caption{Time-to-solution and iteration count to compute the solvation energy of arginine with a variable permittivity, using standard and hybrid FEM-BEM coupling. Can we make this only two plots?}
+\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
+\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
+% \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
+% \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
+\caption{Time-to-solution and iteration count to compute the solvation energy of arginine with a variable permittivity, using standard and hybrid FEM-BEM coupling. %Can we make this only two plots?
+}
 \label{fig:arg_variable}

### 2022-03-04 results.tex
added notes after meeting Michal

@@
 
-Do we really need to compute the vacuum case numerically? We should be able to do it analytically, right?
+\begin{itemize}
+\item Do we really need to compute the vacuum case numerically? We should be able to do it analytically, right?
+\item Run BEM-BEM with the non regularized version.
+\end{itemize}
 
@@
 \centering
-%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
+   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
@@
 We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS for comparison. 
+We chose APBS because it provides an easy interface to control de dielectric map.....
 As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
@@
 &0.17$\times$0.17$\times$0.17 & -32.3413\\ 
+& FINER & If possible\\ 
 \hline
@@
 FEM-BEM    & 8  & -32.674 \\
-    & 12 & -32.648 \\
     & 16 & -32.293 \\
@@
 FEM-BEM    & 8  & -32.660 \\
-    & 12 & -32.587 \\
     & 16 & -32.359 \\
@@
 \end{tabular}
-\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS.}
+\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS. Add performance result?}
 \label{table:arg_variable}

### 2022-03-09 methods.tex
minor edit to methods
added BEM-BEM coupling to methods

@@
 \subsection*{\sffamily \large BEM-BEM coupling}
-\begin{itemize}
-    \item Direct formulation
-\end{itemize}
+
+The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson-Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,CooperForsythClementiBarba2016} and more recently, with Bempp-cl.~\cite{SearchCooperWout2022}
+
+There are several possible boundary integral formulations of Equation \eqref{eq:pbe}.~\cite{SearchCooperWout2022} The simplest form was presented by Yoon and Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, which only couples the potential at the interface, and not its derivative.
+Applying Green's second identity to Equation \eqref{eq:pbe} we get 
+%
+\begin{align} \label{eq:volume_potential}
+\phi_{1}+ K_{L}^{\Omega_1}(\phi_{1,\Gamma}) -  V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Omega_1} - \mathbf{r}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
+\phi_{2} - K_{Y}^{\Omega_2}(\phi_{2,\Gamma}) + V_{Y}^{\Omega_2} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0 \quad \text{on $\Omega_2$,}
+\end{align}
+%
+where $\phi_{1,\Gamma} = \phi_1(\mathbf{r}_\Gamma)$ and $\phi_{2,\Gamma} = \phi_2(\mathbf{r}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+$K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
+%
+\begin{align}\label{eq:single_double}
+V^\Omega_{L,Y}(\varphi) = \oint_\Gamma g_{L,Y}(\mathbf{r}_\Omega,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}'\nonumber\\
+K^\Omega_{L,Y}(\varphi) = \oint_\Gamma \frac{\partial g_{L,Y}}{\partial\mathbf{n}'}(\mathbf{r}_\Omega,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}',\nonumber\\
+\end{align}
+%
+where $\varphi(\mathbf{r})$ can be any distribution over $\Gamma$, and 
+%
+\begin{align}\label{eq:green_func}
+g_L(\mathbf{r},\mathbf{r}')=\frac{1}{4\pi|\mathbf{r}-\mathbf{r}'|} \nonumber \\
+g_Y(\mathbf{r},\mathbf{r}')=\frac{e^{-\kappa|\mathbf{r}-\mathbf{r}'|}}{4\pi|\mathbf{r}-\mathbf{r}'|}
+\end{align}
+%
+are the free-space Green's function of the Laplace and linearized Poisson-Boltzmann equations, respectively.
+
+In the \emph{direct} formulation, we take the limit of Equation \eqref{eq:volume_potential} as $\mathbf{r}$ approaches $\Gamma$and apply the interface conditions for $\phi$ and $\epsilon\partial\phi/\partial\mathbf{n}$ to get
+%
+\begin{align} \label{eq:direct}
+\frac{\phi_{1,\Gamma}}{2}+ K_{L}^{\Gamma}(\phi_{1,\Gamma}) -  V_{L}^{\Gamma} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Gamma} - \mathbf{r}_k|} \nonumber \\
+\frac{\phi_{1,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{1,\Gamma}) + \frac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{1,\Gamma} \right) & = 0
+\end{align}
+%
+Even though this formulation is poorly conditioned with respect to the mesh size, it can model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,WangCooperBetckeBarba2021}
 

### 2022-03-15 methods.tex
Updated plots and manuscript
I attach plots with preconditioner and without. It give a little more understanding of behaviour of each method, at least I think so. We should discuss that.
In terms of manuscript, I am sorry, it is quite rough draft, but I am struggling with what should be included in terms of mathematics and derivation of methods.

@@
 \begin{align}\label{eq:pbe}
-\nabla^2\phi_1(\mathbf{x}) &= \frac{1}{\epsilon}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
-\left(\nabla^2 - \kappa^2\right)\phi_2 &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
-\phi_1 = \phi_2 &\quad \epsilon_1\frac{\partial\phi_1}{\partial\mathbf{n}} = \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}} \quad \mathbf{x}\in \Gamma. 
+\nabla^2\phi_1(\mathbf{x}) &= \frac{1}{\epsilon_1}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
+\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
+\phi_1(\mathbf{x})  = \phi_2 (\mathbf{x}), &\quad \epsilon_1\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  = \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})  \quad \mathbf{x}\in \Gamma.
 \end{align}
@@
 \begin{align}\label{eq:phic}
-\nabla^2\phi_c(\mathbf{x}) &= \frac{1}{\epsilon_1}\sum_{k=1}^{N_q}q_k\delta(\mathbf{x},\mathbf{x}_k) \quad \mathbf{x}\in\Omega_1\cup\Omega_2\nonumber\\
+\nabla^2\phi_c(\mathbf{x}) &= \frac{1}{\epsilon}\sum_{k=1}^{N_q}q_k\delta(\mathbf{x},\mathbf{x}_k) \quad \mathbf{x}\in\Omega_1\cup\Omega_2\nonumber\\
 \phi_c(\mathbf{x})&=0 \quad \text{ as } |\mathbf{x}|\to\infty
@@
     \item Description with constant and variable permittivity
-    \item Standard BEM-BEM and FEM-BEM coupling approach
+
+BEM reduces the dimension of the problem by using the boundary integral equation, hence its popularity as a numerical solution of  the Poisson-Boltzmann equation in molecular electrostatics.
+Unfortunately, such advantage comes also with the cost.
+A fundamental solution must be found before the BEM can be applied.
+There are many linear problems for which fundamental solutions are not known.
+It is a case if we consider the heterogenous permittivity inside the molecule
+   \begin{align} \label{eq:pbe_vp}
+\epsilon_1(\mathbf{x}) \nabla^2\phi_1(\mathbf{x}) &= \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
+\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
+\phi_1(\mathbf{x})  = \phi_2(\mathbf{x}),  &\quad \epsilon_1(\mathbf{x})\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  = \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})  \quad \mathbf{x}\in \Gamma.
+\end{align}
+For such case finite element methods (FEM) are more suitable.
+
+The coupling of finite element (FEM) and boundary element (BEM) methods is the most widely used approach for solving multi-physical problems on an unbounded domain.
+It allows to take advantage of both methods.
+On the one hand, the BEM approximates only boundary conditions, hence it is commonly used for problems involving infinite or semi-infinite domains.
+On the other hand, the FEM is known for its robustness and universal applicability even for problem of inhomogeneous or non-linear nature.
+And that is why, we present two formualtions of FEM-BEM coupling for Poisson-Boltzmann equation.
+
+    \item Standard FEM-BEM coupling approach
+
+    We start with the variational formulation of the internal problem. Applying integration by parts for first equation of~\eqref{eq:pbe_vp} for every $v \in H_0^1(\Omega_1)$ we have
+\begin{equation}
+\label{eq:fem}
+ \int_{\Omega_1} \epsilon_1 \nabla \phi_1 : \nabla v ~d\mathbf{x}  - \oint_\Gamma \epsilon_1\partial_n \phi_1 v ds =   \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)  v ~d\mathbf{x}.
+\end{equation}
+For external problem we use BEM and the same direct formulation as in~\eqref{eq:direct}, hence we obtain
+\begin{align*}
+\frac{\phi_{1,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{1,\Gamma}) + \frac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{1,\Gamma} \right) & = 0.
+\end{align*}
+
     \item Hybrid FEM-BEM coupling
+
+    The main difference between the standard and hybrid FEM-BEM formulations is addition of hybrid variable $\widetilde{\phi}$ that is a trace of $\phi_1$ and $\phi_2$ on the interface $\Gamma$ ($\widetilde{\phi} = \phi_1 = \phi_2$ on  $\Gamma$).
+Both FEM and BEM formulations are modified to include the hybrid variable by adding some terms that enforce the equality of it with the trace of $\phi_1$ and $\phi_2$.
+    The previous standard formulation of interior problem~\eqref{eq:fem} can be rewritten as follows
+\begin{align*}
+ \int_{\Omega_m} \frac{\epsilon_1(\mathbf{x})}{\epsilon_2} \nabla \phi_1 : \nabla v d\mathbf{x} -  \oint_\Gamma \frac{\epsilon_1(\mathbf{x})}{\epsilon_2}  \partial_n \phi_1 v ds
+  & \\
+ -  \oint_\Gamma \frac{\epsilon_1(\mathbf{x})}{\epsilon_2} \partial_n v (\phi_1 - \widetilde{\phi}) ds
+  + \tfrac{\tau_F}{h} \oint_\Gamma \frac{\epsilon_1(\mathbf{x})}{\epsilon_2} (\phi_1 - \widetilde{\phi}) v ds & = \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)   v ~d\mathbf{x}.
+\end{align*}
+With every iteration we are solving above problem for given $\widetilde{\phi}$ .
+%We are using FEniCS finite element library, hence the above formulation is more sumilar to the implementation.
+
+In the case of exterior problem of~\eqref{eq:pbe_vp} we use Yukawa kernel and 
+%matrix form, for clarity and similarity with BEMpp implementation.
+In this case we consider linearised formulation of the Poisson-Boltzman equation that means our operators are built as for modified Helmholtz equation with wavenumber $\kappa$.
+For given $\widetilde{\phi}$, with each iteration we are solving the following system
+\begin{align*}
+V_{Y}^{\Gamma} \lambda  - \left( \tfrac{1}{2}Id + K_{Y}^{\Gamma}  \right) u &= - \widetilde{u},  \\
+ \left( \tfrac{1}{2} Id +  K_{Y}^{',\Gamma}\right)  \lambda + \left(W_{Y}^{\Gamma} + \tau_B Id\right)  u  &= \tau_B  \widetilde{u},
+\end{align*}
+where $K'$ and $W$ are the adjoint double-layer potentials and hypersingular operator for the Yukawa kernel.
+
+Both, the interior and exterior problems have unique solutions for given $\widetilde{u}$. In order to find $\widetilde{u}$ we solve the following problem on $\Gamma$
+$$
+\tau_B \left( u_s - \widetilde{u}\right) + \tfrac{\tau_F}{h} \left( u_m - \widetilde{u}\right) - \left(\frac{\epsilon_m}{\epsilon_s} \partial_n u -\lambda\right)  = 0.
+$$
 \end{itemize}

### 2022-03-15 results.tex
Updated plots and manuscript
I attach plots with preconditioner and without. It give a little more understanding of behaviour of each method, at least I think so. We should discuss that.
In terms of manuscript, I am sorry, it is quite rough draft, but I am struggling with what should be included in terms of mathematics and derivation of methods.

@@
 In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
-For the hybrid FEM-BEM coupling approach, we used $\tau$=10.
+For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
 
@@
 These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], invoking \texttt{tetgen} with the string \texttt{abcd}.
-For the hybrid FEM-BEM coupling approach, we used $\tau$=10.
+For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
 
@@
    \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
+   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
-  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_time.png}
-\caption{Time-to-solution for arginine with a constant permittivity. %(1) fix title, (2) can we put them in a single plot, (3) 
-maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?}
+  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
+  \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
+\caption{Time-to-solution for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).  %(1) fix title, (2) can we put them in a single plot, (3) 
+%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
+}
 \label{fig:arg_contant_time}
@@
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
-  \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_iter.png}
+  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
+  \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
-\caption{Iteration count for arginine with a constant permittivity.
+\caption{Iteration count for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
 %(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations?

### 2022-03-17 results.tex
edits to results

@@
 This section presents verification and performance results of the standard and hybrid FEM-BEM coupling schemes, for molecules modeled as cavities with constant and varying permittivity.
-When the permittivity inside the molecule was constant, we tested convergence against the available analytical expression of the solvation energy of a sphere [Kirkwood1934], and then compared a more realistic geometry (arginine) with a purely BEM implementation.
-On the other hand, we considered a Gaussian-varying permittivity [Alexov and earlier] inside arginine, and used APBS [Baker2001] to verify.
-The final result of this section shows the scaling of the standard and hybrid FEM-BEM coupling, as the molecule size grows.
+With a constant permittivity inside the molecule, we tested convergence against an analytical expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
+We also considered a Gaussian-varying permittivity [Alexov and earlier] inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
+The final tests show the scaling of the standard and hybrid FEM-BEM coupling, as the molecule size grows.
 
@@
 
-The Kirkwood sphere [Kirkwood1934] is a standard benchmarck for the Poisson-Boltzmann equation in molecular electrostatics. 
-Here, we considered a spherical cavity with radius $R=2$ \AA, with three charges ($q_1$=1, $q_2$=1, and $q_3$=0.75) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
-Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.33752347454015$ kcal/mol).
+The Kirkwood sphere \cite{Kirkwood1934} is a standard benchmark test for the Poisson-Boltzmann equation in molecular electrostatics. 
+In this case, we considered a spherical cavity of radius $R=2$ \AA, with three charges ($q_1$=1, $q_2$=1, and $q_3$=0.75) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
+Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.3375$ kcal/mol).
 In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
 For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
-
 The error in Figure \ref{fig:error_sphere} decays linearly with the surface area, which agrees with the expected convergence for P1 elements, indicating a correct implementation of the numerical scheme.
-We can see that the purely BEM implementation outperforms (or not?) FEM-BEM coupling in terms of accuracy for equivalent meshes, and also that the hybrid approach does not (or does?) influence accuracy.
+%We can see that the purely BEM implementation outperforms (or not?) FEM-BEM coupling in terms of accuracy for equivalent meshes, and also that the hybrid approach does not (or does?) influence accuracy.
 
@@
 
-%\begin{itemize}
-%    \item Show convergence to analytical solution for
-%    \begin{itemize}
-%        \item BEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.32\textwidth}
-%  \includegraphics[width=\linewidth]{BEM_BEM_Sphere_const_coeff_error.png}
-%  \caption{Error}
-%\endminipage\hfill
-%\minipage{0.32\textwidth}
-%  \includegraphics[width=\linewidth]{BEM_BEM_Sphere_const_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.32\textwidth}%
-%  \includegraphics[width=\linewidth]{BEM_BEM_Sphere_const_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%        \item Standard FEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.32\textwidth}
-%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_const_coeff_error.png}
-%  \caption{Error}
-%\endminipage\hfill
-%\minipage{0.32\textwidth}
-%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_const_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.32\textwidth}%
-%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_const_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%        \item Hybrid FEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.32\textwidth}
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_error.png}
-%  \caption{Error}
-%\endminipage\hfill
-%\minipage{0.32\textwidth}
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.32\textwidth}%
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_const_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%    \end{itemize}
-%\end{itemize}
-
-\subsection*{\sffamily \large Performance for arginine}
+\subsection*{\sffamily \large Performance with arginine}
 
@@
 We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper [Rocchia].
-These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], invoking \texttt{tetgen} with the string \texttt{abcd}.
+These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], which invoked \texttt{tetgen} with the string \texttt{abcd}.
 For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
 
-Figure \ref{fig:arg_constant_time} compares the time-to-solution with the three schemes, and shows that using only BEM outperforms both coupled FEM-BEM approaches.
+The solvation energy computed with the three schemes is presented by Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
+Then, Figure \ref{fig:arg_constant_time} compares the time-to-solution, and shows that using only BEM outperforms both coupled FEM-BEM approaches.
 Even though hybrid FEM-BEM is slower than standard FEM-BEM in Figure \ref{fig:arg_constant_time}, the iteration count in Figure \ref{fig:arg_constant_iter} shows that hybrid FEM-BEM needs less iterations (can we compare them?).
 This behavior is promising going towards larger problems, specially since the hybrid approach allows for more flexibility in the choice of preconditioner.
-We can also see that accuracy is not affected (or is?) by considering a FEM region inside the molecule (need fig to check this).
 
@@
    \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
+\caption{Solvation energy for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
+%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
+}
+\label{fig:arg_constant_energy}
+\end{figure}
+
+\begin{figure}
+\centering
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
@@
   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
-\caption{Time-to-solution for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).  %(1) fix title, (2) can we put them in a single plot, (3) 
+\caption{Time-to-solution for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
+NOTE: x axis differ between top and bottom.
+Also, should we include preconditioned vs non preconditioned?
+We could easily precondition BEM-BEM too.
+%(1) fix title, (2) can we put them in a single plot, (3)
 %maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
 }
-\label{fig:arg_contant_time}
+\label{fig:arg_constant_time}
 \end{figure}
@@
 \end{figure}
-
-%\begin{itemize}
-%    \item Use arginine or a small protein (1PGB?)
-%    \begin{itemize}
-%        \item BEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{BEM_BEM_Arginine_const_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.45\textwidth}%
-%  \includegraphics[width=\linewidth]{BEM_BEM_Arginine_const_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%        \item Standard FEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_const_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.45\textwidth}%
-%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_const_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%        \item Hybrid FEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.45\textwidth}%
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_const_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%    \end{itemize}
-%    \item Compare computer time and iterations for FEM-BEM with standard and hybrid approaches, without preconditioner. Choose hybrid.
-%    \item Show performance of hybrid method with preconditioner.
-%\end{itemize}
 
@@
 
-We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS for comparison. 
-We chose APBS because it provides an easy interface to control de dielectric map.....
-As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
+We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS~\cite{BakerETal2001} for comparison. 
+We chose APBS because it provides an easy interface to control dielectric maps, in order to make sure that they agree with the ones imposed in our FEM-BEM coupled approach.
+As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically (MOVE TO METHODS).
 For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, however, the solvent permittivity was set to $\epsilon$=2. 
@@
 Table \ref{table:arg_variable} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approaches.
-We can see that they are both converging to equivalent values of solvation energy, where the finest meshes agree up to the third significant figure.
+We can see that they are both converging to equivalent values, where the finest meshes agree up to the third significant figure.
 
@@
 \hline
-\multirow{3}{*}{APBS}& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
+\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & -32.4652\\ 
+& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
 &0.26$\times$0.26$\times$0.26 & -32.3375\\ 
 &0.17$\times$0.17$\times$0.17 & -32.3413\\ 
-& FINER & If possible\\ 
 \hline
@@
 
-%
-%    \begin{itemize}
-%        \item Standard FEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_varying_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.45\textwidth}%
-%  \includegraphics[width=\linewidth]{FEM_BEM_Sphere_varying_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%        \item Hybrid FEM-BEM
-%\begin{figure}[!htb]
-%\minipage{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_varying_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.45\textwidth}%
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Sphere_varying_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-
-%\begin{figure}[!htb]
-%\minipage{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.45\textwidth}%
-%  \includegraphics[width=\linewidth]{FEM_BEM_Arginine_varying_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-%\begin{figure}[!htb]
-%\minipage{0.45\textwidth}
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
-%  \caption{Iterations}
-%\endminipage\hfill
-%\minipage{0.45\textwidth}%
-%  \includegraphics[width=\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
-%  \caption{Computational time}
-%\endminipage
-%\end{figure}
-
 \subsection*{\sffamily \large Performance analysis for larger structures}

### 2022-03-17 methods.tex
Changes to methods

@@
 
-The implicit solvent model can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_X$ in Figure XX), and the Poisson equation in the solute region ($\Omega_Y$ in Figure XX).
+The implicit solvent model can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_1$ in Figure XX), and the Poisson equation in the solute region ($\Omega_2$ in Figure XX).
 These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous.
@@
 BEM reduces the dimension of the problem by using the boundary integral equation, hence its popularity as a numerical solution of  the Poisson-Boltzmann equation in molecular electrostatics.
-Unfortunately, such advantage comes also with the cost.
+Unfortunately, such advantage comes with the cost.
 A fundamental solution must be found before the BEM can be applied.
 There are many linear problems for which fundamental solutions are not known.
-It is a case if we consider the heterogenous permittivity inside the molecule
+For Poisson-Boltzmann equation it is a case if we consider the heterogenous permittivity inside the molecule
    \begin{align} \label{eq:pbe_vp}
@@
 
+   As mentioned before we will use finite element discretisation for internal problem on domain $\Omega_1$ and boundary elements for external domain $\Omega_2$.
+The formulation below can be applied for homogeneous and heterogeneous $\epsilon_1$, hence for simplicity we do not distinguish between these cases in the formulation.
+
     We start with the variational formulation of the internal problem. Applying integration by parts for first equation of~\eqref{eq:pbe_vp} for every $v \in H_0^1(\Omega_1)$ we have
@@
 
+Using the above definition and assuming that $\lambda_{1,\Gamma}  = \frac{\partial}{\partial \mathbf{n}} \phi_{1,\Gamma} $ the coupling problem can be written as follows
+\begin{center}
+  \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_{1,\Gamma} \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$}
+\begin{equation} 
+\label{eq:standard_fem_bem}
+ \left\{
+ \begin{array}{rcl}
+ \int_{\Omega_1} \epsilon_1 \nabla \phi_1 : \nabla v ~d\mathbf{x}  - \oint_\Gamma \epsilon_1\partial_n \phi_1 v ds &=&   \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)  v ~d\mathbf{x} \\[3mm]
+  \oint_\Gamma \left(\tfrac{1}{2} - K_{Y}^{\Gamma}\right) \phi_{1,\Gamma} \zeta ds + \frac{\epsilon_1}{\epsilon_2} \oint_\Gamma V_{Y}^{\Gamma} \lambda_{1,\Gamma} \zeta ds &=&0.
+  \end{array}
+  \right.
+\end{equation}
+\end{center}
+
+%\begin{align}\label{eq:standard_fem_bem}
+% \int_{\Omega_1} \epsilon_1 \nabla \phi_1 : \nabla v ~d\mathbf{x}  - \oint_\Gamma \epsilon_1\partial_n \phi_1 v ds &=   \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)  v ~d\mathbf{x} \\
+% \oint_\Gamma \frac{\phi_{1,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{1,\Gamma}) + \frac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \lambda_{1,\Gamma} \right) & = 0
+%\end{align}
+
     \item Hybrid FEM-BEM coupling
 
+  In the previous section, we focused on the standard formulation.
+Now, we propose the weak penalty formulation of a couple problem.
+The discretisation is made by using finite element methods in the domain $\Omega_1$ and boundary integral methods in the domain $\Omega_2$.
+
     The main difference between the standard and hybrid FEM-BEM formulations is addition of hybrid variable $\widetilde{\phi}$ that is a trace of $\phi_1$ and $\phi_2$ on the interface $\Gamma$ ($\widetilde{\phi} = \phi_1 = \phi_2$ on  $\Gamma$).
-Both FEM and BEM formulations are modified to include the hybrid variable by adding some terms that enforce the equality of it with the trace of $\phi_1$ and $\phi_2$.
-    The previous standard formulation of interior problem~\eqref{eq:fem} can be rewritten as follows
+Both FEM and BEM subproblems are modified to include the hybrid variable by adding some terms that enforce the equality of it with the trace of $\phi_1$ and $\phi_2$.
+
+    The standard formulation of interior problem~\eqref{eq:fem} can be rewritten as follows
 \begin{align*}
@@
 \end{align*}
-With every iteration we are solving above problem for given $\widetilde{\phi}$ .
+With every iteration we are solving above problem for given $\widetilde{\phi}$ and hence obtaining the solution $ \phi_1$.
 %We are using FEniCS finite element library, hence the above formulation is more sumilar to the implementation.
@@
 In this case we consider linearised formulation of the Poisson-Boltzman equation that means our operators are built as for modified Helmholtz equation with wavenumber $\kappa$.
-For given $\widetilde{\phi}$, with each iteration we are solving the following system
+for given $\widetilde{\phi}$, with each iteration we are solving the following system
 \begin{align*}
-V_{Y}^{\Gamma} \lambda  - \left( \tfrac{1}{2}Id + K_{Y}^{\Gamma}  \right) u &= - \widetilde{u},  \\
- \left( \tfrac{1}{2} Id +  K_{Y}^{',\Gamma}\right)  \lambda + \left(W_{Y}^{\Gamma} + \tau_B Id\right)  u  &= \tau_B  \widetilde{u},
+V_{Y}^{\Gamma} \lambda_{2,\Gamma}  - \left( \tfrac{1}{2}Id + K_{Y}^{\Gamma}  \right) \phi_2 &= - \widetilde{\phi},  \\
+ \left( \tfrac{1}{2} Id +  K_{Y}^{',\Gamma}\right)  \lambda_{2,\Gamma} + \left(W_{Y}^{\Gamma} + \tau_B Id\right)  \phi_2  &= \tau_B \widetilde{\phi},
 \end{align*}
@@
 
-Both, the interior and exterior problems have unique solutions for given $\widetilde{u}$. In order to find $\widetilde{u}$ we solve the following problem on $\Gamma$
-$$
-\tau_B \left( u_s - \widetilde{u}\right) + \tfrac{\tau_F}{h} \left( u_m - \widetilde{u}\right) - \left(\frac{\epsilon_m}{\epsilon_s} \partial_n u -\lambda\right)  = 0.
-$$
+Both, the interior and exterior problems have unique solutions for given $\widetilde{\phi}$. In order to find $\widetilde{\phi}$ we solve the following problem on $\Gamma$
+\begin{equation*}
+\tfrac{\tau_F}{h} \left( \phi_1 - \widetilde{\phi}\right) + \tau_B \left( \phi_2 - \widetilde{\phi}\right)  - \left(\frac{\epsilon_1}{\epsilon_2} \frac{\partial}{\partial \mathbf{n}} \phi_1 -\lambda_{2,\Gamma} \right)  = 0.
+\end{equation*}
 \end{itemize}

### 2022-03-25 methods.tex
Heterogenous permittivity - repair equation (8)
Previous wrong commit
added lu formulation

@@
 
-There are several possible boundary integral formulations of Equation \eqref{eq:pbe}.~\cite{SearchCooperWout2022} The simplest form was presented by Yoon and Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, which only couples the potential at the interface, and not its derivative.
+There are several possible boundary integral formulations of Equation \eqref{eq:pbe}.~\cite{SearchCooperWout2022} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
+Here, we use the better conditioned formulation presented by Lu and co-workers.~\cite{LuETal2006,LuETal2009,ZhangETal2019}
 Applying Green's second identity to Equation \eqref{eq:pbe} we get 
@@
 
-In the \emph{direct} formulation, we take the limit of Equation \eqref{eq:volume_potential} as $\mathbf{r}$ approaches $\Gamma$and apply the interface conditions for $\phi$ and $\epsilon\partial\phi/\partial\mathbf{n}$ to get
+If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{r}$ approaches $\Gamma$, we get
 %
@@
 \frac{\phi_{1,\Gamma}}{2}+ K_{L}^{\Gamma}(\phi_{1,\Gamma}) -  V_{L}^{\Gamma} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Gamma} - \mathbf{r}_k|} \nonumber \\
-\frac{\phi_{1,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{1,\Gamma}) + \frac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{1,\Gamma} \right) & = 0
+\frac{\phi_{2,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{2,\Gamma}) + V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0
 \end{align}
 %
+The {\it direct} formulation\cite{YoonLenhoff1991} couples the two expressions of Eq.
+\eqref{eq:direct} on $\Gamma$ with the interface conditions.
 Even though this formulation is poorly conditioned with respect to the mesh size, it can model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,WangCooperBetckeBarba2021}
+The formulation presented by Lu\cite{LuETal2006} takes the normal derivative of \eqref{eq:direct} to couple both $\phi$ and $\partial\phi/\partial\mathbf{n}$ as
+%
+\begin{align}\label{eq:lu}
+    & \frac{\phi_{2,\Gamma}}{2}\left(\frac{\epsilon_1}{\epsilon_2}+1\right) - \left(K_Y^\Gamma - \frac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)(\phi_{2,\Gamma}) + \left(V_Y^\Gamma - V_L^\Gamma\right)\left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}
+     \nonumber \\
+    &\frac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)(\phi_{2,\Gamma}) +  \frac{1}{2}\frac{\phi_{2,\Gamma}}{\partial\mathbf{n}}\left(1+\frac{\epsilon_1}{\epsilon_2}\right) + \left(\frac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{r}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}\right)
+\end{align}
+%
+The two new integral operators that appear are defined as 
+%
+\begin{align}\label{eq:adj_hyp}
+K^{\prime\Gamma}_{L,Y}(\varphi) = \oint_\Gamma \frac{g_{L,Y}}{\partial\mathbf{n}}(\mathbf{r}_\Gamma,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}'\nonumber\\
+W^\Gamma_{L,Y}(\varphi) = - \oint_\Gamma \frac{\partial^2 g_{L,Y}}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{r}_\Gamma,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}'
+\end{align}
+%
+and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior.
+
+Having computed the electrostatic potential with Eq.
+\eqref{eq:lu}, the reaction potential ($\phi_r$) in Eq.
+\eqref{eq:energy} by subtracting out the Coulombic component out of $\phi_1$ in Eq.
+\eqref{eq:volume_potential}.
+This gives
+%
+\begin{align} \label{eq:phi_reac}
+\phi_{r} = - K_{L}^{\Omega_1}(\phi_{1,\Gamma}) + V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right)
+\end{align}
 
@@
    \begin{align} \label{eq:pbe_vp}
-\epsilon_1(\mathbf{x}) \nabla^2\phi_1(\mathbf{x}) &= \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
+\nabla \cdot \left(\epsilon_1(\mathbf{x}) \nabla \phi_1(\mathbf{x})\right) &= \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
 \left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\

### 2022-03-28 methods.tex
added citations in methods

@@
 %
-where $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively, $\kappa$ is the inverse of the Debye length, related with the salt concentration, and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.
+Here, $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively, $\kappa$ is the inverse of the Debye length, related with the salt concentration, and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.
 
-The electrostatic potential in $\Omega_1$ can be further decomposed into singular and regular components as $\phi_1 = \phi_c + \phi_R$, where $\phi_c$ is the solution to
+The electrostatic potential in $\Omega_1$ can be further decomposed into singular and regular components as $\phi_1 = \phi_c + \phi_r$, where $\phi_c$ is the solution to
 %
@@
 
-Physically, $\phi_c$ can be interpreted as the Coulomb-type potential from the point charges, whereas $\phi_R$, also known as reaction potential, is originated by the polarization of the solvent. 
+Physically, $\phi_c$ can be interpreted as the Coulomb-type potential from the point charges, whereas $\phi_r$, also known as reaction potential, is originated by the polarization of the solvent and reorganization of the free ions.
 Usually, $\epsilon_1$ is considered a constant value, yielding an analytical expression for $\phi_c$, however, this is not the general case.
 
-There are regularized versions of Equation \eqref{eq:pbe} [HolstETal2008,GengZhao2020] which are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods.
+There are regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} which are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods.
 However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permitivitties.
@@
 
-The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson-Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,CooperForsythClementiBarba2016} and more recently, with Bempp-cl.~\cite{SearchCooperWout2022}
+The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson-Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl.~\cite{search2022towards}
 
-There are several possible boundary integral formulations of Equation \eqref{eq:pbe}.~\cite{SearchCooperWout2022} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
-Here, we use the better conditioned formulation presented by Lu and co-workers.~\cite{LuETal2006,LuETal2009,ZhangETal2019}
+There are several possible boundary integral formulations of Equation \eqref{eq:pbe}.~\cite{search2022towards} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
+Here, we use the better conditioned formulation presented by Lu and co-workers.~\cite{LuETal2006,LuETal2009,debuhr2016dashmm}
 Applying Green's second identity to Equation \eqref{eq:pbe} we get 
@@
 \begin{align} \label{eq:volume_potential}
-\phi_{1}+ K_{L}^{\Omega_1}(\phi_{1,\Gamma}) -  V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Omega_1} - \mathbf{r}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
-\phi_{2} - K_{Y}^{\Omega_2}(\phi_{2,\Gamma}) + V_{Y}^{\Omega_2} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0 \quad \text{on $\Omega_2$,}
+\phi_{1}(\mathbf{r}_{\Omega_1})+ K_{L}^{\Omega_1}(\phi_{1,\Gamma}) -  V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Omega_1} - \mathbf{r}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
+\phi_{2}(\mathbf{r}_{\Omega_2}) - K_{Y}^{\Omega_2}(\phi_{2,\Gamma}) + V_{Y}^{\Omega_2} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0 \quad \text{on $\Omega_2$,}
 \end{align}
 %
-where $\phi_{1,\Gamma} = \phi_1(\mathbf{r}_\Gamma)$ and $\phi_{2,\Gamma} = \phi_2(\mathbf{r}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+where $\mathbf{r}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_{1,\Gamma} = \phi_1(\mathbf{r}_\Gamma)$ and $\phi_{2,\Gamma} = \phi_2(\mathbf{r}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
 $K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
@@
 
-If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{r}$ approaches $\Gamma$, we get
+If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{r}_{\Omega}$ approaches $\Gamma$, we get
 %
@@
 %
-The {\it direct} formulation\cite{YoonLenhoff1991} couples the two expressions of Eq.
-\eqref{eq:direct} on $\Gamma$ with the interface conditions.
-Even though this formulation is poorly conditioned with respect to the mesh size, it can model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,WangCooperBetckeBarba2021}
+The {\it direct} formulation\cite{YoonLenhoff1990} couples the two expressions of Eq.
+\eqref{eq:direct} on $\Gamma$, considering the interface conditions.
+Even though this formulation is poorly conditioned with respect to the mesh size, it can still model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,MartinezETal2019,wang2021high}
 The formulation presented by Lu\cite{LuETal2006} takes the normal derivative of \eqref{eq:direct} to couple both $\phi$ and $\partial\phi/\partial\mathbf{n}$ as
@@
 Having computed the electrostatic potential with Eq.
-\eqref{eq:lu}, the reaction potential ($\phi_r$) in Eq.
-\eqref{eq:energy} by subtracting out the Coulombic component out of $\phi_1$ in Eq.
+\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.
+\eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$ in Eq.
 \eqref{eq:volume_potential}.
@@
 \begin{align} \label{eq:phi_reac}
-\phi_{r} = - K_{L}^{\Omega_1}(\phi_{1,\Gamma}) + V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right)
+\phi_{r} = - K_{L}^{\Omega_1}(\phi_{1,\Gamma}) + V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right),
 \end{align}
+%
+which is valid as long as $\epsilon_1$ is a constant.
 

### 2022-03-29 intro.tex
added more refs

In biologically relevant settings, the structure and function of biomolecules is largely determined by the surrounding water, which usually contains salt. 
To describe these systems accurately, we need to account for the solvent correctly, which has given rise to a wide range of models \cite{onufriev2018water}
Highly detailed models consider every water molecule and salt ion explicitly, however, there are approximated models that use continuum theory to represent this ionic solution, knwon as implicit-solvent models\cite{RouxSimonson1999,DecherchiETal2015}.
In the case of electrostatics, the implicit-solvent model is mathematically characterized by the Poisson-Boltzmann equation (PBE)\cite{Baker2004,Bardhan2012}, which is widely used to compute solvation free energies and mean-field potentials.

The implicit-solvent model for electrostatics describes the dissolved molecule as a infinite medium with a low-dielectric solute-shaped cavity, which contains a charge distribution from the partial charges --- usually a sum of Dirac deltas at the atom's locations.
The outer solvent region is represented with a high dielectric, and considers the presence of salt.
These two regions are interfaced by the molecular surface, which can be defined in various ways \cite{HarrisBoschitcshFenley2013}, where the continuity of the electrostatic potential and electric displacement are enforced.

The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{AltmanBardhanWhiteTidor09,LuETal2006,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
In particular, the boundary element method (BEM) has proven to be very efficient for high accuracy calculations [GengKrasny2013,CooperBardhanBarba2014], mainly due to the precise description of the molecular surface and point charges. 
However, BEM is limited to constant material properties in each region, and the linear version of the PBE. 
Even though these limitations are acceptable in a wide range of applications, there are cases when BEM falls short, for example, if a variable permittivity is required inside the solute [cite], or the solute is highly charged such that the linear approximation breaks [cite?].

This article presents a methodology to overcome some of those limitations, through coupling boundary and finite elements (FEM-BEM).
This approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the dissolved molecule.

### 2022-03-29 results.tex
Update of results in the paper
added more refs

@@
 With a constant permittivity inside the molecule, we tested convergence against an analytical expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
-We also considered a Gaussian-varying permittivity [Alexov and earlier] inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
+We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
 The final tests show the scaling of the standard and hybrid FEM-BEM coupling, as the molecule size grows.
@@
    \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
-   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
+%    \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
 \caption{Solvation energy for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
@@
   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
-  \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
+%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
 \caption{Time-to-solution for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
@@
   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
-  \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
+%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
@@
 Standard    & 4  & -33.129 \\
-FEM-BEM    & 8  & -32.674 \\
+FEM-BEM    & 8  & -32.673 \\
     & 16 & -32.293 \\
@@
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
-    & 2 & -35.333\\
-Hybrid    & 4  & -33.079 \\
-FEM-BEM    & 8  & -32.660 \\
-    & 16 & -32.359 \\
+    & 2 & -34.408\\
+Hybrid    & 4  & -32.815 \\
+FEM-BEM    & 8  & -32.566 \\
+    & 16 & -32.379 \\
 \hline

### 2022-03-29 intro.tex
added more refs and weak form in bembem

@@
 The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{AltmanBardhanWhiteTidor09,LuETal2006,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
-In particular, the boundary element method (BEM) has proven to be very efficient for high accuracy calculations [GengKrasny2013,CooperBardhanBarba2014], mainly due to the precise description of the molecular surface and point charges.
+In particular, the boundary element method (BEM) has proven to be very efficient for high accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.
 However, BEM is limited to constant material properties in each region, and the linear version of the PBE. 
-Even though these limitations are acceptable in a wide range of applications, there are cases when BEM falls short, for example, if a variable permittivity is required inside the solute [cite], or the solute is highly charged such that the linear approximation breaks [cite?].
+Even though these limitations are acceptable in a wide range of applications, there are cases when BEM falls short, for example, if a variable permittivity is required inside the solute \cite{grant2001smooth,li2013dielectric}, or the solute is highly charged such that the linear approximation breaks\cite{FogolariETal1999}.
 
-This article presents a methodology to overcome some of those limitations, through coupling boundary and finite elements (FEM-BEM).
+This article presents a methodology to overcome some of those limitations, by coupling finite and boundary elements methods (FEM-BEM coupling).
 This approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the dissolved molecule.

### 2022-03-29 methods.tex
added more refs and weak form in bembem

@@
 \begin{align} \label{eq:volume_potential}
-\phi_{1}(\mathbf{r}_{\Omega_1})+ K_{L}^{\Omega_1}(\phi_{1,\Gamma}) -  V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Omega_1} - \mathbf{r}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
-\phi_{2}(\mathbf{r}_{\Omega_2}) - K_{Y}^{\Omega_2}(\phi_{2,\Gamma}) + V_{Y}^{\Omega_2} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0 \quad \text{on $\Omega_2$,}
+\phi_{1}(\mathbf{r}_{\Omega_1})+ K_{L}^{\Omega_1}(\phi_{1,\Gamma}) -  V_{L}^{\Omega_1} \lambda_1 & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Omega_1} - \mathbf{r}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
+\phi_{2}(\mathbf{r}_{\Omega_2}) - K_{Y}^{\Omega_2}(\phi_{2,\Gamma}) + V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
 \end{align}
@@
 where $\mathbf{r}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_{1,\Gamma} = \phi_1(\mathbf{r}_\Gamma)$ and $\phi_{2,\Gamma} = \phi_2(\mathbf{r}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
 $K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
@@
 \begin{align} \label{eq:direct}
-\frac{\phi_{1,\Gamma}}{2}+ K_{L}^{\Gamma}(\phi_{1,\Gamma}) -  V_{L}^{\Gamma} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Gamma} - \mathbf{r}_k|} \nonumber \\
-\frac{\phi_{2,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{2,\Gamma}) + V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0
+\frac{\phi_{1,\Gamma}}{2}+ K_{L}^{\Gamma}(\phi_{1,\Gamma}) -  V_{L}^{\Gamma} \lambda_1 & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Gamma} - \mathbf{r}_k|} \nonumber \\
+\frac{\phi_{2,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{2,\Gamma}) + V_{Y}^{\Gamma} \lambda_2 & = 0
 \end{align}
@@
 \begin{align}\label{eq:lu}
-    & \frac{\phi_{2,\Gamma}}{2}\left(\frac{\epsilon_1}{\epsilon_2}+1\right) - \left(K_Y^\Gamma - \frac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)(\phi_{2,\Gamma}) + \left(V_Y^\Gamma - V_L^\Gamma\right)\left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}
+    & \frac{\phi_{2,\Gamma}}{2}\left(\frac{\epsilon_1}{\epsilon_2}+1\right) - \left(K_Y^\Gamma - \frac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)(\phi_{2,\Gamma}) + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}
      \nonumber \\
-    &\frac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)(\phi_{2,\Gamma}) +  \frac{1}{2}\frac{\phi_{2,\Gamma}}{\partial\mathbf{n}}\left(1+\frac{\epsilon_1}{\epsilon_2}\right) + \left(\frac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{r}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}\right)
+    &\frac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)(\phi_{2,\Gamma}) +  \frac{1}{2}\lambda_2\left(1+\frac{\epsilon_1}{\epsilon_2}\right) + \left(\frac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{r}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}\right)
 \end{align}
@@
 and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior. 
+In weak form, Eq. \eqref{eq:lu} becomes
+%
+\begin{align}\label{eq:lu_disc}
+&\left< \frac{1}{2}\left(\frac{\epsilon_1}{\epsilon_2}+1\right) I - \left(K_Y^\Gamma - \frac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)(\phi_{2}), v \right>_{\Gamma} + \left< \left(V_Y^\Gamma - V_L^\Gamma\right) \lambda_2, v \right>_\Gamma = \left( \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}, v \right)_{\Omega_1} \nonumber \\
+&\left< \frac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_{2} \right>_\Gamma + \left< \left(1+\frac{\epsilon_1}{\epsilon_2}\right) + \left(\frac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2, v\right>_\Gamma = 0
+\end{align}
+%
+where $v$ is a test function, and $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{r})v(\mathbf{r})d\mathbf{r}$ and $\left(\varphi,v\right)_\Omega = \int_\Omega \varphi(\mathbf{r})v(\mathbf{r})d\mathbf{r}$ are the inner products on the surface and domain, respectively.
+This can be written in matrix form as
+%
+\begin{align}
+Matrix equation
+\end{align}
+%
 
 Having computed the electrostatic potential with Eq.
-\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.
+\eqref{eq:lu_disc}, we obtain the reaction potential ($\phi_r$) in Eq.
 \eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$ in Eq.

### 2022-03-29 results.tex
added more refs and weak form in bembem

@@
 In the solvent region, we used the permittivity of water ($\epsilon_2$=80) and an inverse of the Debye length of $\kappa=0.125$ \AA$^{-1}$.
+As in these cases there is an analytical solution for $\phi_c$ in Eq.
+\eqref{eq:phic}, we compute $\phi_r$ with Eq.
+\eqref{eq:phi_reac} in both BEM-BEM and FEM-BEM coupling approaches.
+Then, for FEM-BEM, the integral over $\Gamma$ in Eq.
+\eqref{eq:phi_reac} corresponds to the trace of the solution vector.
 

### 2022-04-19 methods.tex
Work on paper
Methods: adding matrix formulations and changes of notation for consistence.
Results: update of results for more refine volume mesh

--- 2022-03-28 methods.tex
@@
 \begin{align}\label{eq:pbe}
-\nabla^2\phi_1(\mathbf{x}) &= \frac{1}{\epsilon_1}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
+\nabla^2\phi_1(\mathbf{x}) &= \tfrac{1}{\epsilon_1}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
 \left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
@@
 \begin{align}\label{eq:phic}
-\nabla^2\phi_c(\mathbf{x}) &= \frac{1}{\epsilon}\sum_{k=1}^{N_q}q_k\delta(\mathbf{x},\mathbf{x}_k) \quad \mathbf{x}\in\Omega_1\cup\Omega_2\nonumber\\
+\nabla^2\phi_c(\mathbf{x}) &= \tfrac{1}{\epsilon}\sum_{k=1}^{N_q}q_k\delta(\mathbf{x},\mathbf{x}_k) \quad \mathbf{x}\in\Omega_1\cup\Omega_2\nonumber\\
 \phi_c(\mathbf{x})&=0 \quad \text{ as } |\mathbf{x}|\to\infty
@@
 \begin{equation}\label{eq:dG} 
-\Delta G_{solv} = \frac{1}{2}\int_{\Omega_1} \rho(\mathbf{x})\phi_{r}(\mathbf{x}) = \frac{1}{2}\sum_{k=1}^{N_q} q_k\phi_r(\mathbf{x_k})
+\Delta G_{solv} = \tfrac{1}{2}\int_{\Omega_1} \rho(\mathbf{x})\phi_{r}(\mathbf{x}) = \tfrac{1}{2}\sum_{k=1}^{N_q} q_k\phi_r(\mathbf{x_k})
 \end{equation}
@@
 
-\subsection*{\sffamily \large BEM-BEM coupling}
+\subsubsection*{\sffamily \normalsize BEM-BEM coupling}
 
@@
 \begin{align} \label{eq:volume_potential}
-\phi_{1}(\mathbf{r}_{\Omega_1})+ K_{L}^{\Omega_1}(\phi_{1,\Gamma}) -  V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Omega_1} - \mathbf{r}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
-\phi_{2}(\mathbf{r}_{\Omega_2}) - K_{Y}^{\Omega_2}(\phi_{2,\Gamma}) + V_{Y}^{\Omega_2} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0 \quad \text{on $\Omega_2$,}
+\phi_{1}(\mathbf{x}_{\Omega_1})+ K_{L}^{\Omega_1}\phi_1 -  V_{L}^{\Omega_1} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Omega_1} - \mathbf{x}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
+\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
 \end{align}
 %
-where $\mathbf{r}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_{1,\Gamma} = \phi_1(\mathbf{r}_\Gamma)$ and $\phi_{2,\Gamma} = \phi_2(\mathbf{r}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+where $\mathbf{x}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
 $K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
@@
 \begin{align}\label{eq:single_double}
-V^\Omega_{L,Y}(\varphi) = \oint_\Gamma g_{L,Y}(\mathbf{r}_\Omega,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}'\nonumber\\
-K^\Omega_{L,Y}(\varphi) = \oint_\Gamma \frac{\partial g_{L,Y}}{\partial\mathbf{n}'}(\mathbf{r}_\Omega,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}',\nonumber\\
+V^D \varphi (\mathbf{x}) = \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+K^D \varphi (\mathbf{x}) = \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
 \end{align}
 %
-where $\varphi(\mathbf{r})$ can be any distribution over $\Gamma$, and 
+where $D \in \{\Omega_1, \Omega_2, \Gamma\}$, $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and 
 %
 \begin{align}\label{eq:green_func}
-g_L(\mathbf{r},\mathbf{r}')=\frac{1}{4\pi|\mathbf{r}-\mathbf{r}'|} \nonumber \\
-g_Y(\mathbf{r},\mathbf{r}')=\frac{e^{-\kappa|\mathbf{r}-\mathbf{r}'|}}{4\pi|\mathbf{r}-\mathbf{r}'|}
+g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
 \end{align}
@@
 
-If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{r}_{\Omega}$ approaches $\Gamma$, we get
+If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{x}_{\Omega}$ approaches $\Gamma$, we get
 %
 \begin{align} \label{eq:direct}
-\frac{\phi_{1,\Gamma}}{2}+ K_{L}^{\Gamma}(\phi_{1,\Gamma}) -  V_{L}^{\Gamma} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right) & = \frac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{r}_{\Gamma} - \mathbf{r}_k|} \nonumber \\
-\frac{\phi_{2,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{2,\Gamma}) + V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) & = 0
+\tfrac{\phi_1}{2}+ K_{L}^{\Gamma}\phi_1 -  V_{L}^{\Gamma} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Gamma} - \mathbf{x}_k|} \nonumber \\
+\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 + V_{Y}^{\Gamma} \lambda_2 & = 0
 \end{align}
@@
 \begin{align}\label{eq:lu}
-    & \frac{\phi_{2,\Gamma}}{2}\left(\frac{\epsilon_1}{\epsilon_2}+1\right) - \left(K_Y^\Gamma - \frac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)(\phi_{2,\Gamma}) + \left(V_Y^\Gamma - V_L^\Gamma\right)\left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}
+    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
      \nonumber \\
-    &\frac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)(\phi_{2,\Gamma}) +  \frac{1}{2}\frac{\phi_{2,\Gamma}}{\partial\mathbf{n}}\left(1+\frac{\epsilon_1}{\epsilon_2}\right) + \left(\frac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\left( \frac{\partial}{\partial \mathbf{n}} \phi_{2,\Gamma} \right) = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{r}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{r}_{\Gamma} - \mathbf{r}_k|}\right)
+    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
 \end{align}
@@
 %
-\begin{align}\label{eq:adj_hyp}
-K^{\prime\Gamma}_{L,Y}(\varphi) = \oint_\Gamma \frac{g_{L,Y}}{\partial\mathbf{n}}(\mathbf{r}_\Gamma,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}'\nonumber\\
-W^\Gamma_{L,Y}(\varphi) = - \oint_\Gamma \frac{\partial^2 g_{L,Y}}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{r}_\Gamma,\mathbf{r}')\varphi(\mathbf{r}')d\mathbf{r}'
+\begin{align}
+\label{eq:adj_hyp}
+K^{\prime\Gamma}_i\varphi (\mathbf{x}) = \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+W^\Gamma_i\varphi (\mathbf{x}) = - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+\end{align}
+where $i \in \{L,Y\}$, 
+and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior. 
+In weak form, Eq. \eqref{eq:lu} becomes
+%
+\begin{align}\label{eq:lu_disc}
+&\left< \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\phi_{2}}{2} - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_{2}, v \right>_{\Gamma} + \left< \left(V_Y^\Gamma - V_L^\Gamma\right) \lambda_2, v \right>_\Gamma = \left< \sum_{k=0}^{N_q}  f_k, v \right>_{\Gamma} \nonumber \\
+&\left< \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_{2}, \zeta \right>_\Gamma + \left<  \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\lambda_2}{2} + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2, \zeta\right>_\Gamma = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}} f_k, \zeta \right>_{\Gamma}
 \end{align}
 %
-and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior.
+where $v, \zeta$ are test functions, $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ %and $\left(\varphi,v\right)_\Omega = \int_\Omega \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are
+is the inner products on the surface% and domain, respectively
+and $f_k := \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}$.
+
+We introduce below the matrix formulation. Let $\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ be the vector of canonical basis
+functions of $W_{h}^{k}$ and  $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
+functions of $\Lambda_{h}^{l}$. We define the following matrices associated with the corresponding bilinear forms
+\begin{align*}
+\widetilde{K}_{\alpha \beta} = \left<\left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right) \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}
+ &,&
+\widetilde{V}_{\alpha \beta} = \left<\left(V_Y^\Gamma - V_L^\Gamma\right) \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
+\widetilde{W}_{\alpha \beta} = \left<\left(W_Y^\Gamma - W_L^\Gamma\right) \phi^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
+ &,&
+\widetilde{K'}_{\alpha \beta} = \left<\left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right) \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma},
+\end{align*}
+and vectors associated with the corresponding linear forms
+\begin{align*}
+\vec{f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},   \phi^{\beta}_1  \right>_{\Gamma} &,& \vec{\partial f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),   \phi^{\beta}_1  \right>_{\Gamma}.
+\end{align*}
+
+Using the above definition the discrete problem~\eqref{eq:fem_bem_disctrete} can be written in the following matrix form
+\begin{align*}
+\begin{bmatrix}
+ \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I - \widetilde{K}  & \widetilde{V}  \\  
+ \tfrac{\epsilon_1}{\epsilon_2} \widetilde{W} & \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I + \widetilde{K'}
+\end{bmatrix}
+\begin{bmatrix}
+\vec{\phi}_2 \\
+\vec{\lambda}_2 
+\end{bmatrix}
+= 
+\begin{bmatrix}
+\vec{f} \\  
+\vec{\partial f}
+\end{bmatrix}.
+\end{align*}
+%
 
 Having computed the electrostatic potential with Eq.
-\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.
+\eqref{eq:lu_disc}, we obtain the reaction potential ($\phi_r$) in Eq.
 \eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$ in Eq.
@@
 \begin{align} \label{eq:phi_reac}
-\phi_{r} = - K_{L}^{\Omega_1}(\phi_{1,\Gamma}) + V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_{1,\Gamma}  \right),
+\phi_{r} = - K_{L}^{\Omega_1}(\phi_1) + V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_1  \right),
 \end{align}
@@
 
-\subsection*{\sffamily \large FEM-BEM coupling}
+\subsection*{\sffamily \normalsize FEM-BEM coupling}
 
-\begin{itemize}
-    \item Description with constant and variable permittivity
+{\sffamily \small Description with constant and variable permittivity}
 
@@
 On the other hand, the FEM is known for its robustness and universal applicability even for problem of inhomogeneous or non-linear nature.
-And that is why, we present two formualtions of FEM-BEM coupling for Poisson-Boltzmann equation.
+And that is why, we present two formulations of FEM-BEM coupling for Poisson-Boltzmann equation.
 
-    \item Standard FEM-BEM coupling approach
+{\sffamily \small Standard FEM-BEM coupling approach}
 
@@
 \label{eq:fem}
- \int_{\Omega_1} \epsilon_1 \nabla \phi_1 : \nabla v ~d\mathbf{x}  - \oint_\Gamma \epsilon_1\partial_n \phi_1 v ds =   \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)  v ~d\mathbf{x}.
+ \left( \epsilon_1 \nabla \phi_1, \nabla v \right)_{\Omega_1}  -  \left<  \epsilon_1\partial_n \phi_1, v \right>_\Gamma =  \left( \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v\right)_{\Omega_1},
 \end{equation}
+where $v$ is a test function, and $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ and $\left(\varphi,v\right)_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are the inner products on the surface and domain, respectively.
 For external problem we use BEM and the same direct formulation as in~\eqref{eq:direct}, hence we obtain
 \begin{align*}
-\frac{\phi_{1,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{1,\Gamma}) + \frac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_{1,\Gamma} \right) & = 0.
+\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_1 \right) & = 0.
 \end{align*}
 
-Using the above definition and assuming that $\lambda_{1,\Gamma}  = \frac{\partial}{\partial \mathbf{n}} \phi_{1,\Gamma} $ the coupling problem can be written as follows
+Using the above definition and assuming that $\lambda_2  = \frac{\partial}{\partial \mathbf{n}} \phi_1 $ the coupling problem can be written as follows
 \begin{center}
-  \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_{1,\Gamma} \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$}
+  \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_2 \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$}
 \begin{equation} 
@@
  \begin{array}{rcl}
- \int_{\Omega_1} \epsilon_1 \nabla \phi_1 : \nabla v ~d\mathbf{x}  - \oint_\Gamma \epsilon_1\partial_n \phi_1 v ds &=&   \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)  v ~d\mathbf{x} \\[3mm]
-  \oint_\Gamma \left(\tfrac{1}{2} - K_{Y}^{\Gamma}\right) \phi_{1,\Gamma} \zeta ds + \frac{\epsilon_1}{\epsilon_2} \oint_\Gamma V_{Y}^{\Gamma} \lambda_{1,\Gamma} \zeta ds &=&0.
+ \left(  \epsilon_1 \nabla \phi_1, \nabla v \right)_{\Omega_1}  - \left< \epsilon_1 \lambda_2, v \right>_\Gamma &=&   \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right)_{\Omega_1} \\[3mm]
+  \left< \left(\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \phi_1, \zeta \right>_\Gamma + \tfrac{\epsilon_1}{\epsilon_2} \left< V_{Y}^{\Gamma} \lambda_2, \zeta \right>_\Gamma &=&0.
   \end{array}
@@
 % \int_{\Omega_1} \epsilon_1 \nabla \phi_1 : \nabla v ~d\mathbf{x}  - \oint_\Gamma \epsilon_1\partial_n \phi_1 v ds &=   \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)  v ~d\mathbf{x} \\
-% \oint_\Gamma \frac{\phi_{1,\Gamma}}{2} - K_{Y}^{\Gamma}(\phi_{1,\Gamma}) + \frac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \lambda_{1,\Gamma} \right) & = 0
+% \oint_\Gamma \tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \lambda_2^1 \right) & = 0
 %\end{align}
 
-    \item Hybrid FEM-BEM coupling
+We introduce below the matrix formulation. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
+functions of the finite element space $V_{h}^{j}$, %$\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis functions of $W_{h}^{k}$,  
+$\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
+functions of $\Lambda_{h}^{l}$. % and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis functions of  $M_{h}^{m}$
+% $T:\Omega_1 \rightarrow \Gamma$ and $E:\Gamma \rightarrow \Omega_1$ trace and extendable operators respectively.
+We define the following matrices  associated with the corresponding bilinear forms
+\begin{align*}
+A_{\alpha \beta} = \left(\nabla \phi_1, \nabla \phi_1^{\beta} \right)_{\Omega_1}  
+&,&
+M_{\alpha \beta} = \left< \widetilde{\phi}^{\alpha}, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
+K_{\alpha \beta} = \left<K_{Y}^{\Gamma} \phi^{\alpha}_1, \ \lambda^{\beta}_2 \right>_{\Gamma}
+ &,&
+V_{\alpha \beta} = \left<V_{Y}^{\Gamma} \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, 
+\end{align*}
+and vector associated with the corresponding linear form
+\begin{equation*}
+\vec{f}_{\beta} := \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  \phi_1^{\beta} \right)_{\Omega_1}.
+\end{equation*}
+Using the above definition the discrete problem~\eqref{eq:standard_fem_bem} can be written in the following matrix form
+\begin{align*}
+\begin{bmatrix}
+\epsilon_1 A &  - \epsilon_1 M^T \\  
+\left(\tfrac12 I + K \right) &  \tfrac{\epsilon_1}{\epsilon_2} V 
+\end{bmatrix}
+\begin{bmatrix}
+\vec{\phi}_1 \\  
+\vec{\lambda}_2
+\end{bmatrix}
+= 
+\begin{bmatrix}
+\vec{f} \\  
+0
+\end{bmatrix}.
+\end{align*}
+
+{\sffamily \small Hybrid FEM-BEM coupling}
 
@@
 \begin{align*}
- \int_{\Omega_m} \frac{\epsilon_1(\mathbf{x})}{\epsilon_2} \nabla \phi_1 : \nabla v d\mathbf{x} -  \oint_\Gamma \frac{\epsilon_1(\mathbf{x})}{\epsilon_2}  \partial_n \phi_1 v ds
+ \left(  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} \nabla \phi_1, \nabla v \right)_{\Omega_1} -  \left<  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2}  \partial_n \phi_1, v \right>_\Gamma
   & \\
- -  \oint_\Gamma \frac{\epsilon_1(\mathbf{x})}{\epsilon_2} \partial_n v (\phi_1 - \widetilde{\phi}) ds
-  + \tfrac{\tau_F}{h} \oint_\Gamma \frac{\epsilon_1(\mathbf{x})}{\epsilon_2} (\phi_1 - \widetilde{\phi}) v ds & = \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)   v ~d\mathbf{x}.
+ -  \left<  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} \partial_n v, (\phi_1 - \widetilde{\phi}) \right>_\Gamma
+  + \tfrac{\tau_F}{h} \left<  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} (\phi_1 - \widetilde{\phi}), v \right>_\Gamma & = \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),   v \right)_{\Omega_1}.
 \end{align*}
@@
 \begin{align*}
-V_{Y}^{\Gamma} \lambda_{2,\Gamma}  - \left( \tfrac{1}{2}Id + K_{Y}^{\Gamma}  \right) \phi_2 &= - \widetilde{\phi},  \\
- \left( \tfrac{1}{2} Id +  K_{Y}^{',\Gamma}\right)  \lambda_{2,\Gamma} + \left(W_{Y}^{\Gamma} + \tau_B Id\right)  \phi_2  &= \tau_B \widetilde{\phi},
+V_{Y}^{\Gamma} \lambda_2  - \left( \tfrac{1}{2}I + K_{Y}^{\Gamma}  \right) \phi_2 &= - \widetilde{\phi},  \\
+ \left( \tfrac{1}{2} I +  K_{Y}^{'\Gamma}\right)  \lambda_2 + \left(W_{Y}^{\Gamma} + \tau_B I\right)  \phi_2  &= \tau_B \widetilde{\phi},
 \end{align*}
@@
 \begin{equation*}
-\tfrac{\tau_F}{h} \left( \phi_1 - \widetilde{\phi}\right) + \tau_B \left( \phi_2 - \widetilde{\phi}\right)  - \left(\frac{\epsilon_1}{\epsilon_2} \frac{\partial}{\partial \mathbf{n}} \phi_1 -\lambda_{2,\Gamma} \right)  = 0.
+\tfrac{\tau_F}{h} \left( \phi_1 - \widetilde{\phi}\right) + \tau_B \left( \phi_2 - \widetilde{\phi}\right)  - \left(\tfrac{\epsilon_1}{\epsilon_2} \frac{\partial}{\partial \mathbf{n}} \phi_1 -\lambda_2 \right)  = 0.
 \end{equation*}
-\end{itemize}
+
+We introduce below the matrix formulation and algorithm used for implementation. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
+functions of the finite element space $V_{h}^{j}$, $\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis
+functions of $W_{h}^{k}$,  $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
+functions of $\Lambda_{h}^{l}$ and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis
+functions of  $M_{h}^{m}$. We define the following matrices associated with the corresponding bilinear forms
+\begin{center}
+$A_{\alpha \beta} = \left(  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} \nabla \phi^{\alpha}_1, \nabla \phi^{\beta}_1  \right)_{\Omega_1}  - \left< \partial_n \phi^{\alpha}_1 ,  \phi^{\beta}_1 \right>_{\Gamma}   - \left< \phi^{\alpha}_1  , \ \partial_n \phi^{\beta}_1  \right>_{\Gamma}   + \tfrac{\tau_F}{h} \left< \phi^{\alpha}_1 ,\ \phi^{\beta}_1  \right>_{\Gamma}, $                                                                                                                                                                                                                                                                                                        \end{center}
+\vspace{-15pt}
+\begin{align*}
+B_{\alpha \beta} = \left< \widetilde{\phi}^{\alpha}, \ \partial_n \phi^{\beta}_1  \right>_{\Gamma} - \tfrac{\tau_F}{h} \left< \widetilde{\phi}^{\alpha},\ \phi^{\beta}_1  \right>_{\Gamma} 
+ &,& 
+M_{\alpha \beta} =\left< \widetilde{\phi}^{\alpha}, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
+K'_{\alpha \beta} = \left<K_{Y}^{'\Gamma} \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
+ &,&
+V_{\alpha \beta} = \left<V_{Y}^{\Gamma} \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
+W_{\alpha \beta} = \left< W_{Y}^{\Gamma} \phi^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
+ &,&
+K_{\alpha \beta} = -\left<K_{Y}^{\Gamma} \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma},
+\end{align*}
+and vector associated with the corresponding linear form
+\begin{equation*}
+\vec{f}_{\beta} = \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),   \phi^{\beta}_1 \right)_{\Omega_1}.
+\end{equation*}
+
+Using the above definition the discrete problem~\eqref{eq:fem_bem_disctrete} can be written in the following matrix form
+\begin{align*}
+\begin{bmatrix}
+A & 0 & 0 & B \\  
+0 & \tfrac12 I + K &  V & - \tau_B I \\
+0 & \tau_B I + W & \tfrac12 I - K' & M \\
+B^T & - \tau_B I & -M^T & \left(\tfrac{\tau_F}{h} + \tau_B\right) I
+\end{bmatrix}
+\begin{bmatrix}
+\vec{\phi}_1 \\  
+\vec{\phi}_2 \\
+\vec{\lambda}_2 \\
+\vec{\widetilde{\phi}}
+\end{bmatrix}
+= 
+\begin{bmatrix}
+\vec{f} \\  
+0 \\
+0 \\
+0
+\end{bmatrix}.
+\end{align*}
+To solve this system we use the Schur complement and the Steklov-Poincar\'e  operator to eliminate all variables except the hybrid one as follows
+\begin{align}
+\label{eq:Schur}
+\left(\left(\tfrac{\tau_F}{h} + \tau_B\right) I  - B^T A^{-1} B + \begin{bmatrix} \tau_B I & M^T \end{bmatrix} \begin{bmatrix}
+\tfrac12 I + K &  V  \\
+\tau_B I + W & \tfrac12 I - K'
+\end{bmatrix}^{-1}
+\begin{bmatrix}
+ -\tau_B I \\
+M
+\end{bmatrix} 
+\right) \vec{\widetilde{\phi}}
+= -B^T A^{-1} \vec{f}
+\end{align}
+
+In our experiment tests we consider $\mathcal{V}_h\times \Lambda_{h}^{l} \times M_{h}^{m}$ with $j = k = m = l = 1$.
+We let the interface meshes  coincide with the trace mesh of volume mesh on $\Gamma$.
+%As we know from our experiments as well as the one performed in~\cite{MR3945809}, there is a flexibility with the  choice of positive parameter $\tau_B$, hence for simplicity we use $\tau_B = 1$.
+
+For our experiments we use two numerical softwares: FEniCS~\cite{AlnaesBlechta2015a} and Bempp~\cite{SmigajEtAl2015}.
+We use the solution of interior and exterior Dirichlet boundary value problems to construct a Schur complement system~\eqref{eq:Schur}.
+The solution $\vec{\widetilde{\phi}}$ on $\Gamma$ of the eliminated system~\eqref{eq:Schur} is obtained using the nested MINRES method~\cite{}.
+Although one can use direct solvers to solve the interior and exterior Dirichlet boundary value problems, we here used preconditioned iterative solvers suitable for large scale applications.
+The interior Dirichlet boundary value problem is solved by using FEniCS and generalized minimal residual method (GMRES)~\cite{MR848568} without and with incomplete Cholesky preconditioner.
+The discrete exterior problem is solved by using the GMRES without or with mass matrix preconditioner to solve in Bempp the external Dirichlet boundary value problem.
+The tolerance of the iterative solvers is chosen to be not greater the $10^{-6}$. 
+Overall, the algorithm has the following structure:
+\begin{enumerate}
+ \item Assemble the FE weak form in FEniCS and define matrix-vector formulation  using GMRES with tolerance $10^{-8}$
+ \begin{equation*}
+ LHS_{FEM} := B^T A^{-1} B \vec{\widetilde{\phi}} .
+ \end{equation*}
+ \item Assemble BE operators in BEMpp and define matrix-vector formulation 
+using GMRES with tolerance $10^{-8}$
+ \begin{equation*}
+ LHS_{BEM} := \begin{bmatrix} \tau_B I & M^T \end{bmatrix} \begin{bmatrix}
+\tfrac12 I + K &  V  \\
+\tau_B I + W & \tfrac12 I - K'
+\end{bmatrix}^{-1}
+\begin{bmatrix}
+ -\tau_B I \\
+M
+\end{bmatrix} 
+\vec{\widetilde{\phi}}  .
+ \end{equation*}
+ \item Combine matrix-vector formulation of interior and exterior problem in the lhs of~\eqref{eq:Schur}.
+ \item Build rhs of~\eqref{eq:Schur}
+ \begin{equation*}
+ RHS := -B^T A^{-1} \vec{f}.
+ \end{equation*}
+ \item Solve the reduced system using MINRES with tolerance $10^{-6}$.
+ \begin{equation*}
+ \left(\tfrac{\tau_F}{h} + \tau_B\right) I \vec{\widetilde{\phi}}  - LHS_{FEM} + LHS_{BEM} = RHS .
+ \end{equation*}
+ \item Use solution $\vec{\widetilde{\phi}}$ to obtain the solution $\vec{\phi}$ by solving the interior problem or to obtain the solution $\begin{bmatrix} \vec{\phi}_2 \\ \vec{\lambda}_2 \end{bmatrix}$ by solving the exterior problem.
+ \item Calculate the solvation energy.
+\end{enumerate}

### 2022-04-19 results.tex
Work on paper
Methods: adding matrix formulations and changes of notation for consistence.
Results: update of results for more refine volume mesh

@@
 \centering
-   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
+   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error_11.png}
 %    \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
-\caption{Solvation energy for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
+\caption{Solvation energy for arginine with a constant permittivity.
 %maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
@@
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
-  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
+  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time_11.png}
+  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_setup_time_11.png}
 %   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
-\caption{Time-to-solution for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
+\caption{Time-to-solution for arginine with a constant permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems).
 NOTE: x axis differ between top and bottom.
@@
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
-  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
+  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter_11.png}
 %   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
 %   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
-\caption{Iteration count for arginine with a constant permittivity (left: Preconditioned systems, right: No preconditioner).
+\caption{Iteration count for arginine with a constant permittivity.
 %(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations?
@@
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
-    & 2 & -36.239\\
-Standard    & 4  & -33.129 \\
-FEM-BEM    & 8  & -32.673 \\
-    & 16 & -32.293 \\
+    & 2 & -35.688 \\
+Standard    & 4  & -33.304 \\
+FEM-BEM    & 8  & -32.634 \\
+    & 16 & -31.868 \\
 \hline
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
-    & 2 & -34.408\\
-Hybrid    & 4  & -32.815 \\
-FEM-BEM    & 8  & -32.566 \\
-    & 16 & -32.379 \\
+    & 2 & -34.670\\
+Hybrid    & 4  & -33.603 \\
+FEM-BEM    & 8  & -32.822 \\
+    & 16 & -32.072 \\
 \hline
@@
 \centering
-\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
-\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
-% \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
-% \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
-\caption{Time-to-solution and iteration count to compute the solvation energy of arginine with a variable permittivity, using standard and hybrid FEM-BEM coupling. %Can we make this only two plots?
+% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
+% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
+\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
+\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
+\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
+\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using standard and hybrid FEM-BEM coupling.
+%Can we make this only two plots?
 }

### 2022-05-04 methods.tex
removed all references to hybrid FEM-BEM

@@
 \begin{align} \label{eq:phi_reac}
-\phi_{r} = - K_{L}^{\Omega_1}(\phi_1) + V_{L}^{\Omega_1} \left(\frac{\partial}{\partial \mathbf{n}}  \phi_1  \right),
+\phi_{r} = - K_{L}^{\Omega_1}(\phi_1) + V_{L}^{\Omega_1} \left(  \lambda_1  \right),
 \end{align}
 %
-which is valid as long as $\epsilon_1$ is a constant.
+which is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
 
@@
 
-{\sffamily \small Description with constant and variable permittivity}
-
-BEM reduces the dimension of the problem by using the boundary integral equation, hence its popularity as a numerical solution of  the Poisson-Boltzmann equation in molecular electrostatics.
-Unfortunately, such advantage comes with the cost.
-A fundamental solution must be found before the BEM can be applied.
-There are many linear problems for which fundamental solutions are not known.
-For Poisson-Boltzmann equation it is a case if we consider the heterogenous permittivity inside the molecule
+BEM is a popular alternative to solve the Poisson-Boltzmann equation numerically because it reduces the dimension of the problem by using the boundary integral formulation.
+Unfortunately, this advantage comes at a cost: it requires a fundamental solution to be applied.
+There are many linear problems for which fundamental solutions are not known, for example, this is the case for the Poisson-Boltzmann equation with a heterogenous permittivity inside the molecule
+%
    \begin{align} \label{eq:pbe_vp}
@@
 \left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
-\phi_1(\mathbf{x})  = \phi_2(\mathbf{x}),  &\quad \epsilon_1(\mathbf{x})\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  = \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})  \quad \mathbf{x}\in \Gamma.
+\phi_1(\mathbf{x})  = \phi_2(\mathbf{x}),  &\quad \epsilon_1(\mathbf{x})\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  = \epsilon_2(\mathbf{x})\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})  \quad \mathbf{x}\in \Gamma.
 \end{align}
-For such case finite element methods (FEM) are more suitable.
+%
+For such case, a finite element method (FEM) is more suitable.
 
-The coupling of finite element (FEM) and boundary element (BEM) methods is the most widely used approach for solving multi-physical problems on an unbounded domain.
-It allows to take advantage of both methods.
-On the one hand, the BEM approximates only boundary conditions, hence it is commonly used for problems involving infinite or semi-infinite domains.
-On the other hand, the FEM is known for its robustness and universal applicability even for problem of inhomogeneous or non-linear nature.
-And that is why, we present two formulations of FEM-BEM coupling for Poisson-Boltzmann equation.
+The coupling of finite element (FEM) and boundary element (BEM) methods is a widely used approach to solve multi-physical problems on unbounded domains [citation?], as it takes advantage of both methods.
+On one hand, the BEM satifies the infinite boundary conditions exactly when they decay to zero, and only approximates boundary conditions on surfaces, hence, it is commonly used for problems involving infinite or semi-infinite domains.
+On the other hand, the FEM is known for its robustness and universal applicability, even for problems of inhomogeneous or non-linear nature.
 
-{\sffamily \small Standard FEM-BEM coupling approach}
+{\sffamily \small Modeling the solute with a Gaussian-based variable permittivity}\\
 
-   As mentioned before we will use finite element discretisation for internal problem on domain $\Omega_1$ and boundary elements for external domain $\Omega_2$.
-The formulation below can be applied for homogeneous and heterogeneous $\epsilon_1$, hence for simplicity we do not distinguish between these cases in the formulation.
+In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
+A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom,\cite{grant2001smooth} which has shown enhanced accuracy in some applications, like pKa calculations.\cite{li2013dielectric}
+In this setting, we define a density function $\rho$ depending on position $r$ as
+%
+\begin{equation}
+\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|r-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right)
+\end{equation}
+%
+where the product runs over all the atoms of the solute, $R_i$ is the van der Waals radius of atom i, and we used $\sigma$=1. Then, we can compute the permittivity as
+%
+\begin{equation}\label{eq:varying_eps}
+\epsilon := \left(1-\rho \right) \epsilon_1 + \rho\epsilon_2
+\end{equation}
 
-    We start with the variational formulation of the internal problem. Applying integration by parts for first equation of~\eqref{eq:pbe_vp} for every $v \in H_0^1(\Omega_1)$ we have
+As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
+For vacuum calculations, we considered the same distribution of $\epsilon_2$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon$=2. 
+Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff.\cite{li2013dielectric} We did not consider a cutoff in our calculations.
+
+{\sffamily \small The Johnson-N\'ed\'elec FEM-BEM coupling for molecular electrostatics}\\
+
+   We modeled the electrostatic component of solvation of a solute with a Gaussian-varying permittivit (Eq.
+\eqref{eq:varying_eps}) with a finite element discretisation in the internal domain ($\Omega_1$), and boundary elements for external domain ($\Omega_2$).
+We used the Johnson-N\'ed\'elec formulation [citation needed], which is the simplest form of FEM-BEM coupling, and we detail it next.
+
+   We start with the variational formulation of the internal problem. Applying integration by parts for first equation of~\eqref{eq:pbe_vp} for every $v \in H_0^1(\Omega_1)$, we have
+% 
 \begin{equation}
@@
 \end{equation}
+%
 where $v$ is a test function, and $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ and $\left(\varphi,v\right)_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are the inner products on the surface and domain, respectively.
-For external problem we use BEM and the same direct formulation as in~\eqref{eq:direct}, hence we obtain
+For the external problem with BEM, we use the direct formulation from Eq.~\eqref{eq:direct} to obtain
 \begin{align*}
-\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \frac{\partial}{\partial \mathbf{n}} \phi_1 \right) & = 0.
+\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma}  \left(\lambda_1 \right) & = 0.
 \end{align*}
-
-Using the above definition and assuming that $\lambda_2  = \frac{\partial}{\partial \mathbf{n}} \phi_1 $ the coupling problem can be written as follows
+%
+Then, the coupling problem can be written as
+%
 \begin{center}
@@
 
-We introduce below the matrix formulation. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
+This can also be written in matrix form. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
 functions of the finite element space $V_{h}^{j}$, %$\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis functions of $W_{h}^{k}$,  
-$\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
+$\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ --- the vector of canonical basis
 functions of $\Lambda_{h}^{l}$. % and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis functions of  $M_{h}^{m}$
@@
 \end{equation*}
-Using the above definition the discrete problem~\eqref{eq:standard_fem_bem} can be written in the following matrix form
+Using the above definition the discrete problem in Eq.~\eqref{eq:standard_fem_bem} can be written in the following matrix form
 \begin{align*}
@@
 \end{align*}
-
-{\sffamily \small Hybrid FEM-BEM coupling}
-
-  In the previous section, we focused on the standard formulation.
-Now, we propose the weak penalty formulation of a couple problem.
-The discretisation is made by using finite element methods in the domain $\Omega_1$ and boundary integral methods in the domain $\Omega_2$.
-
-    The main difference between the standard and hybrid FEM-BEM formulations is addition of hybrid variable $\widetilde{\phi}$ that is a trace of $\phi_1$ and $\phi_2$ on the interface $\Gamma$ ($\widetilde{\phi} = \phi_1 = \phi_2$ on  $\Gamma$).
-Both FEM and BEM subproblems are modified to include the hybrid variable by adding some terms that enforce the equality of it with the trace of $\phi_1$ and $\phi_2$.
-
-    The standard formulation of interior problem~\eqref{eq:fem} can be rewritten as follows
-\begin{align*}
- \left(  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} \nabla \phi_1, \nabla v \right)_{\Omega_1} -  \left<  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2}  \partial_n \phi_1, v \right>_\Gamma
-  & \\
- -  \left<  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} \partial_n v, (\phi_1 - \widetilde{\phi}) \right>_\Gamma
-  + \tfrac{\tau_F}{h} \left<  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} (\phi_1 - \widetilde{\phi}), v \right>_\Gamma & = \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),   v \right)_{\Omega_1}.
-\end{align*}
-With every iteration we are solving above problem for given $\widetilde{\phi}$ and hence obtaining the solution $ \phi_1$.
-%We are using FEniCS finite element library, hence the above formulation is more sumilar to the implementation.
-
-In the case of exterior problem of~\eqref{eq:pbe_vp} we use Yukawa kernel and 
-%matrix form, for clarity and similarity with BEMpp implementation.
-In this case we consider linearised formulation of the Poisson-Boltzman equation that means our operators are built as for modified Helmholtz equation with wavenumber $\kappa$.
-for given $\widetilde{\phi}$, with each iteration we are solving the following system
-\begin{align*}
-V_{Y}^{\Gamma} \lambda_2  - \left( \tfrac{1}{2}I + K_{Y}^{\Gamma}  \right) \phi_2 &= - \widetilde{\phi},  \\
- \left( \tfrac{1}{2} I +  K_{Y}^{'\Gamma}\right)  \lambda_2 + \left(W_{Y}^{\Gamma} + \tau_B I\right)  \phi_2  &= \tau_B \widetilde{\phi},
-\end{align*}
-where $K'$ and $W$ are the adjoint double-layer potentials and hypersingular operator for the Yukawa kernel.
-
-Both, the interior and exterior problems have unique solutions for given $\widetilde{\phi}$. In order to find $\widetilde{\phi}$ we solve the following problem on $\Gamma$
-\begin{equation*}
-\tfrac{\tau_F}{h} \left( \phi_1 - \widetilde{\phi}\right) + \tau_B \left( \phi_2 - \widetilde{\phi}\right)  - \left(\tfrac{\epsilon_1}{\epsilon_2} \frac{\partial}{\partial \mathbf{n}} \phi_1 -\lambda_2 \right)  = 0.
-\end{equation*}
-
-We introduce below the matrix formulation and algorithm used for implementation. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
-functions of the finite element space $V_{h}^{j}$, $\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis
-functions of $W_{h}^{k}$,  $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
-functions of $\Lambda_{h}^{l}$ and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis
-functions of  $M_{h}^{m}$. We define the following matrices associated with the corresponding bilinear forms
-\begin{center}
-$A_{\alpha \beta} = \left(  \tfrac{\epsilon_1(\mathbf{x})}{\epsilon_2} \nabla \phi^{\alpha}_1, \nabla \phi^{\beta}_1  \right)_{\Omega_1}  - \left< \partial_n \phi^{\alpha}_1 ,  \phi^{\beta}_1 \right>_{\Gamma}   - \left< \phi^{\alpha}_1  , \ \partial_n \phi^{\beta}_1  \right>_{\Gamma}   + \tfrac{\tau_F}{h} \left< \phi^{\alpha}_1 ,\ \phi^{\beta}_1  \right>_{\Gamma}, $                                                                                                                                                                                                                                                                                                        \end{center}
-\vspace{-15pt}
-\begin{align*}
-B_{\alpha \beta} = \left< \widetilde{\phi}^{\alpha}, \ \partial_n \phi^{\beta}_1  \right>_{\Gamma} - \tfrac{\tau_F}{h} \left< \widetilde{\phi}^{\alpha},\ \phi^{\beta}_1  \right>_{\Gamma} 
- &,& 
-M_{\alpha \beta} =\left< \widetilde{\phi}^{\alpha}, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
-K'_{\alpha \beta} = \left<K_{Y}^{'\Gamma} \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
- &,&
-V_{\alpha \beta} = \left<V_{Y}^{\Gamma} \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
-W_{\alpha \beta} = \left< W_{Y}^{\Gamma} \phi^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
- &,&
-K_{\alpha \beta} = -\left<K_{Y}^{\Gamma} \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma},
-\end{align*}
-and vector associated with the corresponding linear form
-\begin{equation*}
-\vec{f}_{\beta} = \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),   \phi^{\beta}_1 \right)_{\Omega_1}.
-\end{equation*}
-
-Using the above definition the discrete problem~\eqref{eq:fem_bem_disctrete} can be written in the following matrix form
-\begin{align*}
-\begin{bmatrix}
-A & 0 & 0 & B \\  
-0 & \tfrac12 I + K &  V & - \tau_B I \\
-0 & \tau_B I + W & \tfrac12 I - K' & M \\
-B^T & - \tau_B I & -M^T & \left(\tfrac{\tau_F}{h} + \tau_B\right) I
-\end{bmatrix}
-\begin{bmatrix}
-\vec{\phi}_1 \\  
-\vec{\phi}_2 \\
-\vec{\lambda}_2 \\
-\vec{\widetilde{\phi}}
-\end{bmatrix}
-= 
-\begin{bmatrix}
-\vec{f} \\  
-0 \\
-0 \\
-0
-\end{bmatrix}.
-\end{align*}
-To solve this system we use the Schur complement and the Steklov-Poincar\'e  operator to eliminate all variables except the hybrid one as follows
-\begin{align}
-\label{eq:Schur}
-\left(\left(\tfrac{\tau_F}{h} + \tau_B\right) I  - B^T A^{-1} B + \begin{bmatrix} \tau_B I & M^T \end{bmatrix} \begin{bmatrix}
-\tfrac12 I + K &  V  \\
-\tau_B I + W & \tfrac12 I - K'
-\end{bmatrix}^{-1}
-\begin{bmatrix}
- -\tau_B I \\
-M
-\end{bmatrix} 
-\right) \vec{\widetilde{\phi}}
-= -B^T A^{-1} \vec{f}
-\end{align}
-
-In our experiment tests we consider $\mathcal{V}_h\times \Lambda_{h}^{l} \times M_{h}^{m}$ with $j = k = m = l = 1$.
-We let the interface meshes  coincide with the trace mesh of volume mesh on $\Gamma$.
-%As we know from our experiments as well as the one performed in~\cite{MR3945809}, there is a flexibility with the  choice of positive parameter $\tau_B$, hence for simplicity we use $\tau_B = 1$.
-
-For our experiments we use two numerical softwares: FEniCS~\cite{AlnaesBlechta2015a} and Bempp~\cite{SmigajEtAl2015}.
-We use the solution of interior and exterior Dirichlet boundary value problems to construct a Schur complement system~\eqref{eq:Schur}.
-The solution $\vec{\widetilde{\phi}}$ on $\Gamma$ of the eliminated system~\eqref{eq:Schur} is obtained using the nested MINRES method~\cite{}.
-Although one can use direct solvers to solve the interior and exterior Dirichlet boundary value problems, we here used preconditioned iterative solvers suitable for large scale applications.
-The interior Dirichlet boundary value problem is solved by using FEniCS and generalized minimal residual method (GMRES)~\cite{MR848568} without and with incomplete Cholesky preconditioner.
-The discrete exterior problem is solved by using the GMRES without or with mass matrix preconditioner to solve in Bempp the external Dirichlet boundary value problem.
-The tolerance of the iterative solvers is chosen to be not greater the $10^{-6}$. 
-Overall, the algorithm has the following structure:
-\begin{enumerate}
- \item Assemble the FE weak form in FEniCS and define matrix-vector formulation  using GMRES with tolerance $10^{-8}$
- \begin{equation*}
- LHS_{FEM} := B^T A^{-1} B \vec{\widetilde{\phi}} .
- \end{equation*}
- \item Assemble BE operators in BEMpp and define matrix-vector formulation 
-using GMRES with tolerance $10^{-8}$
- \begin{equation*}
- LHS_{BEM} := \begin{bmatrix} \tau_B I & M^T \end{bmatrix} \begin{bmatrix}
-\tfrac12 I + K &  V  \\
-\tau_B I + W & \tfrac12 I - K'
-\end{bmatrix}^{-1}
-\begin{bmatrix}
- -\tau_B I \\
-M
-\end{bmatrix} 
-\vec{\widetilde{\phi}}  .
- \end{equation*}
- \item Combine matrix-vector formulation of interior and exterior problem in the lhs of~\eqref{eq:Schur}.
- \item Build rhs of~\eqref{eq:Schur}
- \begin{equation*}
- RHS := -B^T A^{-1} \vec{f}.
- \end{equation*}
- \item Solve the reduced system using MINRES with tolerance $10^{-6}$.
- \begin{equation*}
- \left(\tfrac{\tau_F}{h} + \tau_B\right) I \vec{\widetilde{\phi}}  - LHS_{FEM} + LHS_{BEM} = RHS .
- \end{equation*}
- \item Use solution $\vec{\widetilde{\phi}}$ to obtain the solution $\vec{\phi}$ by solving the interior problem or to obtain the solution $\begin{bmatrix} \vec{\phi}_2 \\ \vec{\lambda}_2 \end{bmatrix}$ by solving the exterior problem.
- \item Calculate the solvation energy.
-\end{enumerate}

### 2022-05-04 results.tex
removed all references to hybrid FEM-BEM

@@
 
-As a more realistic test, we assessed the performance of the standard and hybrid FEM-BEM coupling techniques against a purely BEM implementation for arginine [cite arg]. 
-We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper [Rocchia].
-These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer [pygamer], which invoked \texttt{tetgen} with the string \texttt{abcd}.
-For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
+As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine [cite arg]. 
+We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}
+These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer,~\cite{lee2020open} which invoked \texttt{tetgen} [citation] with the string \texttt{abcd}.
 
 The solvation energy computed with the three schemes is presented by Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
-Then, Figure \ref{fig:arg_constant_time} compares the time-to-solution, and shows that using only BEM outperforms both coupled FEM-BEM approaches.
-Even though hybrid FEM-BEM is slower than standard FEM-BEM in Figure \ref{fig:arg_constant_time}, the iteration count in Figure \ref{fig:arg_constant_iter} shows that hybrid FEM-BEM needs less iterations (can we compare them?).
-This behavior is promising going towards larger problems, specially since the hybrid approach allows for more flexibility in the choice of preconditioner.
-
-\begin{itemize}
-\item Do we really need to compute the vacuum case numerically? We should be able to do it analytically, right?
-\item Run BEM-BEM with the non regularized version.
-\end{itemize}
+Then, Figure \ref{fig:arg_constant_time} compares the time-to-solution, and shows that using only BEM outperforms the coupled FEM-BEM approach.
 
@@
 \caption{Time-to-solution for arginine with a constant permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems). 
-NOTE: x axis differ between top and bottom.
+%NOTE: x axis differ between top and bottom.
 Also, should we include preconditioned vs non preconditioned?
@@
 
-In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
-A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom [earlier papers], which has shown enhanced accuracy in some applications, like binding energy calculations (check) [Alexov].
-In this setting, we define a density function $\rho$ depending on position $r$ as
-%
-\begin{equation}
-\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|r-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right)
-\end{equation}
-%
-where the product is over the atoms of the solute, $R_i$ is the vdW
-radius of atom i and we used $\sigma$=1. Then, we can compute the permittivity as
-%
-\begin{equation}
-\epsilon := \left(1-\rho \right) \epsilon_1 + \rho\epsilon_2
-\end{equation}
-%
-
-We used Equation \eqref{eq:epsilon_gauss} to generate dielectric maps, which we ran on APBS~\cite{BakerETal2001} for comparison. 
-We chose APBS because it provides an easy interface to control dielectric maps, in order to make sure that they agree with the ones imposed in our FEM-BEM coupled approach.
-As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically (MOVE TO METHODS).
-For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, however, the solvent permittivity was set to $\epsilon$=2. 
-Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff [Alexov]. 
-We did not consider a cutoff in our calculations, but this does not affect our validation exercise.
+We used Equation \eqref{eq:varying_eps} to generate dielectric maps, which we ran on APBS~\cite{BakerETal2001} for comparison. 
+We chose APBS because it provides an easy interface to control dielectric maps, in order to ensure their agreement with the maps imposed in our FEM-BEM coupled approach.
 
@@
 
-Table \ref{table:arg_variable} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approaches.
-We can see that they are both converging to equivalent values, where the finest meshes agree up to the third significant figure.
+Table \ref{table:arg_variable} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approach.
+We can see that they are both converging to equivalent values, where the finest meshes agree up to 1.5\% (0.5 kcal/mol).
 
 Figure \ref{fig:arg_variable} contains performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
-Similar to the case with constant permittivity, although the hybrid approach requires less iterations (are we counting them appropriately?
-meaning there are external and internal iterations), the total time to solution is less for the standard approach.
-This means that each iteration of hybrid FEM-BEM is slower than the standard counterpart.
 
@@
     & 2 & -35.688 \\
-Standard    & 4  & -33.304 \\
-FEM-BEM    & 8  & -32.634 \\
+FEM-BEM    & 4  & -33.304 \\
+coupling    & 8  & -32.634 \\
     & 16 & -31.868 \\
@@
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
-    & 2 & -34.670\\
-Hybrid    & 4  & -33.603 \\
-FEM-BEM    & 8  & -32.822 \\
-    & 16 & -32.072 \\
-\hline
+%    & 2 & -34.670\\
+%Hybrid    & 4  & -33.603 \\
+%FEM-BEM    & 8  & -32.822 \\
+%    & 16 & -32.072 \\
+%\hline
 \end{tabular}
-\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the standard and hybrid FEM-BEM approaches, and APBS. Add performance result?}
+\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS.
+The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.
+Add performance result?}
 \label{table:arg_variable}
@@
 \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
-\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using standard and hybrid FEM-BEM coupling.
+\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.
 %Can we make this only two plots?
@@
 
-So far, in all the small structures that we have tested, the standard approach has been more efficient than the hybrid one.
-However, the fact that there are better preconditioning strategies for the hybrid approach indicates that it may become faster for larger test cases, where conditioning of the linear system is usually more important.
-In this section, we compare both approaches for larger structures.
+So far, we have only tested the FEM-BEM coupled approach with small structures. Here, we study its behavior with larger structures to evaluate its applicability in more realistic settings.

### 2022-05-09 main.tex
added citations in methods
minor change

@@
 (75 words.) Images for the graphical Table of Contents should capture the essence of a paper, displaying a figure, plot, or scheme that is central to the theme of the manuscript.
-The text of the graphical Table of Contents is meant for the non-specialist and should ideally contain no obscure jargon or mathematical symbols / equations, but should attempt to convey the gist of the paper in everyday terms, while remaining consistent with accepted standards of scientific literature.
+The text of the graphical Table of Contents is meant for the non-specialist and should ideally contain no obscure jargon or mathematical symbols / equations, but should attempt to convey the gist of the paper in everyday terms while remaining consistent with accepted standards of scientific literature.
 \end{minipage}
@@
 
-%\bibliography{bibtexrefs}   % Produces the bibliography via BibTeX.
+\bibliography{main}   % Produces the bibliography via BibTeX.
 
-\begin{thebibliography}{99}
-
-\bibitem{Coulson}
-Coulson, C. A., Rev. Mod. Phys., \textbf{1960}, 32,170-177.
-\bibitem{Malrieu}
-Malrieu, J.-P., J. Mol. Struct., \textbf{1998}, 424, 1-2,83-91.
-\bibitem{Shaik}
-Shaik, S., New. J. Chem., \textbf{2007}, 31,2015-2028.
-\bibitem{Hoffmann}
-Hoffman, R., Schleyer, P. v. R., Schaefer III, H. F., \textbf{2008}, 47, 7164-7167.
-\bibitem{Perdew}
-Perdew, J. P., Ruzsinszky, A., Constantin, L., Sun, J., Csonka, G., J. Chem. Theory Comput., \textbf{2009}, 5, 902-908.
-\bibitem{Koros}
-Koros, W. J.; Chern, R. T. In Handbook of Separation Process Technology; Rousseau, E. D.; Russell, B., Eds.; Wiley: New York, \textbf{1987}; Vol. 2, Chapter 20, pp 34-45.
-\end{thebibliography}
+%\begin{thebibliography}{99}
+%
+%
+%\bibitem{Coulson}
+%Coulson, C. A., Rev. Mod. Phys., \textbf{1960}, 32,170-177.
+%\bibitem{Malrieu}
+%Malrieu, J.-P., J. Mol. Struct., \textbf{1998}, 424, 1-2,83-91.
+%\bibitem{Shaik}
+%Shaik, S., New. J. Chem., \textbf{2007}, 31,2015-2028.
+%\bibitem{Hoffmann}
+%Hoffman, R., Schleyer, P. v. R., Schaefer III, H. F., \textbf{2008}, 47, 7164-7167.
+%\bibitem{Perdew}
+%Perdew, J. P., Ruzsinszky, A., Constantin, L., Sun, J., Csonka, G., J. Chem. Theory Comput., \textbf{2009}, 5, 902-908.
+%\bibitem{Koros}
+%Koros, W. J.; Chern, R. T. In Handbook of Separation Process Technology; Rousseau, E. D.; Russell, B., Eds.; Wiley: New York, \textbf{1987}; Vol. 2, Chapter 20, pp 34-45.
+%\end{thebibliography}
 

### 2022-10-03 results.tex
Part of the work on 'Result' section

@@
-This section presents verification and performance results of the standard and hybrid FEM-BEM coupling schemes, for molecules modeled as cavities with constant and varying permittivity.
+This section presents the verification and performance results of the presented FEM-BEM coupling schemes, for molecules modeled as cavities with constant and varying permittivity.
 With a constant permittivity inside the molecule, we tested convergence against an analytical expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
 We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
-The final tests show the scaling of the standard and hybrid FEM-BEM coupling, as the molecule size grows.
+The final tests show the scaling of the FEM-BEM coupling, as the molecule size grows.
 
@@
 In this case, we considered a spherical cavity of radius $R=2$ \AA, with three charges ($q_1$=1, $q_2$=1, and $q_3$=0.75) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
-Figure \ref{fig:error_sphere} shows the error convergence of the standard and hybrid FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.3375$ kcal/mol).
+Figure \ref{fig:error_sphere} shows the error convergence of the FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.3375$ kcal/mol). 
 In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
-For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
+%For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
 The error in Figure \ref{fig:error_sphere} decays linearly with the surface area, which agrees with the expected convergence for P1 elements, indicating a correct implementation of the numerical scheme.
@@
 
-The solvation energy computed with the three schemes is presented by Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
-Then, Figure \ref{fig:arg_constant_time} compares the time-to-solution, and shows that using only BEM outperforms the coupled FEM-BEM approach.
+The solvation energy computed with the two schemes is presented by Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
+Then, Figure \ref{fig:arg_constant_time_iter} compares the iteration count and time-to-solution.
+The left plot shows that using only BEM outperforms the coupled FEM-BEM approach in terms of iterations count.
+However, if we look at the total time that solvers take to obtain the solution, we can see the advantage of using the FEM-BEM coupling.
+The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation.
 
@@
 \centering
-   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error_11.png}
+   \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_error_11.png}
 %    \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
@@
 \centering
-%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter.png}
-  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time_11.png}
-  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_setup_time_11.png}
-%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_time.png}
-\caption{Time-to-solution for arginine with a constant permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems). 
+   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter_11.png}
+%  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time_11.png}
+%  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_setup_time_11.png}
+  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_total_time_11.png}
+  \caption{Iteration count (left) and time-to-solution (right) for arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
 %NOTE: x axis differ between top and bottom.
@@
 }
-\label{fig:arg_constant_time}
+\label{fig:arg_constant_time_iter}
 \end{figure}
 
-\begin{figure}
-\centering
-%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
-  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter_11.png}
-%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
-%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
-\caption{Iteration count for arginine with a constant permittivity.
+%\begin{figure}
+%\centering
+%%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
+%  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter_11.png}
+%%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
+%%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
+%\caption{Iteration count for arginine with a constant permittivity.
 %(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations?
 maybe we should present the total count?
-}
-\label{fig:arg_contant_iter}
-\end{figure}
+%}
+%\label{fig:arg_contant_iter}
+%\end{figure}
 

### 2022-10-04 main.tex
added some references, and update result section
 Do not worry if you overwrite Methods, since I just corrected one equation.
To main I just added authors, nothing important.

@@
 \title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
-\author{Author A\thanks{Department of Biology, University 1, ...}, Author B\thanks{Department of Chemistry, University 2, ...}, Author C \thanks{Department of Physics, University 3, ...} Author D\thanks{Department of Mathematics, University College London, ...}}
+\author{Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Christopher D.
+Cooper\thanks{Department of Mechanical Engineering, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}, Matthew W.
+Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}}
 
@@
 (75 words.) Images for the graphical Table of Contents should capture the essence of a paper, displaying a figure, plot, or scheme that is central to the theme of the manuscript.
-The text of the graphical Table of Contents is meant for the non-specialist and should ideally contain no obscure jargon or mathematical symbols / equations, but should attempt to convey the gist of the paper in everyday terms while remaining consistent with accepted standards of scientific literature.
+The text of the graphical Table of Contents is meant for the non-specialist and should ideally contain no obscure jargon or mathematical symbols / equations, but should attempt to convey the gist of the paper in everyday terms, while remaining consistent with accepted standards of scientific literature.
 \end{minipage}

### 2022-10-04 methods.tex
minor edit
Adding permittivity scaling to direct formulation (4)
Adding permittivity scaling to direct formulation (7)
added some references, and update result section
 Do not worry if you overwrite Methods, since I just corrected one equation.
To main I just added authors, nothing important.

@@
 \phi_{1}(\mathbf{x}_{\Omega_1})+ K_{L}^{\Omega_1}\phi_1 -  V_{L}^{\Omega_1} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Omega_1} - \mathbf{x}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
-\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
+\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
 \end{align}
@@
 \tfrac{\phi_1}{2}+ K_{L}^{\Gamma}\phi_1 -  V_{L}^{\Gamma} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Gamma} - \mathbf{x}_k|} \nonumber \\
-\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 + V_{Y}^{\Gamma} \lambda_2 & = 0
+\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 +  \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Gamma} \lambda_2 & = 0
 \end{align}
@@
 
-As $\epsilon_2$ is variable, Equation \eqref{eq:phi_coulomb} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
+As $\epsilon_2$ is variable, Equation \eqref{eq:phic} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
 For vacuum calculations, we considered the same distribution of $\epsilon_2$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon$=2. 

### 2022-10-04 results.tex
added some references, and update result section
 Do not worry if you overwrite Methods, since I just corrected one equation.
To main I just added authors, nothing important.

@@
 Figure \ref{fig:error_sphere} shows the error convergence of the FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.3375$ kcal/mol). 
-In these runs, the FEM mesh was generated using Bempp (check?) from a surface discretization with W, X, Y, and Z vertices per \AA$^2$ on the SES, which was also used for the BEM runs. 
+In these runs, the FEM mesh was generated using GMSH~\cite{geuzaine2009gmsh}. 
+%Bempp (check?) from a surface discretization 
+with 1, 2, 4, and 8 vertices per \AA$^2$ on the SES, the surface mesh of this volume one was also used for the BEM runs. 
 %For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
@@
 
-As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine [cite arg]. 
+As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine (the structure of arginine taken from the protein data bank \cite{bank}).
 We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}

### 2022-10-13 intro.tex
added refs and text to intro

@@
 In biologically relevant settings, the structure and function of biomolecules is largely determined by the surrounding water, which usually contains salt. 
-To describe these systems accurately, we need to account for the solvent correctly, which has given rise to a wide range of models \cite{onufriev2018water}
-Highly detailed models consider every water molecule and salt ion explicitly, however, there are approximated models that use continuum theory to represent this ionic solution, knwon as implicit-solvent models\cite{RouxSimonson1999,DecherchiETal2015}.
+To describe these systems accurately, we need to account for the solvent correctly, which has given rise to a wide range of models.\cite{onufriev2018water}
+Highly detailed models consider every water molecule and salt ion explicitly, however, there are approximated models that use continuum theory to represent this ionic solution, known as implicit-solvent models.\cite{RouxSimonson1999,DecherchiETal2015}
 In the case of electrostatics, the implicit-solvent model is mathematically characterized by the Poisson-Boltzmann equation (PBE)\cite{Baker2004,Bardhan2012}, which is widely used to compute solvation free energies and mean-field potentials.
@@
 
-The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{AltmanBardhanWhiteTidor09,LuETal2006,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
+The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{boschitsch2002fast,AltmanBardhanWhiteTidor09,LuETal2006,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
 In particular, the boundary element method (BEM) has proven to be very efficient for high accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.
@@
 
-This article presents a methodology to overcome some of those limitations, by coupling finite and boundary elements methods (FEM-BEM coupling).
-This approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the dissolved molecule.
+This article presents a methodology to overcome some of those limitations, by coupling finite and boundary elements methods.
+The Poisson-Boltzmann equation has been solved with hybrid numerical methods in the past, for example, coupling finite difference with boundary elements\cite{boschitsch2004hybrid}, to solve the nonlinar equation, and finite elements,\cite{xie2016new,ying2018hybrid} to model the size-modificed Poisson-Boltzmann equation.
+To the best of our knowledge, this is the first time finite and boundary elements are combined in this application.
+Our approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the dissolved molecule.

### 2022-10-13 main.tex
Cleaning references
I put accessed November 4, 2020, but I do not know when did we take Arginine data.

@@
 
-\clearpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FIGURE CAPTIONS
-
-%%%%% FIGURE ---- cc.eps
-\begin{figure}
-\caption{\label{cc} Place Figure 1 caption here.
+%\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% FIGURE CAPTIONS
+%
+%%%%%% FIGURE ---- cc.eps
+%\begin{figure}
+%\caption{\label{cc} Place Figure 1 caption here.
 In the case of reproduced figures in review articles, you must obtain the publisher's permission and state a suitable notice here along with a citation.}
-\end{figure}
-
-\begin{figure}
-\caption{\label{fig2} Place Figure 2 caption here.
+%\end{figure}
+%
+%\begin{figure}
+%\caption{\label{fig2} Place Figure 2 caption here.
 Figures should be uploaded as individual files, preferably .tif or .eps files, at high enough resolution (600 to 1200 dpi) to ensure clarity.
@@
 For high quality illustrations, we highly recommend the use of the TikZ package.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FIGURE FILES
-
-\clearpage
-
-%\vspace*{0.1in}   %%% FIGURE 1
-%\begin{center}
-%\includegraphics[width=0.2\columnwidth,keepaspectratio=true]{cc.eps}
-%\end{center}
-\vspace{0.25in}
-\hspace*{3in}
-{\Large
-\begin{minipage}[t]{3in}
-\baselineskip = .5\baselineskip
-Figure 1 \\
-Author A, Author B, Author C, Author D \\
-J.\ Comput.\ Chem.
-\end{minipage}
-}
-
-\clearpage
-
-\begin{table}
-\begin{tabular}{|c|c|c|c|}\hline
-\textbf{Quantity} & \textbf{Calculated} & \textbf{Observed} & \textbf{Error} \\ \hline
-  Density & 5.3 & 6.3 & Within limits \\ \hline
-  Optical magnification & 8.3 & 90.9 & Utterly unacceptable\! \\ \hline
-\end{tabular}
-\caption{\label{tbl1} Place table caption here.}
-\end{table}
+%\end{figure}
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% FIGURE FILES
+%
+%\clearpage
+%
+%%\vspace*{0.1in}   %%% FIGURE 1
+%%\begin{center}
+%%\includegraphics[width=0.2\columnwidth,keepaspectratio=true]{cc.eps}
+%%\end{center}
+%\vspace{0.25in}
+%\hspace*{3in}
+%{\Large
+%\begin{minipage}[t]{3in}
+%\baselineskip = .5\baselineskip
+%Figure 1 \\
+%Author A, Author B, Author C, Author D \\
+%J.\ Comput.\ Chem.
+%\end{minipage}
+%}
+%
+%\clearpage
+%
+%\begin{table}
+%\begin{tabular}{|c|c|c|c|}\hline
+%\textbf{Quantity} & \textbf{Calculated} & \textbf{Observed} & \textbf{Error} \\ \hline
+%  Density & 5.3 & 6.3 & Within limits \\ \hline
+%  Optical magnification & 8.3 & 90.9 & Utterly unacceptable\! \\ \hline
+%\end{tabular}
+%\caption{\label{tbl1} Place table caption here.}
+%\end{table}
 

### 2022-10-13 intro.tex
added a few more refs and modifications to intro

@@
 
-The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{boschitsch2002fast,AltmanBardhanWhiteTidor09,LuETal2006,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
+The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
 In particular, the boundary element method (BEM) has proven to be very efficient for high accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.
@@
 This article presents a methodology to overcome some of those limitations, by coupling finite and boundary elements methods.
-The Poisson-Boltzmann equation has been solved with hybrid numerical methods in the past, for example, coupling finite difference with boundary elements\cite{boschitsch2004hybrid}, to solve the nonlinar equation, and finite elements,\cite{xie2016new,ying2018hybrid} to model the size-modificed Poisson-Boltzmann equation.
+FEM-BEM coupling is a popular technique in the context of mixed linear-nonlinear models,\cite{carstensen1995coupling,aurada2013classical} fracture mechanics,\cite{aour2007coupled} fluid-structure interaction,\cite{estorff1991fem} acoustics,\cite{hiptmair2006stabilized} and electromagnetics.\cite{matsuoka1988calculation,hiptmair2008stabilized,bruckner20123d}
+On the other hand, the PBE has been solved with hybrid numerical methods in the past, for example, coupling finite difference with boundary elements,\cite{boschitsch2004hybrid} to solve the nonlinear PBE in a specific region, and finite elements,\cite{xie2016new,ying2018hybrid} to implement modifications to the PBE model ({\it ie.} the size-modified PBE).
 To the best of our knowledge, this is the first time finite and boundary elements are combined in this application.
-Our approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the dissolved molecule.
+Our approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the solute molecule.

### 2022-10-13 results.tex

@@
 All runs were done on XX computer with YY specifications.
+
+\section*{\sffamily \Large Software environment}
+
+For the finite element computations we use the software package FEniCSx while for the boundary element computations we use Bempp-cl together with Exafmm-t.
+FEniCSx is the successor of the widely used FEniCS finite element library.
+It provides a convenient Python interface, in which problems are described using UFL (Unified Form Language), a convenient domain specific language specifically designed for finite element discretisations of partial differential equations.
+During assembly the UFL description is transformed into efficient low-level C++ code and just-in-time compiled.
+Bempp-cl is a Python package that uses low-level OpenCL kernels written in C99 to provide optimised assembly routines.
+For moderate discretisation sizes up to a few ten thousand elements, the built-in dense assembly routines are highly efficient.
+
+For very large grid sizes the user can enable FMM assembly which internally is handled in Bempp-cl through an interface to the Exafmm-t FMM library.
+For $N$ surface elements this reduces the memory and computational complexity from $\mathcal{O}(N^2)$ in the dense assembly case to $\mathcal{O}(N)$ in the FMM case, making large boundary element problems tractable on standard workstations.
+
+To couple FEniCSx with Bempp-cl we load a volume mesh with FEniCSx.
+We then export the corresponding boundary mesh into Bempp-cl and assemble the boundary spaces there.
+Bempp-cl provides numerical trace operators that can translate from the degree of freedom (dof) representation in FEniCSx to the dof representation in Bempp-cl.
+The corresponding translation work is handled opaquely and the user only needs to deal with high-level interfaces of FEniCSx operators, Bempp-cl operators, and trace operators.
+FMM assembly fits automatically into this framework and can be enabled or disabled as simple configuration option.
+
+Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (PROVIDE LINK), and all codes used in this sections are simple Jupyter Notebooks that can be reproducibly executed in this provided Docker image.
 

### 2022-10-13 intro.tex
added text to intro and cut down bem-bem coupling in methods

@@
 
-This article presents a methodology to overcome some of those limitations, by coupling finite and boundary elements methods.
+The present article describes a methodology to overcome some of those limitations, by coupling finite and boundary elements methods.
+This approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the solute molecule.
 FEM-BEM coupling is a popular technique in the context of mixed linear-nonlinear models,\cite{carstensen1995coupling,aurada2013classical} fracture mechanics,\cite{aour2007coupled} fluid-structure interaction,\cite{estorff1991fem} acoustics,\cite{hiptmair2006stabilized} and electromagnetics.\cite{matsuoka1988calculation,hiptmair2008stabilized,bruckner20123d}
-On the other hand, the PBE has been solved with hybrid numerical methods in the past, for example, coupling finite difference with boundary elements,\cite{boschitsch2004hybrid} to solve the nonlinear PBE in a specific region, and finite elements,\cite{xie2016new,ying2018hybrid} to implement modifications to the PBE model ({\it ie.} the size-modified PBE).
+On the other hand, the PBE has been solved with hybrid numerical methods in the past, for example, by coupling finite difference with boundary elements\cite{boschitsch2004hybrid} or finite elements,\cite{xie2016new,ying2018hybrid} which were mainly used to solve the nonlinear PBE in a specific region, and to implement modifications to the PBE model ({\it ie.} the size-modified PBE).
 To the best of our knowledge, this is the first time finite and boundary elements are combined in this application.
-Our approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the solute molecule.
+
+Here we prototype this principle with the simplest implementation possible: a Johnson-N\'ed\'elec\cite{johnson1980coupling} coupling, mass-matrix and diagonal preconditioning, and no accceleration algorithms ({\it ie.} fast multipole method) or distributed memory execution.
+This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in the software libraries used in this work, in particular, Bempp-cl and FEniCSx.
+These libraries are designed for ease-of-use through a simple Python interface, making them ideal tools to explore and improve computational efficiency, towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}
+We hope this work will inspire research along these lines.

### 2022-10-13 methods.tex
added text to intro and cut down bem-bem coupling in methods

@@
 There are several possible boundary integral formulations of Equation \eqref{eq:pbe}.~\cite{search2022towards} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
-Here, we use the better conditioned formulation presented by Lu and co-workers.~\cite{LuETal2006,LuETal2009,debuhr2016dashmm}
-Applying Green's second identity to Equation \eqref{eq:pbe} we get 
-%
-\begin{align} \label{eq:volume_potential}
-\phi_{1}(\mathbf{x}_{\Omega_1})+ K_{L}^{\Omega_1}\phi_1 -  V_{L}^{\Omega_1} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Omega_1} - \mathbf{x}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
-\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
-\end{align}
-%
-where $\mathbf{x}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
-For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
-$K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
-%
-\begin{align}\label{eq:single_double}
-V^D \varphi (\mathbf{x}) = \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-K^D \varphi (\mathbf{x}) = \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
-\end{align}
-%
-where $D \in \{\Omega_1, \Omega_2, \Gamma\}$, $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and 
-%
-\begin{align}\label{eq:green_func}
-g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
-g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
-\end{align}
-%
-are the free-space Green's function of the Laplace and linearized Poisson-Boltzmann equations, respectively.
-
-If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{x}_{\Omega}$ approaches $\Gamma$, we get
-%
-\begin{align} \label{eq:direct}
-\tfrac{\phi_1}{2}+ K_{L}^{\Gamma}\phi_1 -  V_{L}^{\Gamma} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Gamma} - \mathbf{x}_k|} \nonumber \\
-\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 +  \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Gamma} \lambda_2 & = 0
-\end{align}
-%
-The {\it direct} formulation\cite{YoonLenhoff1990} couples the two expressions of Eq.
-\eqref{eq:direct} on $\Gamma$, considering the interface conditions.
-Even though this formulation is poorly conditioned with respect to the mesh size, it can still model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,MartinezETal2019,wang2021high}
-The formulation presented by Lu\cite{LuETal2006} takes the normal derivative of \eqref{eq:direct} to couple both $\phi$ and $\partial\phi/\partial\mathbf{n}$ as
+Here, we use the better conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
 %
@@
 %
-The two new integral operators that appear are defined as 
+In Equation \eqref{eq:lu}, $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
+$V$, $K$, $K^{\prime}$, and $W$ are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
+These are defined as
 %
-\begin{align}
-\label{eq:adj_hyp}
-K^{\prime\Gamma}_i\varphi (\mathbf{x}) = \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-W^\Gamma_i\varphi (\mathbf{x}) = - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+\begin{align}\label{eq:single_double}
+V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
 \end{align}
-where $i \in \{L,Y\}$, 
-and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior. 
+%
+where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and
+%
+\begin{align}\label{eq:green_func}
+g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+\end{align}
+%
+are the corresponding free-space Green's functions.
+
+%Applying Green's second identity to Equation \eqref{eq:pbe} we get 
+%
+%\begin{align} \label{eq:volume_potential}
+%\phi_{1}(\mathbf{x}_{\Omega_1})+ K_{L}^{\Omega_1}\phi_1 -  V_{L}^{\Omega_1} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Omega_1} - \mathbf{x}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
+%\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
+%\end{align}
+%
+%where $\mathbf{x}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
+$K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
+%
+%\begin{align}\label{eq:single_double}
+%V^D \varphi (\mathbf{x}) = \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%K^D \varphi (\mathbf{x}) = \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+%\end{align}
+%
+%where $D \in \{\Omega_1, \Omega_2, \Gamma\}$, $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and 
+%
+%\begin{align}\label{eq:green_func}
+%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+%\end{align}
+%
+%are the free-space Green's function of the Laplace and linearized Poisson-Boltzmann equations, respectively.
+
+%If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{x}_{\Omega}$ approaches $\Gamma$, we get
+%
+%\begin{align} \label{eq:direct}
+%\tfrac{\phi_1}{2}+ K_{L}^{\Gamma}\phi_1 -  V_{L}^{\Gamma} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Gamma} - \mathbf{x}_k|} \nonumber \\
+%\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 +  \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Gamma} \lambda_2 & = 0
+%\end{align}
+%
+%The {\it direct} formulation\cite{YoonLenhoff1990} couples the two expressions of Eq.
+\eqref{eq:direct} on $\Gamma$, considering the interface conditions.
+Even though this formulation is poorly conditioned with respect to the mesh size, it can still model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,MartinezETal2019,wang2021high}
+%The formulation presented by Lu\cite{LuETal2006} takes the normal derivative of \eqref{eq:direct} to couple both $\phi$ and $\partial\phi/\partial\mathbf{n}$ as
+%
+%\begin{align}\label{eq:lu}
+%    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
+%     \nonumber \\
+%    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
+%\end{align}
+%
+%The two new integral operators that appear are defined as 
+%
+%\begin{align}
+%\label{eq:adj_hyp}
+%K^{\prime\Gamma}_i\varphi (\mathbf{x}) = \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%W^\Gamma_i\varphi (\mathbf{x}) = - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+%\end{align}
+%where $i \in \{L,Y\}$, 
+%and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior.
+
 In weak form, Eq. \eqref{eq:lu} becomes
@@
 \eqref{eq:lu_disc}, we obtain the reaction potential ($\phi_r$) in Eq.
-\eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$ in Eq.
-\eqref{eq:volume_potential}.
-This gives
+\eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$.
+This gives\cite{CooperBardhanBarba2014}
 %
 \begin{align} \label{eq:phi_reac}
-\phi_{r} = - K_{L}^{\Omega_1}(\phi_1) + V_{L}^{\Omega_1} \left(  \lambda_1  \right),
+\phi_{r}(\mathbf{r}) = - K_{L}^{\mathbf{r}}(\phi_1) + V_{L}^{\mathbf{r}} \left(  \lambda_1  \right),
 \end{align}
 %
-which is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
+where $\mathbf{r}\in\Omega_1$.
+This is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
 

### 2022-10-13 methods.tex
moved variable permittivity to results

@@
 On the other hand, the FEM is known for its robustness and universal applicability, even for problems of inhomogeneous or non-linear nature.
-
-{\sffamily \small Modeling the solute with a Gaussian-based variable permittivity}\\
-
-In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
-A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom,\cite{grant2001smooth} which has shown enhanced accuracy in some applications, like pKa calculations.\cite{li2013dielectric}
-In this setting, we define a density function $\rho$ depending on position $r$ as
-%
-\begin{equation}
-\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|r-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right)
-\end{equation}
-%
-where the product runs over all the atoms of the solute, $R_i$ is the van der Waals radius of atom i, and we used $\sigma$=1. Then, we can compute the permittivity as
-%
-\begin{equation}\label{eq:varying_eps}
-\epsilon := \left(1-\rho \right) \epsilon_1 + \rho\epsilon_2
-\end{equation}
-
-As $\epsilon_2$ is variable, Equation \eqref{eq:phic} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
-For vacuum calculations, we considered the same distribution of $\epsilon_2$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon$=2. 
-Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff.\cite{li2013dielectric} We did not consider a cutoff in our calculations.
-
-{\sffamily \small The Johnson-N\'ed\'elec FEM-BEM coupling for molecular electrostatics}\\
-
-   We modeled the electrostatic component of solvation of a solute with a Gaussian-varying permittivit (Eq.
-\eqref{eq:varying_eps}) with a finite element discretisation in the internal domain ($\Omega_1$), and boundary elements for external domain ($\Omega_2$).
-We used the Johnson-N\'ed\'elec formulation [citation needed], which is the simplest form of FEM-BEM coupling, and we detail it next.
+Here, we used the Johnson-N\'ed\'elec formulation,\cite{johnson1980coupling} which is the simplest form of FEM-BEM coupling, and we detail it next.
 

### 2022-10-13 results.tex
moved variable permittivity to results

@@
 
+\subsection*{\sffamily \large Motivation: modeling the solute with a Gaussian-based variable permittivity}
+
+In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
+A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom,\cite{grant2001smooth} which has shown enhanced accuracy in some applications, like pKa calculations.\cite{li2013dielectric}
+In this setting, we define a density function $\rho$ depending on position $r$ as
+%
+\begin{equation}
+\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|r-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right)
+\end{equation}
+%
+where the product runs over all the atoms of the solute, $R_i$ is the van der Waals radius of atom i, and we used $\sigma$=1. Then, we can compute the permittivity as
+%
+\begin{equation}\label{eq:varying_eps}
+\epsilon := \left(1-\rho \right) \epsilon_1 + \rho\epsilon_2
+\end{equation}
+
+As $\epsilon_2$ is variable, Equation \eqref{eq:phic} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
+For vacuum calculations, we considered the same distribution of $\epsilon_2$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon$=2. 
+Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff.\cite{li2013dielectric} We did not consider a cutoff in our calculations.
+
 We used Equation \eqref{eq:varying_eps} to generate dielectric maps, which we ran on APBS~\cite{BakerETal2001} for comparison. 

### 2022-10-21 methods.tex
Moving BEM-BEM section
I have moved the BEM formulation to the results because I do not know how appendices work in this journal. I have made some changes to make readable the method section so please check it.

@@
 
-There are regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} which are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods.
+Regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods.
 However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permitivitties.
@@
 
-\subsection*{\sffamily \large Numerical solution of the Poisson-Boltzmann equation}
+\subsection*{\sffamily \large Novel numerical solution of the Poisson-Boltzmann equation}
 
-\subsubsection*{\sffamily \normalsize BEM-BEM coupling}
+%\subsection*{\sffamily \normalsize FEM-BEM coupling}
 
-The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson-Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl.~\cite{search2022towards}
-
-There are several possible boundary integral formulations of Equation \eqref{eq:pbe}.~\cite{search2022towards} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
-Here, we use the better conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
-%
-\begin{align}\label{eq:lu}
-    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
-     \nonumber \\
-    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
-\end{align}
-%
-In Equation \eqref{eq:lu}, $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
-For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
-$V$, $K$, $K^{\prime}$, and $W$ are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
-These are defined as
-%
-\begin{align}\label{eq:single_double}
-V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
-K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
-\end{align}
-%
-where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and
-%
-\begin{align}\label{eq:green_func}
-g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
-g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
-\end{align}
-%
-are the corresponding free-space Green's functions.
-
-%Applying Green's second identity to Equation \eqref{eq:pbe} we get 
-%
-%\begin{align} \label{eq:volume_potential}
-%\phi_{1}(\mathbf{x}_{\Omega_1})+ K_{L}^{\Omega_1}\phi_1 -  V_{L}^{\Omega_1} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Omega_1} - \mathbf{x}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
-%\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
-%\end{align}
-%
-%where $\mathbf{x}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
-For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
-$K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
-%
-%\begin{align}\label{eq:single_double}
-%V^D \varphi (\mathbf{x}) = \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-%K^D \varphi (\mathbf{x}) = \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
-%\end{align}
-%
-%where $D \in \{\Omega_1, \Omega_2, \Gamma\}$, $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and 
-%
-%\begin{align}\label{eq:green_func}
-%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
-%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
-%\end{align}
-%
-%are the free-space Green's function of the Laplace and linearized Poisson-Boltzmann equations, respectively.
-
-%If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{x}_{\Omega}$ approaches $\Gamma$, we get
-%
-%\begin{align} \label{eq:direct}
-%\tfrac{\phi_1}{2}+ K_{L}^{\Gamma}\phi_1 -  V_{L}^{\Gamma} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Gamma} - \mathbf{x}_k|} \nonumber \\
-%\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 +  \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Gamma} \lambda_2 & = 0
-%\end{align}
-%
-%The {\it direct} formulation\cite{YoonLenhoff1990} couples the two expressions of Eq.
-\eqref{eq:direct} on $\Gamma$, considering the interface conditions.
-Even though this formulation is poorly conditioned with respect to the mesh size, it can still model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,MartinezETal2019,wang2021high}
-%The formulation presented by Lu\cite{LuETal2006} takes the normal derivative of \eqref{eq:direct} to couple both $\phi$ and $\partial\phi/\partial\mathbf{n}$ as
-%
-%\begin{align}\label{eq:lu}
-%    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
-%     \nonumber \\
-%    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
-%\end{align}
-%
-%The two new integral operators that appear are defined as 
-%
-%\begin{align}
-%\label{eq:adj_hyp}
-%K^{\prime\Gamma}_i\varphi (\mathbf{x}) = \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-%W^\Gamma_i\varphi (\mathbf{x}) = - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
-%\end{align}
-%where $i \in \{L,Y\}$, 
-%and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior.
-
-In weak form, Eq. \eqref{eq:lu} becomes
-%
-\begin{align}\label{eq:lu_disc}
-&\left< \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\phi_{2}}{2} - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_{2}, v \right>_{\Gamma} + \left< \left(V_Y^\Gamma - V_L^\Gamma\right) \lambda_2, v \right>_\Gamma = \left< \sum_{k=0}^{N_q}  f_k, v \right>_{\Gamma} \nonumber \\
-&\left< \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_{2}, \zeta \right>_\Gamma + \left<  \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\lambda_2}{2} + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2, \zeta\right>_\Gamma = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}} f_k, \zeta \right>_{\Gamma}
-\end{align}
-%
-where $v, \zeta$ are test functions, $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ %and $\left(\varphi,v\right)_\Omega = \int_\Omega \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are
-is the inner products on the surface% and domain, respectively
-and $f_k := \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}$.
-
-We introduce below the matrix formulation. Let $\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ be the vector of canonical basis
-functions of $W_{h}^{k}$ and  $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
-functions of $\Lambda_{h}^{l}$. We define the following matrices associated with the corresponding bilinear forms
-\begin{align*}
-\widetilde{K}_{\alpha \beta} = \left<\left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right) \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}
- &,&
-\widetilde{V}_{\alpha \beta} = \left<\left(V_Y^\Gamma - V_L^\Gamma\right) \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
-\widetilde{W}_{\alpha \beta} = \left<\left(W_Y^\Gamma - W_L^\Gamma\right) \phi^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
- &,&
-\widetilde{K'}_{\alpha \beta} = \left<\left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right) \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma},
-\end{align*}
-and vectors associated with the corresponding linear forms
-\begin{align*}
-\vec{f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},   \phi^{\beta}_1  \right>_{\Gamma} &,& \vec{\partial f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),   \phi^{\beta}_1  \right>_{\Gamma}.
-\end{align*}
-
-Using the above definition the discrete problem~\eqref{eq:fem_bem_disctrete} can be written in the following matrix form
-\begin{align*}
-\begin{bmatrix}
- \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I - \widetilde{K}  & \widetilde{V}  \\  
- \tfrac{\epsilon_1}{\epsilon_2} \widetilde{W} & \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I + \widetilde{K'}
-\end{bmatrix}
-\begin{bmatrix}
-\vec{\phi}_2 \\
-\vec{\lambda}_2 
-\end{bmatrix}
-= 
-\begin{bmatrix}
-\vec{f} \\  
-\vec{\partial f}
-\end{bmatrix}.
-\end{align*}
-%
-
-Having computed the electrostatic potential with Eq.
-\eqref{eq:lu_disc}, we obtain the reaction potential ($\phi_r$) in Eq.
-\eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$.
-This gives\cite{CooperBardhanBarba2014}
-%
-\begin{align} \label{eq:phi_reac}
-\phi_{r}(\mathbf{r}) = - K_{L}^{\mathbf{r}}(\phi_1) + V_{L}^{\mathbf{r}} \left(  \lambda_1  \right),
-\end{align}
-%
-where $\mathbf{r}\in\Omega_1$.
-This is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
-
-\subsection*{\sffamily \normalsize FEM-BEM coupling}
-
-BEM is a popular alternative to solve the Poisson-Boltzmann equation numerically because it reduces the dimension of the problem by using the boundary integral formulation.
+The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson-Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl.~\cite{search2022towards}.
+Its popularity comes because it reduces the dimension of the problem by using the boundary integral formulation.
 Unfortunately, this advantage comes at a cost: it requires a fundamental solution to be applied.
@@
 %
-For such case, a finite element method (FEM) is more suitable.
+A finite element method (FEM) is more suitable for such case.
 
@@
 where $v$ is a test function, and $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ and $\left(\varphi,v\right)_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are the inner products on the surface and domain, respectively.
-For the external problem with BEM, we use the direct formulation from Eq.~\eqref{eq:direct} to obtain
+For the external problem with BEM, we define the Dirichlet trace~\cite{MR2361676} 
 \begin{align*}
-\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma}  \left(\lambda_1 \right) & = 0.
+% \label{eq:trace_map}
+\gamma:  H^1(\Omega_2) &\rightarrow H^{\frac{1}{2}}(\Gamma) & \gamma f(x) & := \lim_{\Omega_2 \ni y \rightarrow x \in \Gamma}  f(y),
 \end{align*}
+and we use the direct formulation from the second equation of Eq.~\eqref{eq:pbe} to obtain
+\begin{align*}
+\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\gamma \phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma}  \left(\lambda_1 \right) & = 0.
+\end{align*}
+$V$ and $K$ are the single-layer and double-layer operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels. These are defined as
 %
+\begin{align}\label{eq:single_double}
+V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+%K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+\end{align}
+%
+where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and
+%
+\begin{align}\label{eq:green_func}
+g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+\end{align}
+%
+are the corresponding free-space Green's functions.
+
 Then, the coupling problem can be written as
@@
  \left(  \epsilon_1 \nabla \phi_1, \nabla v \right)_{\Omega_1}  - \left< \epsilon_1 \lambda_2, v \right>_\Gamma &=&   \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right)_{\Omega_1} \\[3mm]
-  \left< \left(\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \phi_1, \zeta \right>_\Gamma + \tfrac{\epsilon_1}{\epsilon_2} \left< V_{Y}^{\Gamma} \lambda_2, \zeta \right>_\Gamma &=&0.
+  \left< \left(\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \gamma \phi_1, \zeta \right>_\Gamma + \tfrac{\epsilon_1}{\epsilon_2} \left< V_{Y}^{\Gamma} \lambda_2, \zeta \right>_\Gamma &=&0.
   \end{array}
@@
 \begin{align*}
-A_{\alpha \beta} = \left(\nabla \phi_1, \nabla \phi_1^{\beta} \right)_{\Omega_1}  
+A_{\alpha \beta} = \left(\nabla \phi_1^{\alpha}, \nabla \phi_1^{\beta} \right)_{\Omega_1}  
 &,&
 M_{\alpha \beta} = \left< \widetilde{\phi}^{\alpha}, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
-K_{\alpha \beta} = \left<K_{Y}^{\Gamma} \phi^{\alpha}_1, \ \lambda^{\beta}_2 \right>_{\Gamma}
+K_{\alpha \beta} = \left<K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \ \lambda^{\beta}_2 \right>_{\Gamma}
  &,&
@@
 \epsilon_1 A &  - \epsilon_1 M^T \\  
-\left(\tfrac12 I + K \right) &  \tfrac{\epsilon_1}{\epsilon_2} V 
+\left(\tfrac12 I + K \right) \gamma &  \tfrac{\epsilon_1}{\epsilon_2} V 
 \end{bmatrix}
@@
 \end{align*}
+
+Having computed the electrostatic potential with Eq.
+\eqref{eq:standard_fem_bem}, we obtain the reaction potential ($\phi_r$) in Eq.
+\eqref{eq:dG} by subtracting out the Coulombic component out of $\gamma \phi_1$.
+This gives\cite{CooperBardhanBarba2014}
+%
+\begin{align} \label{eq:phi_reac}
+\phi_{r}(\mathbf{r}) = - K_{L}^{\mathbf{r}}( \gamma \phi_1) + V_{L}^{\mathbf{r}} \left(  \lambda_1  \right),
+\end{align}
+%
+where $\mathbf{r}\in\Omega_1$.
+This is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.

### 2022-10-21 results.tex
Moving BEM-BEM section
I have moved the BEM formulation to the results because I do not know how appendices work in this journal. I have made some changes to make readable the method section so please check it.

@@
 
-For the finite element computations we use the software package FEniCSx while for the boundary element computations we use Bempp-cl together with Exafmm-t.
+For the finite element computations, we use the software package FEniCSx while for the boundary element computations we use Bempp-cl together with Exafmm-t.
 FEniCSx is the successor of the widely used FEniCS finite element library.
-It provides a convenient Python interface, in which problems are described using UFL (Unified Form Language), a convenient domain specific language specifically designed for finite element discretisations of partial differential equations.
+It provides a convenient Python interface, in which problems are described using UFL (Unified Form Language), a convenient domain-specific language specifically designed for finite element discretisations of partial differential equations.
 During assembly the UFL description is transformed into efficient low-level C++ code and just-in-time compiled.
 Bempp-cl is a Python package that uses low-level OpenCL kernels written in C99 to provide optimised assembly routines.
-For moderate discretisation sizes up to a few ten thousand elements, the built-in dense assembly routines are highly efficient.
+The built-in dense assembly routines are highly efficient for moderate discretisation sizes up to a few ten thousand elements.
 
@@
 Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (PROVIDE LINK), and all codes used in this sections are simple Jupyter Notebooks that can be reproducibly executed in this provided Docker image.
+
+\section*{\sffamily \Large BEM-BEM coupling}
+
+Several possible boundary integral formulations of Equation \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
+Here, we use the better conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
+%
+\begin{align}\label{eq:lu}
+    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
+     \nonumber \\
+    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
+\end{align}
+%
+In Equation \eqref{eq:lu}, $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
+$V$, $K$, $K^{\prime}$, and $W$ are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
+These are defined in Equation~\eqref{eq:single_double} and as
+%
+\begin{align}\label{eq:adj_double_hypersingular}
+%V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+\end{align}
+%
+where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and Green's functions $g_L, g_Y$ were defined in Equation~\eqref{eq:green_func}.
+%
+%\begin{align}\label{eq:green_func}
+%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+%\end{align}
+%
+%are the corresponding free-space Green's functions.
+
+%%Applying Green's second identity to Equation \eqref{eq:pbe} we get 
+%%
+%%\begin{align} \label{eq:volume_potential}
+%%\phi_{1}(\mathbf{x}_{\Omega_1})+ K_{L}^{\Omega_1}\phi_1 -  V_{L}^{\Omega_1} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Omega_1} - \mathbf{x}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
+%%\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
+%%\end{align}
+%%
+%%where $\mathbf{x}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
+$K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
+%%
+%%\begin{align}\label{eq:single_double}
+%%V^D \varphi (\mathbf{x}) = \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%%K^D \varphi (\mathbf{x}) = \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+%%\end{align}
+%%
+%%where $D \in \{\Omega_1, \Omega_2, \Gamma\}$, $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and 
+%%
+%%\begin{align}\label{eq:green_func}
+%%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+%%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+%%\end{align}
+%%
+%%are the free-space Green's function of the Laplace and linearized Poisson-Boltzmann equations, respectively. 
+%
+%%If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{x}_{\Omega}$ approaches $\Gamma$, we get
+%%
+%%\begin{align} \label{eq:direct}
+%%\tfrac{\phi_1}{2}+ K_{L}^{\Gamma}\phi_1 -  V_{L}^{\Gamma} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Gamma} - \mathbf{x}_k|} \nonumber \\
+%%\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 +  \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Gamma} \lambda_2 & = 0
+%%\end{align}
+%%
+%%The {\it direct} formulation\cite{YoonLenhoff1990} couples the two expressions of Eq.
+\eqref{eq:direct} on $\Gamma$, considering the interface conditions.
+Even though this formulation is poorly conditioned with respect to the mesh size, it can still model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,MartinezETal2019,wang2021high}
+%%The formulation presented by Lu\cite{LuETal2006} takes the normal derivative of \eqref{eq:direct} to couple both $\phi$ and $\partial\phi/\partial\mathbf{n}$ as
+%%
+%%\begin{align}\label{eq:lu}
+%%    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
+%%     \nonumber \\
+%%    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
+%%\end{align}
+%%
+%%The two new integral operators that appear are defined as 
+%%
+%%\begin{align}
+%%\label{eq:adj_hyp}
+%%K^{\prime\Gamma}_i\varphi (\mathbf{x}) = \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%%W^\Gamma_i\varphi (\mathbf{x}) = - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+%%\end{align}
+%%where $i \in \{L,Y\}$, 
+%%and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior. 
+%
+%In weak form, Eq. \eqref{eq:lu} becomes
+%%
+%\begin{align}\label{eq:lu_disc}
+%&\left< \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\phi_{2}}{2} - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_{2}, v \right>_{\Gamma} + \left< \left(V_Y^\Gamma - V_L^\Gamma\right) \lambda_2, v \right>_\Gamma = \left< \sum_{k=0}^{N_q}  f_k, v \right>_{\Gamma} \nonumber \\
+%&\left< \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_{2}, \zeta \right>_\Gamma + \left<  \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\lambda_2}{2} + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2, \zeta\right>_\Gamma = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}} f_k, \zeta \right>_{\Gamma}
+%\end{align}
+%%
+%where $v, \zeta$ are test functions, $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ %and $\left(\varphi,v\right)_\Omega = \int_\Omega \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are
+%is the inner products on the surface% and domain, respectively
+%and $f_k := \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}$.
+%
+%We introduce below the matrix formulation. Let $\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ be the vector of canonical basis
+%functions of $W_{h}^{k}$ and  $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
+%functions of $\Lambda_{h}^{l}$. We define the following matrices associated with the corresponding bilinear forms
+%\begin{align*}
+%\widetilde{K}_{\alpha \beta} = \left<\left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right) \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}
+% &,&
+%\widetilde{V}_{\alpha \beta} = \left<\left(V_Y^\Gamma - V_L^\Gamma\right) \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
+%\widetilde{W}_{\alpha \beta} = \left<\left(W_Y^\Gamma - W_L^\Gamma\right) \phi^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
+% &,&
+%\widetilde{K'}_{\alpha \beta} = \left<\left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right) \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma},
+%\end{align*}
+%and vectors associated with the corresponding linear forms
+%\begin{align*}
+%\vec{f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},   \phi^{\beta}_1  \right>_{\Gamma} &,& \vec{\partial f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),   \phi^{\beta}_1  \right>_{\Gamma}.
+%\end{align*}
+%
+%Using the above definition the discrete problem~\eqref{eq:fem_bem_disctrete} can be written in the following matrix form
+%\begin{align*}
+%\begin{bmatrix}
+% \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I - \widetilde{K}  & \widetilde{V}  \\  
+% \tfrac{\epsilon_1}{\epsilon_2} \widetilde{W} & \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I + \widetilde{K'}
+%\end{bmatrix}
+%\begin{bmatrix}
+%\vec{\phi}_2 \\
+%\vec{\lambda}_2 
+%\end{bmatrix}
+%= 
+%\begin{bmatrix}
+%\vec{f} \\  
+%\vec{\partial f}
+%\end{bmatrix}.
+%\end{align*}
+%%
+%
 

### 2022-10-27 methods.tex
BEM-BEM in the method section as discusses

@@
 \end{equation}
+
+\subsection*{\sffamily \large BEM-BEM coupling}
+
+Several possible boundary integral formulations of Equation \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
+Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
+%
+\begin{align}\label{eq:lu}
+    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
+     \nonumber \\
+    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
+\end{align}
+%
+In Equation \eqref{eq:lu}, $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
+$V$, $K$, $K^{\prime}$, and $W$ are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
+These are defined %in Equation~\eqref{eq:single_double} and
+as
+%
+\begin{align}\label{eq:all_op}
+V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+\end{align}
+%
+where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and %Green's functions $g_L, g_Y$ were defined in Equation~\eqref{eq:green_func}.
+\begin{align}\label{eq:green_func}
+g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+\end{align}
+are the corresponding free-space Green's functions.
+
+%%Applying Green's second identity to Equation \eqref{eq:pbe} we get 
+%%
+%%\begin{align} \label{eq:volume_potential}
+%%\phi_{1}(\mathbf{x}_{\Omega_1})+ K_{L}^{\Omega_1}\phi_1 -  V_{L}^{\Omega_1} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Omega_1} - \mathbf{x}_k|}  \quad \text{on $\Omega_1$,} \nonumber \\
+%%\phi_{2}(\mathbf{x}_{\Omega_2}) - K_{Y}^{\Omega_2}\phi_2 + \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Omega_2} \lambda_2& = 0 \quad \text{on $\Omega_2$,}
+%%\end{align}
+%%
+%%where $\mathbf{x}_\Omega$ is evaluated anywhere in the correspoding domain, except $\Gamma$, and $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
+For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
+$K$ and $V$ are the double- and single-layer potentials for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels
+%%
+%%\begin{align}\label{eq:single_double}
+%%V^D \varphi (\mathbf{x}) = \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%%K^D \varphi (\mathbf{x}) = \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+%%\end{align}
+%%
+%%where $D \in \{\Omega_1, \Omega_2, \Gamma\}$, $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and 
+%%
+%%\begin{align}\label{eq:green_func}
+%%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+%%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+%%\end{align}
+%%
+%%are the free-space Green's function of the Laplace and linearized Poisson-Boltzmann equations, respectively. 
+%
+%%If we take the limit of Eq. \eqref{eq:volume_potential} as $\mathbf{x}_{\Omega}$ approaches $\Gamma$, we get
+%%
+%%\begin{align} \label{eq:direct}
+%%\tfrac{\phi_1}{2}+ K_{L}^{\Gamma}\phi_1 -  V_{L}^{\Gamma} \lambda_2^1 & = \tfrac{1}{\epsilon_1} \sum_{k=0}^{N_q}  \frac{q_k}{4\pi|\mathbf{x}_{\Gamma} - \mathbf{x}_k|} \nonumber \\
+%%\tfrac{\phi_2}{2} - K_{Y}^{\Gamma}\phi_2 +  \tfrac{\epsilon_1}{\epsilon_2} V_{Y}^{\Gamma} \lambda_2 & = 0
+%%\end{align}
+%%
+%%The {\it direct} formulation\cite{YoonLenhoff1990} couples the two expressions of Eq.
+\eqref{eq:direct} on $\Gamma$, considering the interface conditions.
+Even though this formulation is poorly conditioned with respect to the mesh size, it can still model large systems when it is preconditioned appropriately.\cite{AltmanBardhanWhiteTidor09,MartinezETal2019,wang2021high}
+%%The formulation presented by Lu\cite{LuETal2006} takes the normal derivative of \eqref{eq:direct} to couple both $\phi$ and $\partial\phi/\partial\mathbf{n}$ as
+%%
+%%\begin{align}\label{eq:lu}
+%%    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
+%%     \nonumber \\
+%%    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
+%%\end{align}
+%%
+%%The two new integral operators that appear are defined as 
+%%
+%%\begin{align}
+%%\label{eq:adj_hyp}
+%%K^{\prime\Gamma}_i\varphi (\mathbf{x}) = \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%%W^\Gamma_i\varphi (\mathbf{x}) = - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+%%\end{align}
+%%where $i \in \{L,Y\}$, 
+%%and are called the {\it  adjoint double layer} and {\it hypersingular} operators, respectively. Note that the potential in Eq. \eqref{eq:lu} is evaluated on the exterior. 
+%
+%In weak form, Eq. \eqref{eq:lu} becomes
+%%
+%\begin{align}\label{eq:lu_disc}
+%&\left< \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\phi_{2}}{2} - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_{2}, v \right>_{\Gamma} + \left< \left(V_Y^\Gamma - V_L^\Gamma\right) \lambda_2, v \right>_\Gamma = \left< \sum_{k=0}^{N_q}  f_k, v \right>_{\Gamma} \nonumber \\
+%&\left< \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_{2}, \zeta \right>_\Gamma + \left<  \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\lambda_2}{2} + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2, \zeta\right>_\Gamma = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}} f_k, \zeta \right>_{\Gamma}
+%\end{align}
+%%
+%where $v, \zeta$ are test functions, $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ %and $\left(\varphi,v\right)_\Omega = \int_\Omega \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are
+%is the inner products on the surface% and domain, respectively
+%and $f_k := \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}$.
+%
+%We introduce below the matrix formulation. Let $\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ be the vector of canonical basis
+%functions of $W_{h}^{k}$ and  $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ - the vector of canonical basis
+%functions of $\Lambda_{h}^{l}$. We define the following matrices associated with the corresponding bilinear forms
+%\begin{align*}
+%\widetilde{K}_{\alpha \beta} = \left<\left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right) \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}
+% &,&
+%\widetilde{V}_{\alpha \beta} = \left<\left(V_Y^\Gamma - V_L^\Gamma\right) \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
+%\widetilde{W}_{\alpha \beta} = \left<\left(W_Y^\Gamma - W_L^\Gamma\right) \phi^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
+% &,&
+%\widetilde{K'}_{\alpha \beta} = \left<\left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right) \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma},
+%\end{align*}
+%and vectors associated with the corresponding linear forms
+%\begin{align*}
+%\vec{f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},   \phi^{\beta}_1  \right>_{\Gamma} &,& \vec{\partial f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),   \phi^{\beta}_1  \right>_{\Gamma}.
+%\end{align*}
+%
+%Using the above definition the discrete problem~\eqref{eq:fem_bem_disctrete} can be written in the following matrix form
+%\begin{align*}
+%\begin{bmatrix}
+% \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I - \widetilde{K}  & \widetilde{V}  \\  
+% \tfrac{\epsilon_1}{\epsilon_2} \widetilde{W} & \tfrac12 \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) I + \widetilde{K'}
+%\end{bmatrix}
+%\begin{bmatrix}
+%\vec{\phi}_2 \\
+%\vec{\lambda}_2 
+%\end{bmatrix}
+%= 
+%\begin{bmatrix}
+%\vec{f} \\  
+%\vec{\partial f}
+%\end{bmatrix}.
+%\end{align*}
+%%
+%
+
+Having computed the electrostatic potential with Eq.
+\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.
+\eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$.
+This gives\cite{CooperBardhanBarba2014}
+%
+\begin{align} \label{eq:phi_reac}
+\phi_{r}(\mathbf{r}) = - K_{L}^{\mathbf{r}} \phi_1 + V_{L}^{\mathbf{r}}  \lambda_1  ,
+\end{align}
+%
+where $\mathbf{r}\in\Omega_1$.
+This is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
 
@@
 \begin{align*}
-\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\gamma \phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma}  \left(\lambda_1 \right) & = 0.
+\tfrac{\phi_1}{2} - K_{Y}^{\Gamma}\gamma \phi_1 + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma}  \lambda_1 & = 0.
 \end{align*}
-$V$ and $K$ are the single-layer and double-layer operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels. These are defined as
+$V$ and $K$ are the single-layer and double-layer operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
+These are defined in Equations~\eqref{eq:all_op} and~\eqref{eq:green_func}.
+%as
 %
-\begin{align}\label{eq:single_double}
-V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+%\begin{align}\label{eq:single_double}
+%V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+%K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
 %K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
 %W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
-\end{align}
+%\end{align}
 %
-where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and
+%where $i \in \{L,Y\}$, $\varphi(\mathbf{x})$ can be any distribution over $\Gamma$, and
 %
-\begin{align}\label{eq:green_func}
-g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
-g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
-\end{align}
+%\begin{align}\label{eq:green_func}
+%g_L(\mathbf{x},\mathbf{x}')=\frac{1}{4\pi|\mathbf{x}-\mathbf{x}'|} \nonumber \\
+%g_Y(\mathbf{x},\mathbf{x}')=\frac{e^{-\kappa|\mathbf{x}-\mathbf{x}'|}}{4\pi|\mathbf{x}-\mathbf{x}'|}
+%\end{align}
 %
-are the corresponding free-space Green's functions.
+%are the corresponding free-space Green's functions.
 
@@
 \end{align*}
-
-Having computed the electrostatic potential with Eq.
-\eqref{eq:standard_fem_bem}, we obtain the reaction potential ($\phi_r$) in Eq.
-\eqref{eq:dG} by subtracting out the Coulombic component out of $\gamma \phi_1$.
-This gives\cite{CooperBardhanBarba2014}
-%
-\begin{align} \label{eq:phi_reac}
-\phi_{r}(\mathbf{r}) = - K_{L}^{\mathbf{r}}( \gamma \phi_1) + V_{L}^{\mathbf{r}} \left(  \lambda_1  \right),
-\end{align}
-%
-where $\mathbf{r}\in\Omega_1$.
-This is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.

### 2023-03-23 results.tex
DolfinX version
Updated version with DolfinX results, still we need to decide with Arginine test we consider!
We are missing large scale problem results!

@@
 
-In implicit-solvent models, the molecule is usually considered as a region with constant permittivity, in this case, with $\epsilon_1=4$.
+In implicit-solvent models, the molecule is usually considered as a region with constant permittivity, in this case, with $\epsilon_1=2$.
 In the solvent region, we used the permittivity of water ($\epsilon_2$=80) and an inverse of the Debye length of $\kappa=0.125$ \AA$^{-1}$.
@@
   \centering
-  \includegraphics[width=0.6\linewidth]{Sphere_const_coeff_error.png}
-%   \includegraphics[width=0.45\linewidth]{Sphere_const_coeff_iter.png}
-%   \includegraphics[width=0.45\linewidth]{Sphere_const_coeff_time.png}
+  \includegraphics[width=0.6\linewidth]{DolfinX_Sphere_const_coeff_error.png}
   \caption{Error for the Kirkwood sphere.}
@@
 
-As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine (the structure of arginine taken from the protein data bank \cite{bank}).
+As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine (the structure of arginine taken from the protein data bank \cite{bank} {\color{red} We are using different ARG!}).
 We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}
@@
 \centering
-   \includegraphics[width=0.6\linewidth]{Arginine_const_coeff_error_11.png}
-%    \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_error.png}
-\caption{Solvation energy for arginine with a constant permittivity.
+   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine2_const_coeff_error.png}
+   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine_const_coeff_error_11.png}
+\caption{Solvation energy for arginine with a constant permittivity. (left - Arginine2 and right - Arginine)
 %maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
@@
 \centering
-   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter_11.png}
-%  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time_11.png}
-%  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_setup_time_11.png}
-  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_total_time_11.png}
-  \caption{Iteration count (left) and time-to-solution (right) for arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
+   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
+%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_time.png}
+%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_setup_time.png}
+  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
+%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_iter_11.png}
+%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_time_11.png}
+%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_setup_time_11.png}
+%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
+  \caption{Iteration count (left) and time-to-solution (right) for Arginine2 with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
+%NOTE: x axis differ between top and bottom.
+Also, should we include preconditioned vs non preconditioned?
+We could easily precondition BEM-BEM too.
+%(1) fix title, (2) can we put them in a single plot, (3)
+%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
+}
+\label{fig:arg2_constant_time_iter}
+\end{figure}
+
+\begin{figure}
+\centering
+%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
+%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_time.png}
+%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_setup_time.png}
+%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
+   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_iter_11.png}
+%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_time_11.png}
+%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_setup_time_11.png}
+  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
+  \caption{Iteration count (left) and time-to-solution (right) for Arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
 %NOTE: x axis differ between top and bottom.
@@
 
-As $\epsilon_2$ is variable, Equation \eqref{eq:phic} does not have an analytical solution, and the electrostatic potential in vacuum state has to be computed numerically.
-For vacuum calculations, we considered the same distribution of $\epsilon_2$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon$=2. 
+As $\epsilon$ is variable, Equation \eqref{eq:phic} does not have an analytical solution, and the electrostatic potential in the vacuum state has to be computed numerically.
+For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon_2$=2. 
 Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff.\cite{li2013dielectric} We did not consider a cutoff in our calculations.
@@
 
-Figure \ref{fig:arg_variable} contains performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
+Figure \ref{fig:arg_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
 
@@
 \hline
-\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & -32.4652\\ 
-& 0.39$\times$0.39$\times$0.39 & -32.4042\\ 
-&0.26$\times$0.26$\times$0.26 & -32.3375\\ 
-&0.17$\times$0.17$\times$0.17 & -32.3413\\ 
+\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & -107.6186 \\ 
+& 0.39$\times$0.39$\times$0.39 & -107.8752\\ 
+&0.26$\times$0.26$\times$0.26 & -108.3378\\ 
+&0.195$\times$0.195$\times$0.195 & -108.5837\\ 
+&0.098$\times$0.098$\times$0.098 & -108.8844\\ 
 \hline
@@
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
-    & 2 & -35.688 \\
-FEM-BEM    & 4  & -33.304 \\
-coupling    & 8  & -32.634 \\
-    & 16 & -31.868 \\
+    & 4.1 & -109.933 \\
+FEM-BEM    & 6.7  & -110.238 \\
+coupling    & 8.57  & -109.658 \\
+    & 17 & -109.368 \\
+    & 24.5 & -109.286 \\
 \hline

### 2023-04-05 results.tex
New version with results of the large tests included

@@
 In this case, we considered a spherical cavity of radius $R=2$ \AA, with three charges ($q_1$=1, $q_2$=1, and $q_3$=0.75) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
-Figure \ref{fig:error_sphere} shows the error convergence of the FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -164.3375$ kcal/mol). 
-In these runs, the FEM mesh was generated using GMSH~\cite{geuzaine2009gmsh}. 
+Figure \ref{fig:error_sphere} shows the error convergence of the FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -336.0396$ kcal/mol). 
+In these runs, the FEM mesh was generated using GMSH~\cite{geuzaine2009gmsh} 
 %Bempp (check?) from a surface discretization 
-with 1, 2, 4, and 8 vertices per \AA$^2$ on the SES, the surface mesh of this volume one was also used for the BEM runs. 
+with %1, 2, 4, and 8 
+2, 6, 21 and 83 vertices per \AA$^2$ on the SES, the surface mesh of this volume one was also used for the BEM runs. 
 %For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
@@
 
-As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine (the structure of arginine taken from the protein data bank \cite{bank} {\color{red} We are using different ARG!}).
+As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine (the structure of arginine taken from the protein data bank \cite{bank}).
 We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}
@@
 The solvation energy computed with the two schemes is presented by Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
-Then, Figure \ref{fig:arg_constant_time_iter} compares the iteration count and time-to-solution.
+Then, Figure \ref{fig:arg2_constant_time_iter} compares the iteration count and time-to-solution.
 The left plot shows that using only BEM outperforms the coupled FEM-BEM approach in terms of iterations count.
@@
    \includegraphics[width=0.47\linewidth]{DolfinX_Arginine2_const_coeff_error.png}
-   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine_const_coeff_error_11.png}
-\caption{Solvation energy for arginine with a constant permittivity. (left - Arginine2 and right - Arginine)
+%   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine_const_coeff_error_11.png}
+\caption{Solvation energy for arginine with a constant permittivity. %(left - Arginine2 and right - Arginine)
 %maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
@@
 %  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
-  \caption{Iteration count (left) and time-to-solution (right) for Arginine2 with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
+  \caption{Iteration count (left) and time-to-solution (right) for Arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
 %NOTE: x axis differ between top and bottom.
@@
 
-\begin{figure}
-\centering
-%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
-%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_time.png}
-%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_setup_time.png}
-%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
-   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_iter_11.png}
-%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_time_11.png}
-%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_setup_time_11.png}
-  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
-  \caption{Iteration count (left) and time-to-solution (right) for Arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
-%NOTE: x axis differ between top and bottom.
+%\begin{figure}
+%\centering
+%%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
+%%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_time.png}
+%%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_setup_time.png}
+%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
+%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_iter_11.png}
+%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_time_11.png}
+%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_setup_time_11.png}
+%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
+%  \caption{Iteration count (left) and time-to-solution (right) for Arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
+%%NOTE: x axis differ between top and bottom.
 Also, should we include preconditioned vs non preconditioned?
@@
 %(1) fix title, (2) can we put them in a single plot, (3)
-%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
-}
-\label{fig:arg_constant_time_iter}
-\end{figure}
+%%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
+%}
+%\label{fig:arg_constant_time_iter}
+%\end{figure}
 
@@
 Table \ref{table:arg_variable} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approach.
-We can see that they are both converging to equivalent values, where the finest meshes agree up to 1.5\% (0.5 kcal/mol).
+We can see that they are both converging to equivalent values, where the finest meshes agree up to 1.5\% {\color{red} (shouldn't be 0.5\%?)} (0.5 kcal/mol).
 
-Figure \ref{fig:arg_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
+Figure \ref{fig:arg2_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
 
@@
 Add performance result?}
-\label{table:arg_variable}
+\label{table:arg2_variable}
 \end{table}
+
+%\begin{figure}
+%\centering
+%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
+%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
+%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
+%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
+%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
+%\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.
+%Can we make this only two plots?
+%}
+%\label{fig:arg_variable}
+%\end{figure}
 
@@
 }
-\label{fig:arg_variable}
+\label{fig:arg2_variable}
 \end{figure}
@@
 
-So far, we have only tested the FEM-BEM coupled approach with small structures. Here, we study its behavior with larger structures to evaluate its applicability in more realistic settings.
+So far, we have only tested the FEM-BEM coupled approach with small structures. Here, we study its behaviour with larger structures to evaluate its applicability in more realistic settings.
+
+\begin{table}
+\centering
+\begin{tabular}{c|c|c|c|c|c|c}
+Molecule & Mesh size  & $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
+& vert/\AA$^2$ &  kcal/mol & & sec & sec & sec \\
+\hline
+ 1pgb &  & -300.888 & 826 & 82 & 547 & 629  \\
+ 1lyz &  & -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
+ 1lyz gs3 & & -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
+ 1uxu &  & -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
+ 1igt &  &  -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
+ \hline
+\end{tabular}
+\caption{Large tests' results}
+\label{table:large_variable}
+\end{table}

### 2023-04-06 results.tex
Arg2 instead of Arg
Just putting the correct plots since we use another arginine

@@
 \centering
-% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
-% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
-\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
-\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
-\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
+% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
+% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
+\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
+\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_set_time.png}
+\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
 \caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.

### 2023-04-06 intro.tex
added citation to new paper with variable permittivity

@@
 
-Here we prototype this principle with the simplest implementation possible: a Johnson-N\'ed\'elec\cite{johnson1980coupling} coupling, mass-matrix and diagonal preconditioning, and no accceleration algorithms ({\it ie.} fast multipole method) or distributed memory execution.
+Here we prototype this principle with the simplest implementation possible: a Johnson-N\'ed\'elec\cite{johnson1980coupling} coupling, mass-matrix and diagonal preconditioning, and no distributed memory execution.
 This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in the software libraries used in this work, in particular, Bempp-cl and FEniCSx.

### 2023-04-06 methods.tex
added citation to new paper with variable permittivity

@@
 
-The implicit solvent model can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_1$ in Figure XX), and the Poisson equation in the solute region ($\Omega_2$ in Figure XX).
+The implicit solvent model\cite{RouxSimonson1999,DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_1$ in Figure XX), and the Poisson equation in the solute region ($\Omega_2$ in Figure XX).
 These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous.
@@
 
-Regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods.
-However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permitivitties.
+Regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods, and have recently been extended to super-Gaussian permitivitties in the solute.\cite{wang2022regularization} However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permitivitties, beyond super-Gaussian descriptions.
 

### 2023-04-09 results.tex
added citation to new paper with variable permittivity
added details on the arginine mesh

@@
 
-As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine (the structure of arginine taken from the protein data bank \cite{bank}).
-We generated surface meshes containing W, X, Y, and Z vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}
-These meshes were inputs to our purely BEM solver, and to create the FEM mesh with pyGAMer,~\cite{lee2020open} which invoked \texttt{tetgen} [citation] with the string \texttt{abcd}.
+As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine.
+The structure of arginine taken from the protein data bank, and parameterized with the Amber\cite{ponder2003force} force field. 
+We generated surface meshes containing 4.1, 6.7, 8.6, 17, and 24.5 vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}
+These densities correspond to a grid scale parameter in Nanoshaper equal to 1.6, 2.0, 2.4, 3.4, and 4.0, respectively, where the grid scale is the reciprocal of the average characteristic length of the triangles.
+The surface meshes were inputs to our purely BEM solver and to create the FEM mesh with pyGAMer,~\cite{lee2020open} which invoked TetGen\cite{hang2015tetgen} with a quality parameter (radius-edge ratio) of 1.0.
 

### 2023-04-10 results.tex
Adding DOFs and Computer SPEC

@@
 
-All runs were done on XX computer with YY specifications.
+All runs were done on Lenovo ThinkStation P620 with AMD Ryzen ThreadRipper PRO 3975WX 32-core 3.5 GHz and 128 GB RAM.
 
@@
 \centering
-\begin{tabular}{c|c|c}
-&Mesh size & $\Delta G_{solv}$\\
-&\AA       &  kcal/mol \\
+\begin{tabular}{c|c|c|c}
+&Mesh size  & Grid points? & $\Delta G_{solv}$\\
+&\AA       & &  kcal/mol \\
 \hline
-\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & -107.6186 \\ 
-& 0.39$\times$0.39$\times$0.39 & -107.8752\\ 
-&0.26$\times$0.26$\times$0.26 & -108.3378\\ 
-&0.195$\times$0.195$\times$0.195 & -108.5837\\ 
-&0.098$\times$0.098$\times$0.098 & -108.8844\\ 
+\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 &  & -107.6186 \\ 
+& 0.39$\times$0.39$\times$0.39 & & -107.8752\\ 
+&0.26$\times$0.26$\times$0.26 & & -108.3378\\ 
+&0.195$\times$0.195$\times$0.195 & & -108.5837\\ 
+&0.098$\times$0.098$\times$0.098 & & -108.8844\\ 
 \hline
-&Mesh dens. & \\
-&vert/\AA$^2$ & \\
+&Mesh dens. & DOFs & $\Delta G_{solv}$\\
+&vert/\AA$^2$   &  &  kcal/mol \\
 \hline
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
-    & 4.1 & -109.933 \\
-FEM-BEM    & 6.7  & -110.238 \\
-coupling    & 8.57  & -109.658 \\
-    & 17 & -109.368 \\
-    & 24.5 & -109.286 \\
+    & 4.1 & 3 491 & -109.933 \\
+FEM-BEM    & 6.7  & 5 787 & -110.238 \\
+coupling    & 8.57  & 8 844 & -109.658 \\
+    & 17 & 19 911 & -109.368 \\
+    & 24.5 & 32 302 & -109.286 \\
 \hline
@@
 \centering
-\begin{tabular}{c|c|c|c|c|c|c}
-Molecule & Mesh size  & $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
-& vert/\AA$^2$ &  kcal/mol & & sec & sec & sec \\
+\resizebox{\textwidth}{!}{\begin{tabular}{c|c|c|c|c|c|c|c}
+Molecule & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
+& DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
 \hline
- 1pgb &  & -300.888 & 826 & 82 & 547 & 629  \\
- 1lyz &  & -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
- 1lyz gs3 & & -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
- 1uxu &  & -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
- 1igt &  &  -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
+ 1pgb  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
+ 1lyz  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
+ 1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
+ 1uxu & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
+ 1igt & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
  \hline
-\end{tabular}
+\end{tabular}}
 \caption{Large tests' results}
@@
 \end{table}
+%
+%\begin{table}
+%\centering
+%\begin{tabular}{c|c|c|c|c|c|c|c|c}
+%Molecule & Mesh size  & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
+%& vert/\AA$^2$ & DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
+%\hline
+% 1pgb &  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
+% 1lyz &  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
+% 1lyz gs3 &  & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
+% 1uxu &  & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
+% 1igt &  & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
+% \hline
+%\end{tabular}
+%\caption{Large tests' results}
+%\label{table:large_variable}
+%\end{table}

### 2023-04-10 results.tex
added apbs grid points

@@
 Table \ref{table:arg_variable} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approach.
-We can see that they are both converging to equivalent values, where the finest meshes agree up to 1.5\% {\color{red} (shouldn't be 0.5\%?)} (0.5 kcal/mol).
+We can see that they are both converging to equivalent values, where the finest meshes agree up to 0.5\% (0.5 kcal/mol).
 
@@
 \begin{tabular}{c|c|c|c}
-&Mesh size  & Grid points? & $\Delta G_{solv}$\\
+&Mesh size  & Grid points & $\Delta G_{solv}$\\
 &\AA       & &  kcal/mol \\
 \hline
-\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 &  & -107.6186 \\ 
-& 0.39$\times$0.39$\times$0.39 & & -107.8752\\ 
-&0.26$\times$0.26$\times$0.26 & & -108.3378\\ 
-&0.195$\times$0.195$\times$0.195 & & -108.5837\\ 
-&0.098$\times$0.098$\times$0.098 & & -108.8844\\ 
+\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & 97$\times$97$\times$97 & -107.6186 \\ 
+& 0.39$\times$0.39$\times$0.39 & 129$\times$129$\times$129 & -107.8752\\ 
+&0.26$\times$0.26$\times$0.26 & 193$\times$193$\times$193& -108.3378\\ 
+&0.195$\times$0.195$\times$0.195 & 257$\times$257$\times$257& -108.5837\\ 
+&0.098$\times$0.098$\times$0.098 & 513$\times$513$\times$513& -108.8844\\ 
 \hline
@@
 \caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS.
-The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.
-Add performance result?}
+The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}
 \label{table:arg2_variable}

### 2023-04-10 methods.tex
added figure of molecule

@@
 
-The implicit solvent model\cite{RouxSimonson1999,DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_1$ in Figure XX), and the Poisson equation in the solute region ($\Omega_2$ in Figure XX).
+The implicit solvent model\cite{RouxSimonson1999,DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson equation in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}).
 These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous.
@@
 Here, $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively, $\kappa$ is the inverse of the Debye length, related with the salt concentration, and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.3\textwidth]{implicit_molecule.pdf}
+\caption{Representation of a molecule in an implicit solvent.}
+\label{fig:implicit_molecule}
+\end{figure}
 

### 2023-04-12 results.tex
worked on large test results

@@
 
-So far, we have only tested the FEM-BEM coupled approach with small structures. Here, we study its behaviour with larger structures to evaluate its applicability in more realistic settings.
+So far, we have only tested the FEM-BEM coupled approach with small structures.
+Here, we study its behaviour with larger structures to evaluate its applicability in more realistic settings, and  in test cases where BEM-BEM coupling is not an alternative.
+Using the same Gaussian permittivity field inside the molecule, we computed the solvation free energy of protein G B1 (955 atoms, PDB code 1pgb), lysozyme (1960 atoms, PDB code 1lyz), the barnase-barstar complex (9464 atoms, PDB code 1x1u), and immunoglobulin G (20148 atoms, PDB code 1igt).
+All structures were parameterized with the Amber\cite{Swanson05} force field using pdb2pqr.\cite{Dolinsky04} The surface was meshed with Nanoshaper\cite{decherchi2013general} considering a grid scale of 1.5, and then used to mesh the solute region with pyGAMer\cite{lee2020open} and TetGen\cite{hang2015tetgen} with a radius-edge ratio of 1.0.
+Solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}, showing that our FEM-BEM coupling method can reach medium-to-large sized proteins on a workstation.
+
+Table \ref{table:large_variable} shows that the iteration count increases with the problem size.
+This is expected for Johnson-N\'ed\'elec, which is the simplest coupling strategy.
+To isolate the effect of the increased iterations in the analysis, we separate timings in ``setup'' and ``solving'' time, where the ``setup'' time is independent of the number of iterations, and the ``solving'' time corresponds to the time spent in the GMRES solver.
+Then, the time-per-iteration in table \ref{table:large_variable} only considers the ``solving'' time.
+Looking at the increase in degrees of freedom, which scales equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, mainly due to the dense nature of the BEM portion of the matrix \textcolor{red}{(check if not using fmm)}.
+On the other hand, the ``solving time per iteration'' scales closer to $\mathcal{O}(N)$.
+This is an indication that the high ``solving time'' is mainly due to the increase in iteration count, and having better conditioned coupling methods, such as the so-called hybrid approach,\cite{betcke2022hybrid} can have a large impact in the time to solution.
+
+Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up most of the available RAM memory (\textcolor{red}{check and rewrite}).
+If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system, but also in the choice of fast algorithms\cite{Wantfmm,Betrckefmm} and parallelization.
 
@@
 \centering
-\resizebox{\textwidth}{!}{\begin{tabular}{c|c|c|c|c|c|c|c}
-Molecule & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
-& DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
+\resizebox{\textwidth}{!}{\begin{tabular}{c|c|c|c|c|c|c|c|c}
+Molecule & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Solv. time per & Total Time \\
+& DOFs & DOFs &  kcal/mol & & [sec] & [sec] & iter. [sec] & [sec] \\
 \hline
- 1pgb  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
- 1lyz  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
- 1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
- 1uxu & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
- 1igt & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
+ 1pgb  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 0.6 & 6 629  \\
+ 1lyz  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1.2 & 1 970  \\
+ %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
+ 1x1u & 263 181 & 81 258 \textcolor{red}{82360} &  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
+ 1igt & 597 575 & 187 712 \textcolor{red}{189960} &   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
  \hline
 \end{tabular}}
-\caption{Large tests' results}
+\caption{Results for larger structures with a variable permitivitty.}
 \label{table:large_variable}

### 2023-04-19 results.tex
worked on results section

@@
 
-All runs were done on Lenovo ThinkStation P620 with AMD Ryzen ThreadRipper PRO 3975WX 32-core 3.5 GHz and 128 GB RAM.
+All runs were done on a Lenovo ThinkStation P620 with AMD Ryzen ThreadRipper PRO 3975WX (32-core and 3.5 GHz) and 128 GB RAM.
 
@@
 Then, for FEM-BEM, the integral over $\Gamma$ in Eq.
-\eqref{eq:phi_reac} corresponds to the trace of the solution vector.
+\eqref{eq:phi_reac} corresponds to the trace of the solution vector from Eq.
+\eqref{eq:fembem_matrix}.
 
@@
   \includegraphics[width=0.6\linewidth]{DolfinX_Sphere_const_coeff_error.png}
-  \caption{Error for the Kirkwood sphere.}
+  \caption{Error for the Kirkwood sphere. \textcolor{red}{Chris: I would remove the titles from the figs (applies to other figs)}}
   \label{fig:error_sphere}
@@
 The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation.
+\textcolor{red}{Chris: I though BEM-BEM outperformed FEM-BEM in total time.
+Am I wrong there?}
 
@@
 
-\subsection*{\sffamily \large Convergence and performance for arginine}
+\subsection*{\sffamily \large Convergence for arginine with APBS}
 
@@
 We can see that they are both converging to equivalent values, where the finest meshes agree up to 0.5\% (0.5 kcal/mol).
+The coarsest meshes used in both cases are within the recommended densities for accurate solvation energy simulations with constant permittivity.
+For example, a finite difference mesh with $h$=0.5 \AA~ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of substracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per \AA$^2$ gives acceptable results when computing binding and solvation energies.
+We see a jump in the solvation energy for the FEM-BEM results going from 4.1 to 6.7 vertices per \AA$^2$, but later the energy monotonically decreases, converging to a solution.
+This is an indication that mesh requirements for variable permitivities may be tighter than with a constant permittivity, even though the jump in dielectric constant accross the molecular surface is usually smaller.
 
 Figure \ref{fig:arg2_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
+\textcolor{red}{Chris: if we don't include Fig.
+\ref{fig:arg2_variable}, we should remove this paragraph.
+I believe that if we show performance for fem-bem, a reviewer might be tempted to ask it for APBS too, which might be difficult.}
 
@@
 The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}
-\label{table:arg2_variable}
+\label{table:arg_variable}
 \end{table}
@@
 %Can we make this only two plots?
-}
+\textcolor{red}{Chris: not sure if we want to show performance here. Reviewers may ask for performance with APBS too, and those were run on a different machine, and has a number of steps.}}
 \label{fig:arg2_variable}
@@
 Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up most of the available RAM memory (\textcolor{red}{check and rewrite}).
-If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system, but also in the choice of fast algorithms\cite{Wantfmm,Betrckefmm} and parallelization.
+If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system, but also in the choice of fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and parallelization.
 

### 2023-04-19 conclusion.tex
first attempt at conclusion

This paper presents the first implementation of a FEM-BEM coupling approach to solve the Poisson-Boltzmann equation for molecular electrostatics. This brings the best of both worlds: the accuracy and efficiency of BEM to exactly enforce the boundary conditions at infinity, and the flexibility of FEM to account for space variations of the material properties and nonlinearities. After presenting verification results for a sphere and arginine with a constant permittivity inside the solute, we showcased our implementation with an advanced modeling technique that considers a Gaussian-varying permittivities in a confined region, comparing with the widely-used APBS software. The final scaling results for larger molecules start from protein G B1 (955 atoms) and go up to immunoglobulin G (20 148 atoms), proving the applicability of this approach for realistic problems. Even though our implementation was able to reach medium-to-large systems, we recongnize the need of further research towards opmtimizing the coupling technique, acceleration algorithms, and parallel execution, specially as we look towards much larger solutes, like viruses. We hope this proof-of-concept work will serve as motivation for future model development that considers space varying permittivities and Debye lengths, and mixed linear-nonlinear techniques, specially for highly-charged systems, like nucleic acids.

### 2023-04-20 results.tex
first attempt at conclusion
Replies for the comments

@@
   \centering
-  \includegraphics[width=0.6\linewidth]{DolfinX_Sphere_const_coeff_error.png}
-  \caption{Error for the Kirkwood sphere. \textcolor{red}{Chris: I would remove the titles from the figs (applies to other figs)}}
+  \includegraphics[width=0.5\linewidth]{DolfinX_Sphere_const_coeff_error.png}
+  \caption{Error for the Kirkwood sphere.}
   \label{fig:error_sphere}
@@
 The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation.
-\textcolor{red}{Chris: I though BEM-BEM outperformed FEM-BEM in total time.
-Am I wrong there?}
+\textcolor{red}{Chris: I thought BEM-BEM outperformed FEM-BEM in total time.
+Am I wrong there?} \textcolor{blue}{Michal: Not for this formulation of BEM-BEM since we have hypersingular operator.
+But you can see that for denser meshes we should outperform it.}
 
@@
 \centering
-   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine2_const_coeff_error.png}
+   \includegraphics[width=0.5\linewidth]{DolfinX_Arginine2_const_coeff_error.png}
 %   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine_const_coeff_error_11.png}
@@
 
+\subsection*{\sffamily \large Convergence for arginine with APBS}
+
 We used Equation \eqref{eq:varying_eps} to generate dielectric maps, which we ran on APBS~\cite{BakerETal2001} for comparison. 
 We chose APBS because it provides an easy interface to control dielectric maps, in order to ensure their agreement with the maps imposed in our FEM-BEM coupled approach.
-
-\subsection*{\sffamily \large Convergence for arginine with APBS}
 
@@
 \ref{fig:arg2_variable}, we should remove this paragraph.
-I believe that if we show performance for fem-bem, a reviewer might be tempted to ask it for APBS too, which might be difficult.}
-
+I believe that if we show performance for fem-bem, a reviewer might be tempted to ask it for APBS too, which might be difficult.}  \textcolor{blue}{Michal: I completely agree.
+We were even talking about not putting them, but just for our information, we kept it for now.
+They weren't going to be in the final version}
 \begin{table}
@@
 Then, the time-per-iteration in table \ref{table:large_variable} only considers the ``solving'' time.
-Looking at the increase in degrees of freedom, which scales equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, mainly due to the dense nature of the BEM portion of the matrix \textcolor{red}{(check if not using fmm)}.
+Looking at the increase in degrees of freedom, which scales equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, mainly due to the dense nature of the BEM portion of the matrix \textcolor{red}{(check if not using fmm  \textcolor{blue}{we are using FMM})}.
 On the other hand, the ``solving time per iteration'' scales closer to $\mathcal{O}(N)$.
@@
 
-Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up most of the available RAM memory (\textcolor{red}{check and rewrite}).
+Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up most of the available RAM memory (\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}).
 If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system, but also in the choice of fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and parallelization.
@@
  %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
- 1x1u & 263 181 & 81 258 \textcolor{red}{82360} &  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
- 1igt & 597 575 & 187 712 \textcolor{red}{189960} &   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
+ 1x1u & 263 181 & 81 258 \textcolor{red}{82360} \textcolor{blue}{???}&  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
+ 1igt & 597 575 & 187 712 \textcolor{red}{189960}  \textcolor{blue}{???}&   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
  \hline

### 2023-04-20 main.tex
worked on results section
first attempt at conclusion
minor edits

@@
 \author{Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Christopher D.
-Cooper\thanks{Department of Mechanical Engineering, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}, Matthew W.
+Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}, Matthew W.
 Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}}
@@
 
-\section*{\sffamily \Large RESULTS}
+\section*{\sffamily \Large RESULTS AND DISCUSSION}
 \input{results}
@@
 
-\section*{\sffamily \Large First-order heading}
+%\section*{\sffamily \Large First-order heading}
 
@@
 
-\subsection*{\sffamily \large Second-order heading}
+%\subsection*{\sffamily \large Second-order heading}
 
-\subsubsection*{\sffamily \normalsize Third-order heading}
+%\subsubsection*{\sffamily \normalsize Third-order heading}
 
-{\sffamily \small Fourth-order heading}\\
+%{\sffamily \small Fourth-order heading}\\
 
-\section*{\sffamily \Large DISCUSSION}
+%\section*{\sffamily \Large DISCUSSION}
 
@@
 \section*{\sffamily \Large CONCLUSIONS}
-
+\input{conclusion}
 %((Place Conclusions here.))

### 2023-04-20 results.tex
minor edits

@@
 
-For very large grid sizes the user can enable FMM assembly which internally is handled in Bempp-cl through an interface to the Exafmm-t FMM library.
+For very large grid sizes the user can enable fast multipole method (FMM) assembly which internally is handled in Bempp-cl through an interface to the Exafmm-t FMM library.
 For $N$ surface elements this reduces the memory and computational complexity from $\mathcal{O}(N^2)$ in the dense assembly case to $\mathcal{O}(N)$ in the FMM case, making large boundary element problems tractable on standard workstations.
@@
 The solvation energy computed with the two schemes is presented by Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
-Then, Figure \ref{fig:arg2_constant_time_iter} compares the iteration count and time-to-solution.
+Figure \ref{fig:arg2_constant_time_iter} compares the iteration count and time-to-solution.
 The left plot shows that using only BEM outperforms the coupled FEM-BEM approach in terms of iterations count.
 However, if we look at the total time that solvers take to obtain the solution, we can see the advantage of using the FEM-BEM coupling.
-The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation.
-\textcolor{red}{Chris: I thought BEM-BEM outperformed FEM-BEM in total time.
+The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM \textcolor{red}{true?}).
+Regardless, timings for FEM-BEM coupling scale much worse with size than its pure BEM counterpart, indicating that BEM-BEM coupling is better for larger problems.
+%\textcolor{red}{Chris: I thought BEM-BEM outperformed FEM-BEM in total time.
 Am I wrong there?} \textcolor{blue}{Michal: Not for this formulation of BEM-BEM since we have hypersingular operator.
@@
 %  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
-  \caption{Iteration count (left) and time-to-solution (right) for Arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
+  \caption{Iteration count (left) and time-to-solution (right) for arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
 %NOTE: x axis differ between top and bottom.
@@
 Solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}, showing that our FEM-BEM coupling method can reach medium-to-large sized proteins on a workstation.
+For these larger structures we enabled the FMM capabilities of Bempp-cl.
 
@@
 To isolate the effect of the increased iterations in the analysis, we separate timings in ``setup'' and ``solving'' time, where the ``setup'' time is independent of the number of iterations, and the ``solving'' time corresponds to the time spent in the GMRES solver.
-Then, the time-per-iteration in table \ref{table:large_variable} only considers the ``solving'' time.
-Looking at the increase in degrees of freedom, which scales equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, mainly due to the dense nature of the BEM portion of the matrix \textcolor{red}{(check if not using fmm  \textcolor{blue}{we are using FMM})}.
-On the other hand, the ``solving time per iteration'' scales closer to $\mathcal{O}(N)$.
+Then, the time-per-iteration in Table \ref{table:large_variable} only considers the ``solving'' time.
+Looking at the increase in degrees of freedom (DOFs), which grows equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, but represents the smalle fraction of the total time.
+On the other hand, the ``solving time per iteration'' scales closer to $\mathcal{O}(N)$, which is expected, as we are using a FMM for the BEM portion of the matrix.
 This is an indication that the high ``solving time'' is mainly due to the increase in iteration count, and having better conditioned coupling methods, such as the so-called hybrid approach,\cite{betcke2022hybrid} can have a large impact in the time to solution.
 
-Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up most of the available RAM memory (\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}).
-If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system, but also in the choice of fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and parallelization.
+Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up half of the available RAM memory \textcolor{red}{check}.
+%(\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}). 
+If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system, but also in the optimization of our fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and parallelization.
 

### 2023-04-21 main.tex
Checked result section

@@
 
+\usepackage{hyperref}
+
 \definecolor{background-color}{gray}{0.98}
@@
 \title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
-\author{Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Christopher D.
+\author{Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, \\ Christopher D.
 Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}, Matthew W.

### 2023-04-21 results.tex
Checked result section

@@
 
-For the finite element computations, we use the software package FEniCSx while for the boundary element computations we use Bempp-cl together with Exafmm-t.
+For the finite element computations, we use the software package FEniCSx while for the boundary element computations, we use Bempp-cl together with Exafmm-t.
 FEniCSx is the successor of the widely used FEniCS finite element library.
 It provides a convenient Python interface, in which problems are described using UFL (Unified Form Language), a convenient domain-specific language specifically designed for finite element discretisations of partial differential equations.
-During assembly the UFL description is transformed into efficient low-level C++ code and just-in-time compiled.
+During assembly, the UFL description is transformed into efficient low-level C++ code and just-in-time compiled.
 Bempp-cl is a Python package that uses low-level OpenCL kernels written in C99 to provide optimised assembly routines.
@@
 The corresponding translation work is handled opaquely and the user only needs to deal with high-level interfaces of FEniCSx operators, Bempp-cl operators, and trace operators.
-FMM assembly fits automatically into this framework and can be enabled or disabled as simple configuration option.
+FMM assembly fits automatically into this framework and can be enabled or disabled as a simple configuration option.
 
-Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (PROVIDE LINK), and all codes used in this sections are simple Jupyter Notebooks that can be reproducibly executed in this provided Docker image.
+Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used in this sections are simple Jupyter Notebooks that can be reproducibly executed in this provided Docker image.
 
@@
 However, if we look at the total time that solvers take to obtain the solution, we can see the advantage of using the FEM-BEM coupling.
-The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM \textcolor{red}{true?}).
+The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM).
 Regardless, timings for FEM-BEM coupling scale much worse with size than its pure BEM counterpart, indicating that BEM-BEM coupling is better for larger problems.

### 2023-04-24 results.tex
30% memory instead of 50%

@@
 
-Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up half of the available RAM memory \textcolor{red}{check}.
+Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up 30\% of the available RAM memory \textcolor{red}{check}.
 %(\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}). 

### 2023-04-24 results.tex
Typo and references

@@
 
-For the finite element computations, we use the software package FEniCSx while for the boundary element computations, we use Bempp-cl together with Exafmm-t.
+For the finite element computations, we use the software package FEniCSx~\cite{BasixJoss} while for the boundary element computations, we use Bempp-cl~\cite{BetckeScroggs2021} together with Exafmm-t.
 FEniCSx is the successor of the widely used FEniCS finite element library.
-It provides a convenient Python interface, in which problems are described using UFL (Unified Form Language), a convenient domain-specific language specifically designed for finite element discretisations of partial differential equations.
+It provides a convenient Python interface, describing problems using Unified Form Language (UFL), a convenient domain-specific language specifically designed for finite element discretisations of partial differential equations.
 During assembly, the UFL description is transformed into efficient low-level C++ code and just-in-time compiled.

### 2023-04-24 main.tex
Changes from the meeting on 24/04
Order of Authors and removed unnecessary plots

@@
 \title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
-\author{Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, \\ Christopher D.
-Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}, Matthew W.
-Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}}
+\author{Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Matthew W.
+Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Christopher D.
+Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}}
 

### 2023-04-24 results.tex
Changes from the meeting on 24/04
Order of Authors and removed unnecessary plots

@@
 
-Figure \ref{fig:arg2_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
+%Figure \ref{fig:arg2_variable} contains the performance results of this test case, where we distinguish the iteration count from the calculation in dissolved and vacuum states.
 \textcolor{red}{Chris: if we don't include Fig.
@@
 
+%%\begin{figure}
+%%\centering
+%%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
+%%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
+%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
+%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
+%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
+%%\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.
+%Can we make this only two plots?
+%%}
+%%\label{fig:arg_variable}
+%%\end{figure}
+%
 %\begin{figure}
 %\centering
-%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
-%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
-%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
-%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
-%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
+%% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
+%% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
+%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
+%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_set_time.png}
+%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
 %\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.
 %Can we make this only two plots?
-%}
-%\label{fig:arg_variable}
+%\textcolor{red}{Chris: not sure if we want to show performance here. Reviewers may ask for performance with APBS too, and those were run on a different machine, and has a number of steps.}}
+%\label{fig:arg2_variable}
 %\end{figure}
-
-\begin{figure}
-\centering
-% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
-% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
-\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
-\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_set_time.png}
-\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
-\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.
-%Can we make this only two plots?
-\textcolor{red}{Chris: not sure if we want to show performance here. Reviewers may ask for performance with APBS too, and those were run on a different machine, and has a number of steps.}}
-\label{fig:arg2_variable}
-\end{figure}
 
@@
  %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
- 1x1u & 263 181 & 81 258 \textcolor{red}{82360} \textcolor{blue}{???}&  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
- 1igt & 597 575 & 187 712 \textcolor{red}{189960}  \textcolor{blue}{???}&   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
+ 1x1u & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
+ 1igt & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
  \hline

### 2023-04-24 main.tex
first try at abstract

@@
 \title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
-\author{Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, Matthew W.
-Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Timo Betcke\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Erik Burman\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, Christopher D.
-Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}}
+\author{Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, 
+    Matthew W. Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
+    Timo Betcke\footnotemark[2],~\\%\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
+    Erik Burman\footnotemark[2],~%\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
+    Christopher D. Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}}
 
@@
 \begin{abstract}
-Abstract
+The Poisson-Boltzmann equation is widely used to model electrostatics in molecular systems.
+Available software packages solve it using finite difference, finite element, and boundary element methods, where the latter is attractive due to the accurate representation of the molecular surface and partial charges, and exact enforcement of the boundary conditions at infinity.
+However, the boundary element method is limited to linear equations and piece-wise constant variations of the material properties.
+In this work, we present a scheme that couples finite and boundary elements for the Poisson-Boltzmann equation, where the finite element method is applied in a confined {\it solute} region, and the boundary element method in the external {\it solvent} region.
+As a proof-of-concept exercise, we used the simplest methods available: Johnson-N\'ed\'elec coupling with mass matrix and diagonal preconditioning, implemented in the Bempp-cl and FEniCSx libraries from a simple Python interface.
+We showcased our implementation by computing the polar component of the solvation free energy of a set of molecules using a constant and a Gaussian-varying permittivity.
+First, we validated our implementation against the finite differece code APBS (to 0.5\%), and then, we show scaling from protein G B1 (955 atoms) up to immunoglobuling G (20 148 atoms).
+For small problems we saw that the coupled method was efficient, outperforming a purely boundary integral approach, but scaled worse with size.
+For Gaussian-varying permittivities, which are beyond the applicability of boundary elements, we were able to run medium to large problems on a single workstation.
+However, our results illustrate the need to improve conditioning and incorporate distributed memory parallelism as we aim at larger systems.
+We hope this work will serve as inspiration for future developments that consider space-varying field parameters, and mixed linear-nonlinear schemes for molecular electrostatics with implicit solvent models.
 \end{abstract}

### 2023-04-25 main.tex
added graphical abstract

@@
 \begin{minipage}{1.0\textwidth}
-\includegraphics[width=50mm,height=50mm]{adaptive_mesh_fig.pdf} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
+\includegraphics[width=50mm,height=50mm]{graphical_abstract_fem-bem.png} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
 %\includegraphics[width=110mm,height=20mm]{cc.eps}
 \\
-(75 words.) Images for the graphical Table of Contents should capture the essence of a paper, displaying a figure, plot, or scheme that is central to the theme of the manuscript.
-The text of the graphical Table of Contents is meant for the non-specialist and should ideally contain no obscure jargon or mathematical symbols / equations, but should attempt to convey the gist of the paper in everyday terms, while remaining consistent with accepted standards of scientific literature.
+    The boundary element method is, in many cases, the numerical algorithm of choice to solve the Poisson-Boltzmann equation for molecular electrostatics.
+However, this technique is limited to linear equations and piece-wise constant variations of the field parameters.
+Here, we overcome such limitations by coupling it with a finite element method, implemented with Bempp-cl and FEniCSx libraries through simple Python interfaces.
+This results in an accurate, flexible, and easy-to-use computational tool for model development.
 \end{minipage}

### 2023-04-25 main.tex
resolved last comments and added acknowledgements

@@
 However, this technique is limited to linear equations and piece-wise constant variations of the field parameters.
-Here, we overcome such limitations by coupling it with a finite element method, implemented with Bempp-cl and FEniCSx libraries through simple Python interfaces.
-This results in an accurate, flexible, and easy-to-use computational tool for model development.
+Here, we overcome such limitations by coupling it with a finite element method, implemented using the Bempp-cl and FEniCSx libraries through simple Python interfaces.
+This results in an efficient, accurate, flexible, and easy-to-use computational tool for model development.
 \end{minipage}
@@
 
+CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.
 %((Place Acknowledgments here))

### 2023-04-25 results.tex
resolved last comments and added acknowledgements

@@
 
-Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up 30\% of the available RAM memory \textcolor{red}{check}.
+Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up 30\% of the available RAM memory.
 %(\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}). 

### 2023-04-26 main.tex
added link to github
minor update

@@
 \\
-    The boundary element method is, in many cases, the numerical algorithm of choice to solve the Poisson-Boltzmann equation for molecular electrostatics.
+    The boundary element method is a popular numerical algorithm to solve the Poisson-Boltzmann equation for molecular electrostatics.
 However, this technique is limited to linear equations and piece-wise constant variations of the field parameters.
@@
 %((Place Acknowledgments here))
+
+\subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
+All codes to reproduce the results of this manuscript can be found in the Github repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}
 

### 2023-04-27 conclusion.tex
Updated Results with tol 1e-4

@@
 This brings the best of both worlds: the accuracy and efficiency of BEM to exactly enforce the boundary conditions at infinity, and the flexibility of FEM to account for space variations of the material properties and nonlinearities.
-After presenting verification results for a sphere and arginine with a constant permittivity inside the solute, we showcased our implementation with an advanced modeling technique that considers a Gaussian-varying permittivities in a confined region, comparing with the widely-used APBS software.
+After presenting verification results for a sphere and arginine with a constant permittivity inside the solute, we showcased our implementation with an advanced modeling technique that considers Gaussian-varying permittivities in a confined region, compared with the widely-used APBS software.
 The final scaling results for larger molecules start from protein G B1 (955 atoms) and go up to immunoglobulin G (20 148 atoms), proving the applicability of this approach for realistic problems.
-Even though our implementation was able to reach medium-to-large systems, we recongnize the need of further research towards opmtimizing the coupling technique, acceleration algorithms, and parallel execution, specially as we look towards much larger solutes, like viruses.
-We hope this proof-of-concept work will serve as motivation for future model development that considers space varying permittivities and Debye lengths, and mixed linear-nonlinear techniques, specially for highly-charged systems, like nucleic acids.
+Even though our implementation was able to reach medium-to-large systems, we recongnize the need for further research towards optimizing the coupling technique, acceleration algorithms, and parallel execution, especially as we look towards much larger solutes, like viruses.
+We hope this proof-of-concept work will serve as motivation for future model development that considers space-varying permittivities and Debye lengths, and mixed linear-nonlinear techniques, especially for highly-charged systems, like nucleic acids.

### 2023-04-27 intro.tex
Updated Results with tol 1e-4

@@
-In biologically relevant settings, the structure and function of biomolecules is largely determined by the surrounding water, which usually contains salt. 
+In biologically relevant settings, the structure and function of biomolecules are largely determined by the surrounding water, which usually contains salt. 
 To describe these systems accurately, we need to account for the solvent correctly, which has given rise to a wide range of models.\cite{onufriev2018water}
@@
 
-The implicit-solvent model for electrostatics describes the dissolved molecule as a infinite medium with a low-dielectric solute-shaped cavity, which contains a charge distribution from the partial charges --- usually a sum of Dirac deltas at the atom's locations.
+The implicit-solvent model for electrostatics describes the dissolved molecule as an infinite medium with a low-dielectric solute-shaped cavity, which contains a charge distribution from the partial charges --- usually a sum of Dirac deltas at the atom's locations.
 The outer solvent region is represented with a high dielectric, and considers the presence of salt.
@@
 The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
-In particular, the boundary element method (BEM) has proven to be very efficient for high accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.
-However, BEM is limited to constant material properties in each region, and the linear version of the PBE. 
+In particular, the boundary element method (BEM) has proven to be very efficient for high-accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.
+However, BEM is limited to constant material properties in each region and the linear version of the PBE. 
 Even though these limitations are acceptable in a wide range of applications, there are cases when BEM falls short, for example, if a variable permittivity is required inside the solute \cite{grant2001smooth,li2013dielectric}, or the solute is highly charged such that the linear approximation breaks\cite{FogolariETal1999}.
@@
 The present article describes a methodology to overcome some of those limitations, by coupling finite and boundary elements methods.
-This approach brings the best of both worlds: the flexibility of FEM and efficiency of BEM, all in an accurate description of the solute molecule.
+This approach brings the best of both worlds: the flexibility of FEM and the efficiency of BEM, all in an accurate description of the solute molecule.
 FEM-BEM coupling is a popular technique in the context of mixed linear-nonlinear models,\cite{carstensen1995coupling,aurada2013classical} fracture mechanics,\cite{aour2007coupled} fluid-structure interaction,\cite{estorff1991fem} acoustics,\cite{hiptmair2006stabilized} and electromagnetics.\cite{matsuoka1988calculation,hiptmair2008stabilized,bruckner20123d}
@@
 This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in the software libraries used in this work, in particular, Bempp-cl and FEniCSx.
-These libraries are designed for ease-of-use through a simple Python interface, making them ideal tools to explore and improve computational efficiency, towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}
+These libraries are designed for ease of use through a simple Python interface, making them ideal tools to explore and improve computational efficiency, towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}
 We hope this work will inspire research along these lines.

### 2023-04-27 main.tex
Updated Results with tol 1e-4

@@
 We showcased our implementation by computing the polar component of the solvation free energy of a set of molecules using a constant and a Gaussian-varying permittivity.
-First, we validated our implementation against the finite differece code APBS (to 0.5\%), and then, we show scaling from protein G B1 (955 atoms) up to immunoglobuling G (20 148 atoms).
+First, we validated our implementation against the finite difference code APBS (to 0.5\%), and then, we show scaling from protein G B1 (955 atoms) up to immunoglobulin G (20 148 atoms).
 For small problems we saw that the coupled method was efficient, outperforming a purely boundary integral approach, but scaled worse with size.

### 2023-04-27 methods.tex
worked on results section
Additional comment while reading
Typo and references
resolved last comments and added acknowledgements
Updated Results with tol 1e-4

@@
 
-Regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods, and have recently been extended to super-Gaussian permitivitties in the solute.\cite{wang2022regularization} However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permitivitties, beyond super-Gaussian descriptions.
+Regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods, and have recently been extended to super-Gaussian permittivities in the solute.\cite{wang2022regularization} However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permittivities, beyond super-Gaussian descriptions.
 
-A common quantity of interest in implicit solvent models is the solvation free energy, which the change in Gibbs free energy as the molecule moves from vacuum into the solvent.
+A common quantity of interest in implicit solvent models is the solvation free energy, which is the change in Gibbs free energy as the molecule moves from the vacuum into the solvent.
 Considering the charge distribution $\rho$ consists of point charges, this can be calculated as
@@
 
-Several possible boundary integral formulations of Equation \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon ºand Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
+Several possible boundary integral formulations of Equation \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon and Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
 Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
@@
 \end{align}
+%\textcolor{blue}{Michal: We only have $\phi_2$ and $\lambda_2$ and the solution later is from $\phi_1$ and $\lambda_1$!!!}
+
 %
@@
 %
-where $\mathbf{r}\in\Omega_1$.
+where $\mathbf{r}\in\Omega_1$, and we can obtain $\phi_1$ and $\lambda_1$ from $\phi_2$ and $\lambda_2$ by applying the interface conditions from Eq. \eqref{eq:pbe}.
 This is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
@@
 %
-A finite element method (FEM) is more suitable for such case.
+A finite element method (FEM) is more suitable for such a case.
 
 The coupling of finite element (FEM) and boundary element (BEM) methods is a widely used approach to solve multi-physical problems on unbounded domains [citation?], as it takes advantage of both methods.
-On one hand, the BEM satifies the infinite boundary conditions exactly when they decay to zero, and only approximates boundary conditions on surfaces, hence, it is commonly used for problems involving infinite or semi-infinite domains.
+On one hand, the BEM satisfies the infinite boundary conditions exactly when they decay to zero, and only approximates boundary conditions on surfaces, hence, it is commonly used for problems involving infinite or semi-infinite domains.
 On the other hand, the FEM is known for its robustness and universal applicability, even for problems of inhomogeneous or non-linear nature.
@@
 Using the above definition the discrete problem in Eq.~\eqref{eq:standard_fem_bem} can be written in the following matrix form
-\begin{align*}
+\begin{align}\label{eq:fembem_matrix}
 \begin{bmatrix}
 \epsilon_1 A &  - \epsilon_1 M^T \\  
-\left(\tfrac12 I + K \right) \gamma &  \tfrac{\epsilon_1}{\epsilon_2} V 
+\left(\tfrac12 I - K \right) \gamma &  \tfrac{\epsilon_1}{\epsilon_2} V 
 \end{bmatrix}
@@
 \end{bmatrix}.
-\end{align*}
+\end{align}

### 2023-04-27 results.tex
Updated Results with tol 1e-4

@@
 We then export the corresponding boundary mesh into Bempp-cl and assemble the boundary spaces there.
-Bempp-cl provides numerical trace operators that can translate from the degree of freedom (dof) representation in FEniCSx to the dof representation in Bempp-cl.
+Bempp-cl provides numerical trace operators that can translate from the degree of freedom (DOF) representation in FEniCSx to the dof representation in Bempp-cl.
 The corresponding translation work is handled opaquely and the user only needs to deal with high-level interfaces of FEniCSx operators, Bempp-cl operators, and trace operators.
@@
 In the solvent region, we used the permittivity of water ($\epsilon_2$=80) and an inverse of the Debye length of $\kappa=0.125$ \AA$^{-1}$.
-As in these cases there is an analytical solution for $\phi_c$ in Eq.
+As in these cases, there is an analytical solution for $\phi_c$ in Eq.
 \eqref{eq:phic}, we compute $\phi_r$ with Eq.
@@
 As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine.
-The structure of arginine taken from the protein data bank, and parameterized with the Amber\cite{ponder2003force} force field. 
+The structure of arginine was taken from the protein data bank, and parameterized with the Amber\cite{ponder2003force} force field. 
 We generated surface meshes containing 4.1, 6.7, 8.6, 17, and 24.5 vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}
-These densities correspond to a grid scale parameter in Nanoshaper equal to 1.6, 2.0, 2.4, 3.4, and 4.0, respectively, where the grid scale is the reciprocal of the average characteristic length of the triangles.
+These densities correspond to a grid-scale parameter in Nanoshaper equal to 1.6, 2.0, 2.4, 3.4, and 4.0, respectively, where the grid scale is the reciprocal of the average characteristic length of the triangles.
 The surface meshes were inputs to our purely BEM solver and to create the FEM mesh with pyGAMer,~\cite{lee2020open} which invoked TetGen\cite{hang2015tetgen} with a quality parameter (radius-edge ratio) of 1.0.
 
-The solvation energy computed with the two schemes is presented by Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
+The solvation energy computed with the two schemes is presented in Figure \ref{fig:arg_constant_energy}, which, as expected, converges to a similar answer as the mesh is refined.
 Figure \ref{fig:arg2_constant_time_iter} compares the iteration count and time-to-solution.
-The left plot shows that using only BEM outperforms the coupled FEM-BEM approach in terms of iterations count.
+The left plot shows that using only BEM outperforms the coupled FEM-BEM approach in terms of the iteration count.
 However, if we look at the total time that solvers take to obtain the solution, we can see the advantage of using the FEM-BEM coupling.
 The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM).
-Regardless, timings for FEM-BEM coupling scale much worse with size than its pure BEM counterpart, indicating that BEM-BEM coupling is better for larger problems.
+Regardless, timings for the FEM-BEM coupling scale are much worse with size than its pure BEM counterpart, indicating that BEM-BEM coupling is better for larger problems.
 %\textcolor{red}{Chris: I thought BEM-BEM outperformed FEM-BEM in total time.
@@
 
-In contrast to a purely BEM approach, FEM-BEM coupling gives flexibility to consider space-varying field parameters. 
+In contrast to a purely BEM approach, FEM-BEM coupling gives the flexibility to consider space-varying field parameters. 
 A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom,\cite{grant2001smooth} which has shown enhanced accuracy in some applications, like pKa calculations.\cite{li2013dielectric}
@@
 The coarsest meshes used in both cases are within the recommended densities for accurate solvation energy simulations with constant permittivity.
-For example, a finite difference mesh with $h$=0.5 \AA~ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of substracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per \AA$^2$ gives acceptable results when computing binding and solvation energies.
+For example, a finite difference mesh with $h$=0.5 \AA~ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of subtracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per \AA$^2$ gives acceptable results when computing binding and solvation energies.
 We see a jump in the solvation energy for the FEM-BEM results going from 4.1 to 6.7 vertices per \AA$^2$, but later the energy monotonically decreases, converging to a solution.
-This is an indication that mesh requirements for variable permitivities may be tighter than with a constant permittivity, even though the jump in dielectric constant accross the molecular surface is usually smaller.
+This is an indication that mesh requirements for variable permittivities may be tighter than with a constant permittivity, even though the jump in dielectric constant across the molecular surface is usually smaller.
 
@@
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
-    & 4.1 & 3 491 & -109.933 \\
-FEM-BEM    & 6.7  & 5 787 & -110.238 \\
-coupling    & 8.57  & 8 844 & -109.658 \\
-    & 17 & 19 911 & -109.368 \\
-    & 24.5 & 32 302 & -109.286 \\
+    & 4.1 & 3 491 & -109.907 \\
+FEM-BEM    & 6.7  & 5 787 & -110.199 \\
+coupling    & 8.57  & 8 844 & -109.582 \\
+    & 17 & 19 911 & -109.350 \\
+    & 24.5 & 32 302 & -109.265 \\
 \hline
@@
 All structures were parameterized with the Amber\cite{Swanson05} force field using pdb2pqr.\cite{Dolinsky04} The surface was meshed with Nanoshaper\cite{decherchi2013general} considering a grid scale of 1.5, and then used to mesh the solute region with pyGAMer\cite{lee2020open} and TetGen\cite{hang2015tetgen} with a radius-edge ratio of 1.0.
-Solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}, showing that our FEM-BEM coupling method can reach medium-to-large sized proteins on a workstation.
-For these larger structures we enabled the FMM capabilities of Bempp-cl.
+Solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}, showing that our FEM-BEM coupling method can reach medium-to-large-sized proteins on a workstation.
+For these larger structures, we enabled the FMM capabilities of Bempp-cl.
 
@@
 Then, the time-per-iteration in Table \ref{table:large_variable} only considers the ``solving'' time.
-Looking at the increase in degrees of freedom (DOFs), which grows equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, but represents the smalle fraction of the total time.
-On the other hand, the ``solving time per iteration'' scales closer to $\mathcal{O}(N)$, which is expected, as we are using a FMM for the BEM portion of the matrix.
-This is an indication that the high ``solving time'' is mainly due to the increase in iteration count, and having better conditioned coupling methods, such as the so-called hybrid approach,\cite{betcke2022hybrid} can have a large impact in the time to solution.
+Looking at the increase in degrees of freedom (DOFs), which grows equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, but represents the smaller fraction of the total time.
+On the other hand, the ``solving time per iteration'' scales closer to $\mathcal{O}(N)$, which is expected, as we are using an FMM for the BEM portion of the matrix.
+This is an indication that the high ``solving time'' is mainly due to the increase in iteration count, and having better-conditioned coupling methods, such as the so-called hybrid approach,\cite{betcke2022hybrid} can have a large impact on the time to solution.
 
@@
 %(\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}). 
-If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system, but also in the optimization of our fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and parallelization.
+If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system but also in the optimization of our fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and parallelization.
 
@@
 \hline
- 1pgb  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 0.6 & 6 629  \\
- 1lyz  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1.2 & 1 970  \\
+ 1pgb  & 29 434 &  10 058 &  -300.389 & 613 & 89 & 410 & 0.67 & 702  \\
+ 1lyz  & 56 114 & 18 606 &  -597.515 & 724 & 334 & 921  & 1.27 & 1 255   \\
  %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
- 1x1u & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 3.91 & 24 540  \\
- 1igt & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 & 7.67  &  105 400   \\
+ 1x1u & 263 181 & 81 258 &  -1 975.068 & 1 911 & 8 240 & 7 410 & 3.88 & 15 650  \\
+ 1igt & 597 575 & 187 712 &   -3 279.907 & 1 974 & 40 930 & 15 600 & 7.9  &  56 530   \\
  \hline
 \end{tabular}}
-\caption{Results for larger structures with a variable permitivitty.}
+\caption{Results for larger structures with a variable permittivity.}
 \label{table:large_variable}

### 2023-05-01 results.tex
Updated results, comparison for tol = 1e-4 and 1e-5

@@
   \centering
-  \includegraphics[width=0.5\linewidth]{DolfinX_Sphere_const_coeff_error.png}
-  \caption{Error for the Kirkwood sphere.}
+  \includegraphics[width=0.45\linewidth]{DolfinX_Sphere_const_coeff_error_1e-4.png}
+  \includegraphics[width=0.45\linewidth]{DolfinX_Sphere_const_coeff_error.png}
+  \caption{Error for the Kirkwood sphere.  \textcolor{blue}{(LEFT: $tol = 10^{-4}$, RIGHT: $tol = 10^{-5}$)}}
   \label{fig:error_sphere}
@@
 \centering
-   \includegraphics[width=0.5\linewidth]{DolfinX_Arginine2_const_coeff_error.png}
+   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_error_1e-4.png}
+   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_error.png}
 %   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine_const_coeff_error_11.png}
-\caption{Solvation energy for arginine with a constant permittivity. %(left - Arginine2 and right - Arginine)
-%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
-}
+\caption{Solvation energy for arginine with a constant permittivity.  \textcolor{blue}{(LEFT: $tol = 10^{-4}$, RIGHT: $tol = 10^{-5}$)}}
 \label{fig:arg_constant_energy}
@@
 \centering
-   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
+   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter_1e-4.png}
 %  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_time.png}
 %  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_setup_time.png}
-  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
+  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time_1e-4.png}
 %   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_iter_11.png}
@@
 %  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
-  \caption{Iteration count (left) and time-to-solution (right) for arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
-%NOTE: x axis differ between top and bottom.
-Also, should we include preconditioned vs non preconditioned?
-We could easily precondition BEM-BEM too.
-%(1) fix title, (2) can we put them in a single plot, (3)
-%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
+   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
+  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
+  \caption{Iteration count (left) and time-to-solution (right) for arginine with a constant permittivity.  \textcolor{blue}{(UP: $tol = 10^{-4}$, DOWN: $tol = 10^{-5}$)}
 }
@@
 We used Equation \eqref{eq:varying_eps} to generate dielectric maps, which we ran on APBS~\cite{BakerETal2001} for comparison. 
-We chose APBS because it provides an easy interface to control dielectric maps, in order to ensure their agreement with the maps imposed in our FEM-BEM coupled approach.
+We chose APBS because it provides an easy interface to control dielectric maps to ensure their agreement with the maps imposed in our FEM-BEM coupled approach.
 
@@
 \hline
-%\multirow{5}{*}{Standard FEM-BEM}& 2 & -29.554\\
-%    & 2 & -34.670\\
-%Hybrid    & 4  & -33.603 \\
-%FEM-BEM    & 8  & -32.822 \\
-%    & 16 & -32.072 \\
-%\hline
+%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
+    & 4.1 & 3 491 & -109.931 \\
+FEM-BEM    & 6.7  & 5 787 & -110.237 \\
+coupling    & 8.57  & 8 844 & -109.661 \\
+    & 17 & 19 911 & -109.369 \\
+    & 24.5 & 32 302 & -109.315 \\
+\hline
 \end{tabular}
 \caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS.
-The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}
+The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.
+\textcolor{blue}{(MIDDLE: $tol = 10^{-4}$, DOWN: $tol = 10^{-5}$)}}
 \label{table:arg_variable}
@@
  \hline
+  1pgb  & 29 434 &  10 058 &  -300.888 & 703 & 86 & 472 & 0.67 & 789  \\
+ 1lyz  & 56 114 & 18 606 &  -599.310 & 1073 & 336 & 1 350  & 1.26 & 1 686   \\
+ 1x1u & 263 181 & 81 258 & -1 982.085 & 2 791 & 8 340 & 11 000 & 3.94 & 19 340  \\
+ 1igt & 597 575 & 187 712 &  -3 294.0157 & 5 366 & 41 998 & 40 100 &  7.47 & 82 098    \\
+ \hline
 \end{tabular}}
-\caption{Results for larger structures with a variable permittivity.}
+\caption{Results for larger structures with a variable permittivity. \textcolor{blue}{(UP: $tol = 10^{-4}$, DOWN: $tol = 10^{-5}$)}
+}
 \label{table:large_variable}

### 2023-05-02 results.tex
Update result section
Decision made on the results with tol = 1e-5

@@
   \centering
-  \includegraphics[width=0.45\linewidth]{DolfinX_Sphere_const_coeff_error_1e-4.png}
   \includegraphics[width=0.45\linewidth]{DolfinX_Sphere_const_coeff_error.png}
-  \caption{Error for the Kirkwood sphere.  \textcolor{blue}{(LEFT: $tol = 10^{-4}$, RIGHT: $tol = 10^{-5}$)}}
+  \caption{Error for the Kirkwood sphere.  }
   \label{fig:error_sphere}
@@
 \centering
-   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_error_1e-4.png}
    \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_error.png}
-%   \includegraphics[width=0.47\linewidth]{DolfinX_Arginine_const_coeff_error_11.png}
-\caption{Solvation energy for arginine with a constant permittivity.  \textcolor{blue}{(LEFT: $tol = 10^{-4}$, RIGHT: $tol = 10^{-5}$)}}
+\caption{Solvation energy for arginine with a constant permittivity.}
 \label{fig:arg_constant_energy}
@@
 \centering
-   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter_1e-4.png}
-%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_time.png}
-%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_setup_time.png}
-  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time_1e-4.png}
-%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_iter_11.png}
-%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_time_11.png}
-%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_setup_time_11.png}
-%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
    \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
-  \caption{Iteration count (left) and time-to-solution (right) for arginine with a constant permittivity.  \textcolor{blue}{(UP: $tol = 10^{-4}$, DOWN: $tol = 10^{-5}$)}
-}
+  \caption{Iteration count (left) and time-to-solution (right) for arginine with a constant permittivity.  }
 \label{fig:arg2_constant_time_iter}
 \end{figure}
-
-%\begin{figure}
-%\centering
-%%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_iter.png}
-%%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_time.png}
-%%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_setup_time.png}
-%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_const_coeff_total_time.png}
-%   \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_iter_11.png}
-%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_time_11.png}
-%%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_setup_time_11.png}
-%  \includegraphics[width=0.45\linewidth]{DolfinX_Arginine_const_coeff_total_time_11.png}
-%  \caption{Iteration count (left) and time-to-solution (right) for Arginine with a constant permittivity. %(left: Online time taken to solve systems, right: Offline time taken to set up systems). 
-%%NOTE: x axis differ between top and bottom.
-Also, should we include preconditioned vs non preconditioned?
-We could easily precondition BEM-BEM too.
-%(1) fix title, (2) can we put them in a single plot, (3)
-%%maybe we could also add a "error" wrt extrapolation, or a plot with energy for each mesh?
-%}
-%\label{fig:arg_constant_time_iter}
-%\end{figure}
-
-%\begin{figure}
-%\centering
-%%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_error.png}
-%  \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_iter_11.png}
-%%   \includegraphics[width=0.45\linewidth]{No_prec_Arginine_const_coeff_iter.png}
-%%   \includegraphics[width=0.45\linewidth]{Arginine_const_coeff_time.png}
-%\caption{Iteration count for arginine with a constant permittivity.
-%(1) fix title, (2) can we put them in a single plot, (3) hybrid is internal or external iterations?
-maybe we should present the total count?
-%}
-%\label{fig:arg_contant_iter}
-%\end{figure}
 
@@
 \hline
-%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
-    & 4.1 & 3 491 & -109.907 \\
-FEM-BEM    & 6.7  & 5 787 & -110.199 \\
-coupling    & 8.57  & 8 844 & -109.582 \\
-    & 17 & 19 911 & -109.350 \\
-    & 24.5 & 32 302 & -109.265 \\
-\hline
+%%\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
+%    & 4.1 & 3 491 & -109.907 \\
+%FEM-BEM    & 6.7  & 5 787 & -110.199 \\
+%coupling    & 8.57  & 8 844 & -109.582 \\
+%    & 17 & 19 911 & -109.350 \\
+%    & 24.5 & 32 302 & -109.265 \\
+%\hline
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
@@
 \caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS.
-The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.
-\textcolor{blue}{(MIDDLE: $tol = 10^{-4}$, DOWN: $tol = 10^{-5}$)}}
+The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}
 \label{table:arg_variable}
 \end{table}
-
-%%\begin{figure}
-%%\centering
-%%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
-%%% \includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
-%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time_11.png}
-%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_setup_time_11.png}
-%%\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter_11.png}
-%%\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.
-%Can we make this only two plots?
-%%}
-%%\label{fig:arg_variable}
-%%\end{figure}
-%
-%\begin{figure}
-%\centering
-%% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
-%% \includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
-%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_time.png}
-%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_set_time.png}
-%\includegraphics[width=0.45\linewidth]{DolfinX_Arginine2_varying_coeff_iter.png}
-%\caption{Iteration count and time-to-solution to compute the solvation energy of arginine with a variable permittivity (left: Online time taken to solve systems, right: Offline time taken to set up systems), using FEM-BEM coupling.
-%Can we make this only two plots?
-%\textcolor{red}{Chris: not sure if we want to show performance here. Reviewers may ask for performance with APBS too, and those were run on a different machine, and has a number of steps.}}
-%\label{fig:arg2_variable}
-%\end{figure}
 
@@
 \hline
- 1pgb  & 29 434 &  10 058 &  -300.389 & 613 & 89 & 410 & 0.67 & 702  \\
- 1lyz  & 56 114 & 18 606 &  -597.515 & 724 & 334 & 921  & 1.27 & 1 255   \\
- %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
- 1x1u & 263 181 & 81 258 &  -1 975.068 & 1 911 & 8 240 & 7 410 & 3.88 & 15 650  \\
- 1igt & 597 575 & 187 712 &   -3 279.907 & 1 974 & 40 930 & 15 600 & 7.9  &  56 530   \\
- \hline
+% 1pgb  & 29 434 &  10 058 &  -300.389 & 613 & 89 & 410 & 0.67 & 702  \\
+% 1lyz  & 56 114 & 18 606 &  -597.515 & 724 & 334 & 921  & 1.27 & 1 255   \\
+% %1lyz gs3 & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 3.6 & 12 590   \\
+% 1x1u & 263 181 & 81 258 &  -1 975.068 & 1 911 & 8 240 & 7 410 & 3.88 & 15 650  \\
+% 1igt & 597 575 & 187 712 &   -3 279.907 & 1 974 & 40 930 & 15 600 & 7.9  &  56 530   \\
+% \hline
   1pgb  & 29 434 &  10 058 &  -300.888 & 703 & 86 & 472 & 0.67 & 789  \\
- 1lyz  & 56 114 & 18 606 &  -599.310 & 1073 & 336 & 1 350  & 1.26 & 1 686   \\
+ 1lyz  & 56 114 & 18 606 &  -599.310 & 1 073 & 336 & 1 350  & 1.26 & 1 686   \\
  1x1u & 263 181 & 81 258 & -1 982.085 & 2 791 & 8 340 & 11 000 & 3.94 & 19 340  \\
@@
 \end{tabular}}
-\caption{Results for larger structures with a variable permittivity. \textcolor{blue}{(UP: $tol = 10^{-4}$, DOWN: $tol = 10^{-5}$)}
-}
+\caption{Results for larger structures with a variable permittivity.}
 \label{table:large_variable}
 \end{table}
-%
-%\begin{table}
-%\centering
-%\begin{tabular}{c|c|c|c|c|c|c|c|c}
-%Molecule & Mesh size  & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Total Time \\
-%& vert/\AA$^2$ & DOFs & DOFs &  kcal/mol & & sec & sec & sec \\
-%\hline
-% 1pgb &  & 29 434 &  10 058 &  -300.888 & 826 & 82 & 547 & 629  \\
-% 1lyz &  & 56 114 & 18 606 &  -599.642 & 1 285 & 330 & 1 640  & 1 970  \\
-% 1lyz gs3 &  & 257 391 & 75 048 &  -600.637 & 2 949  & 1 690 & 10 900 & 12 590   \\
-% 1uxu &  & 263 181 & 81 258 &  -1 984.468 & 4 167 & 8 240 & 16 300 & 24 540  \\
-% 1igt &  & 597 575 & 187 712 &   -3 294.230 & 8 361 & 41 200 & 64 200 &  105 400   \\
-% \hline
-%\end{tabular}
-%\caption{Large tests' results}
-%\label{table:large_variable}
-%\end{table}

### 2023-05-02 intro.tex
intro and methods section

@@
 To describe these systems accurately, we need to account for the solvent correctly, which has given rise to a wide range of models.\cite{onufriev2018water}
-Highly detailed models consider every water molecule and salt ion explicitly, however, there are approximated models that use continuum theory to represent this ionic solution, known as implicit-solvent models.\cite{RouxSimonson1999,DecherchiETal2015}
-In the case of electrostatics, the implicit-solvent model is mathematically characterized by the Poisson-Boltzmann equation (PBE)\cite{Baker2004,Bardhan2012}, which is widely used to compute solvation free energies and mean-field potentials.
+Highly detailed models consider every water molecule and salt ion explicitly.
+For solutions with large numbers of molecules, however, these models can be very compuationally expensive, so implicit-solvent models---approximated models that use continuum theory to represent the ionic solution---are often used instead.\cite{RouxSimonson1999,DecherchiETal2015}
+In the case of electrostatics, the implicit-solvent model is mathematically characterized by the Poisson--Boltzmann equation (PBE)\cite{Baker2004,Bardhan2012}, which is widely used to compute solvation free energies and mean-field potentials.
 
-The implicit-solvent model for electrostatics describes the dissolved molecule as an infinite medium with a low-dielectric solute-shaped cavity, which contains a charge distribution from the partial charges --- usually a sum of Dirac deltas at the atom's locations.
-The outer solvent region is represented with a high dielectric, and considers the presence of salt.
-These two regions are interfaced by the molecular surface, which can be defined in various ways \cite{HarrisBoschitcshFenley2013}, where the continuity of the electrostatic potential and electric displacement are enforced.
+The implicit-solvent model for electrostatics describes the dissolved molecule as an infinite medium with a low-dielectric solute-shaped cavity, which contains a charge distribution from the partial charges---usually a sum of Dirac deltas at the atom's locations.
+The outer solvent region is represented with a high dielectric constant, and considers the presence of salt.
+These two regions are interfaced by the molecular surface where the continuity of the electrostatic potential and electric displacement are enforced.
+The molecular surface can be defined in various ways \cite{HarrisBoschitcshFenley2013}.
 
@@
 However, BEM is limited to constant material properties in each region and the linear version of the PBE. 
-Even though these limitations are acceptable in a wide range of applications, there are cases when BEM falls short, for example, if a variable permittivity is required inside the solute \cite{grant2001smooth,li2013dielectric}, or the solute is highly charged such that the linear approximation breaks\cite{FogolariETal1999}.
+Even though these limitations are acceptable in a wide range of applications, there are cases when BEM falls short: for example, if a variable permittivity is required inside the solute \cite{grant2001smooth,li2013dielectric}, or the solute is highly charged such that the linear approximation breaks\cite{FogolariETal1999}.
 
-The present article describes a methodology to overcome some of those limitations, by coupling finite and boundary elements methods.
-This approach brings the best of both worlds: the flexibility of FEM and the efficiency of BEM, all in an accurate description of the solute molecule.
+The present article describes a methodology to overcome some of those limitations, by coupling finite and boundary element methods.
+This approach brings the best of both worlds---the flexibility of FEM and the efficiency of BEM---all in an accurate description of the solute molecule.
 FEM-BEM coupling is a popular technique in the context of mixed linear-nonlinear models,\cite{carstensen1995coupling,aurada2013classical} fracture mechanics,\cite{aour2007coupled} fluid-structure interaction,\cite{estorff1991fem} acoustics,\cite{hiptmair2006stabilized} and electromagnetics.\cite{matsuoka1988calculation,hiptmair2008stabilized,bruckner20123d}
-On the other hand, the PBE has been solved with hybrid numerical methods in the past, for example, by coupling finite difference with boundary elements\cite{boschitsch2004hybrid} or finite elements,\cite{xie2016new,ying2018hybrid} which were mainly used to solve the nonlinear PBE in a specific region, and to implement modifications to the PBE model ({\it ie.} the size-modified PBE).
-To the best of our knowledge, this is the first time finite and boundary elements are combined in this application.
+On the other hand, the PBE has been solved with hybrid numerical methods in the past: for example, by coupling finite differences with boundary elements\cite{boschitsch2004hybrid} or finite elements\cite{xie2016new,ying2018hybrid} to solve the nonlinear PBE in a specific region, and to implement modifications to the PBE model ({\it ie.} the size-modified PBE).
+To the best of our knowledge, this is the first time finite and boundary elements have been combined in this application.
 
-Here we prototype this principle with the simplest implementation possible: a Johnson-N\'ed\'elec\cite{johnson1980coupling} coupling, mass-matrix and diagonal preconditioning, and no distributed memory execution.
-This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in the software libraries used in this work, in particular, Bempp-cl and FEniCSx.
-These libraries are designed for ease of use through a simple Python interface, making them ideal tools to explore and improve computational efficiency, towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}
+In this paper, we prototype this principle with the simplest implementation possible: a Johnson--N\'ed\'elec\cite{johnson1980coupling} coupling, where we solve using mass-matrix and diagonal preconditioning and whithout distributed memory execution.
+This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in open source software libraries.
+In this work, we use the boundary element library Bempp-cl\cite{BetckeScroggs2021} and the finite element library FEniCSx\cite{BasixJoss,BasixDofTransformations,FEniCS}.
+These libraries are easy to use and their full functionalities may be accessed via their Python interfaces, making them ideal tools for easily implementing problems like this as well as for exploring computational efficiency and moving towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}
 We hope this work will inspire research along these lines.

### 2023-05-02 main.tex
Updated results, comparison for tol = 1e-4 and 1e-5
intro and methods section

@@
 
+\newcommand{\mscomment}[1]{\textbf{\color{red}[Matthew: #1]}}
+
 \definecolor{background-color}{gray}{0.98}
 
-\title{Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation}
+\title{Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation}
 \author{Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, 
@@
 \begin{abstract}
-The Poisson-Boltzmann equation is widely used to model electrostatics in molecular systems.
+The Poisson--Boltzmann equation is widely used to model electrostatics in molecular systems.
 Available software packages solve it using finite difference, finite element, and boundary element methods, where the latter is attractive due to the accurate representation of the molecular surface and partial charges, and exact enforcement of the boundary conditions at infinity.
-However, the boundary element method is limited to linear equations and piece-wise constant variations of the material properties.
-In this work, we present a scheme that couples finite and boundary elements for the Poisson-Boltzmann equation, where the finite element method is applied in a confined {\it solute} region, and the boundary element method in the external {\it solvent} region.
-As a proof-of-concept exercise, we used the simplest methods available: Johnson-N\'ed\'elec coupling with mass matrix and diagonal preconditioning, implemented in the Bempp-cl and FEniCSx libraries from a simple Python interface.
-We showcased our implementation by computing the polar component of the solvation free energy of a set of molecules using a constant and a Gaussian-varying permittivity.
-First, we validated our implementation against the finite difference code APBS (to 0.5\%), and then, we show scaling from protein G B1 (955 atoms) up to immunoglobulin G (20 148 atoms).
-For small problems we saw that the coupled method was efficient, outperforming a purely boundary integral approach, but scaled worse with size.
-For Gaussian-varying permittivities, which are beyond the applicability of boundary elements, we were able to run medium to large problems on a single workstation.
-However, our results illustrate the need to improve conditioning and incorporate distributed memory parallelism as we aim at larger systems.
+However, the boundary element method is limited to linear equations and piecewise constant variations of the material properties.
+In this work, we present a scheme that couples finite and boundary elements for the Poisson--Boltzmann equation, where the finite element method is applied in a confined {\it solute} region, and the boundary element method in the external {\it solvent} region.
+As a proof-of-concept exercise, we use the simplest methods available: Johnson--N\'ed\'elec coupling with mass matrix and diagonal preconditioning, implemented using the Bempp-cl and FEniCSx libraries via their Python interfaces.
+We showcase our implementation by computing the polar component of the solvation free energy of a set of molecules using a constant and a Gaussian-varying permittivity.
+We validate our implementation against the finite difference code APBS (to 0.5\%), and show scaling from protein G B1 (955 atoms) up to immunoglobulin G (20\,148 atoms).
+For small problems, the coupled method was efficient, outperforming a purely boundary integral approach.
+For Gaussian-varying permittivities, which are beyond the applicability of boundary elements alone, we were able to run medium to large sized problems on a single workstation.
+Development of better preconditioning techniques and the use of distributed memory parallelism for larger systems remains an area for future work.
 We hope this work will serve as inspiration for future developments that consider space-varying field parameters, and mixed linear-nonlinear schemes for molecular electrostatics with implicit solvent models.
@@
 \begin{wileykeywords}
-Finite element method, Boundary element method, Poisson-Boltzmann, Implicit solvent model, Electrostatics.
+Finite element method, Boundary element method, Poisson--Boltzmann, Implicit solvent model, Electrostatics.
 \end{wileykeywords}
@@
 \\
-    The boundary element method is a popular numerical algorithm to solve the Poisson-Boltzmann equation for molecular electrostatics.
-However, this technique is limited to linear equations and piece-wise constant variations of the field parameters.
-Here, we overcome such limitations by coupling it with a finite element method, implemented using the Bempp-cl and FEniCSx libraries through simple Python interfaces.
+    The boundary element method is a popular numerical algorithm to solve the Poisson--Boltzmann equation for molecular electrostatics.
+However, this technique is limited to linear equations and piecewise constant variations of the field parameters.
+Here, we overcome such limitations by coupling it with a finite element method, implemented using the Bempp-cl and FEniCSx libraries via their Python interfaces.
 This results in an efficient, accurate, flexible, and easy-to-use computational tool for model development.
@@
 % makes references listed with 1., 2., etc.  
-  \makeatletter
+0  \makeatletter
   \renewcommand\@biblabel[1]{#1.}
@@
 \subsection*{\sffamily \large ACKNOWLEDGMENTS}
-
+MB acknowledges the support from Kingston University through First Kingston University Grant. \\
 CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.

### 2023-05-02 methods.tex
intro and methods section

@@
 
-The implicit solvent model\cite{RouxSimonson1999,DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson-Boltzmann governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson equation in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}).
-These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous.
+The implicit solvent model\cite{RouxSimonson1999,DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson--Boltzmann equation governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson equation govnerns in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}).
+These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous across the surface.
 %
-\begin{align}\label{eq:pbe}
-\nabla^2\phi_1(\mathbf{x}) &= \tfrac{1}{\epsilon_1}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
-\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
-\phi_1(\mathbf{x})  = \phi_2 (\mathbf{x}), &\quad \epsilon_1\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  = \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})  \quad \mathbf{x}\in \Gamma.
+\begin{subequations}
+\label{eq:pbe}
+\begin{align}
+\nabla^2\phi_1(\mathbf{x}) &= \tfrac{1}{\epsilon_1}\sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)&&\mathbf{x} \in \Omega_1,\label{eq:pbe1}\\
+\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0&&\mathbf{x}\in\Omega_2,\label{eq:pbe2}\\
+\phi_1(\mathbf{x})  &= \phi_2 (\mathbf{x}),&&\mathbf{x}\in \Gamma,\label{eq:pbe3}\\
+\epsilon_1\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x}) &= \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})&&\mathbf{x}\in \Gamma. \label{eq:pbe4}
 \end{align}
+\end{subequations}
 %
-Here, $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively, $\kappa$ is the inverse of the Debye length, related with the salt concentration, and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.
+Here, $\epsilon_1$ and $\epsilon_2$ are the dielectric constants in the solute and solvent, respectively; $\kappa$ is the inverse of the Debye length, related to the salt concentration; and $q_k$ are the values of the partial charges, located at $\mathbf{x}_k$.
 
@@
 \begin{align}\label{eq:phic}
-\nabla^2\phi_c(\mathbf{x}) &= \tfrac{1}{\epsilon}\sum_{k=1}^{N_q}q_k\delta(\mathbf{x},\mathbf{x}_k) \quad \mathbf{x}\in\Omega_1\cup\Omega_2\nonumber\\
-\phi_c(\mathbf{x})&=0 \quad \text{ as } |\mathbf{x}|\to\infty
+\nabla^2\phi_c(\mathbf{x}) &= \tfrac{1}{\epsilon}\sum_{k=1}^{N_q}q_k\delta(\mathbf{x},\mathbf{x}_k) &&\mathbf{x}\in\Omega_1\cup\Omega_2,\nonumber\\
+\phi_c(\mathbf{x})&=0 &&\text{ as } |\mathbf{x}|\to\infty.
 \end{align}
+Physically, $\phi_c$ can be interpreted as the Coulomb-type potential from the point charges, whereas $\phi_r$, also known as reaction potential, is originated by the polarization of the solvent and reorganization of the free ions.
+Usually, $\epsilon_1$ is considered a constant value, yielding an analytical expression for $\phi_c$. However, this is not the general case.
 
-Physically, $\phi_c$ can be interpreted as the Coulomb-type potential from the point charges, whereas $\phi_r$, also known as reaction potential, is originated by the polarization of the solvent and reorganization of the free ions.
-Usually, $\epsilon_1$ is considered a constant value, yielding an analytical expression for $\phi_c$, however, this is not the general case.
-
-Regularized versions of Equation \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson-Boltzmann equation with finite element or finite difference methods, and have recently been extended to super-Gaussian permittivities in the solute.\cite{wang2022regularization} However, here we use the standard formulation in Equation \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permittivities, beyond super-Gaussian descriptions.
+Regularized versions of the equations in \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson--Boltzmann equation with finite element or finite difference methods, and have recently been extended to super-Gaussian permittivities in the solute.\cite{wang2022regularization} However, here we use the standard formulation in \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permittivities, beyond super-Gaussian descriptions.
 
@@
 \begin{equation}\label{eq:dG} 
-\Delta G_{solv} = \tfrac{1}{2}\int_{\Omega_1} \rho(\mathbf{x})\phi_{r}(\mathbf{x}) = \tfrac{1}{2}\sum_{k=1}^{N_q} q_k\phi_r(\mathbf{x_k})
+\Delta G_{\text{solv}} = \tfrac{1}{2}\int_{\Omega_1} \rho(\mathbf{x})\phi_{r}(\mathbf{x}) = \tfrac{1}{2}\sum_{k=1}^{N_q} q_k\phi_r(\mathbf{x_k}).
 \end{equation}
@@
 
-Several possible boundary integral formulations of Equation \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon and Lenhoff in 1991,~\cite{YoonLenhoff1990} known as the \emph{direct} formulation, however, the resulting system is usually ill-conditioned.
+Several possible boundary integral formulations of \eqref{eq:pbe} exist.~\cite{search2022towards} The simplest form was presented by Yoon and Lenhoff in 1991\cite{YoonLenhoff1990} and is known as the \emph{direct formulation}.
+However, the resulting system is usually ill-conditioned.
 Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
@@
 \begin{align}\label{eq:lu}
-    & \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}
+    \tfrac{\phi_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_2 + \left(V_Y^\Gamma - V_L^\Gamma\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},
      \nonumber \\
-    &\tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 = \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right)
+    \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_2 +  \tfrac{\lambda_2}{2}\left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2 &= \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),
 \end{align}
-%\textcolor{blue}{Michal: We only have $\phi_2$ and $\lambda_2$ and the solution later is from $\phi_1$ and $\lambda_1$!!!}
-
-%
-In Equation \eqref{eq:lu}, $\phi_1 = \phi_1(\mathbf{x}_\Gamma)$ and $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ are the potentials on $\Gamma$ as we approach from $\Omega_1$ and $\Omega_2$, respectively.
-For convenience, we call the normal derivative on the interface ({\it ie.} the Neumann trace) $\lambda=\left(\frac{\partial}{\partial \mathbf{n}}  \phi_{\Gamma}  \right)$.
-$V$, $K$, $K^{\prime}$, and $W$ are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
+where $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Dirichlet trace),
+and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Neumann trace).
+Note that we could use equations \eqref{eq:pbe3} and \eqref{eq:pbe4} to rewrite Equation \eqref{eq:lu} in terms of the interior traces $\phi_1$ and $\lambda_1$.
+The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
 These are defined %in Equation~\eqref{eq:single_double} and
-as
+by
 %
 \begin{align}\label{eq:all_op}
-V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
+V_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma g_i(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
 K_i^\Gamma \varphi (\mathbf{x}) &= \oint_\Gamma \frac{\partial g_i}{\partial\mathbf{n}'}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
-K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'\nonumber\\
-W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x}_\Gamma,\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}'
+K^{\prime\Gamma}_i\varphi (\mathbf{x}) &= \oint_\Gamma \frac{g_i}{\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',\nonumber\\
+W^\Gamma_i\varphi (\mathbf{x}) &= - \oint_\Gamma \frac{\partial^2 g_i}{\partial\mathbf{n}'\partial\mathbf{n}}(\mathbf{x},\mathbf{x}')\varphi(\mathbf{x}')d\mathbf{x}',
 \end{align}
@@
 %\begin{align}\label{eq:lu_disc}
-%&\left< \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\phi_{2}}{2} - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_{2}, v \right>_{\Gamma} + \left< \left(V_Y^\Gamma - V_L^\Gamma\right) \lambda_2, v \right>_\Gamma = \left< \sum_{k=0}^{N_q}  f_k, v \right>_{\Gamma} \nonumber \\
-%&\left< \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_{2}, \zeta \right>_\Gamma + \left<  \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\lambda_2}{2} + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2, \zeta\right>_\Gamma = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}} f_k, \zeta \right>_{\Gamma}
+%&\left\langle \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\phi_{2}}{2} - \left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right)\phi_{2}, v \right\rangle_{\Gamma} + \left\langle \left(V_Y^\Gamma - V_L^\Gamma\right) \lambda_2, v \right\rangle_\Gamma = \left\langle \sum_{k=0}^{N_q}  f_k, v \right\rangle_{\Gamma} \nonumber \\
+%&\left\langle \tfrac{\epsilon_1}{\epsilon_2}\left(W_Y^\Gamma - W_L^\Gamma\right)\phi_{2}, \zeta \right\rangle_\Gamma + \left\langle  \left(1+\tfrac{\epsilon_1}{\epsilon_2}\right) \tfrac{\lambda_2}{2} + \left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right)\lambda_2, \zeta\right\rangle_\Gamma = \left\langle \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}} f_k, \zeta \right\rangle_{\Gamma}
 %\end{align}
 %%
-%where $v, \zeta$ are test functions, $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ %and $\left(\varphi,v\right)_\Omega = \int_\Omega \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are
+%where $v, \zeta$ are test functions, $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ %and $\left(\varphi,v\right\rangle_\Omega = \int_\Omega \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are
 %is the inner products on the surface% and domain, respectively
@@
 %\begin{align*}
-%\widetilde{K}_{\alpha \beta} = \left<\left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right) \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}
+%\widetilde{K}_{\alpha \beta} = \left\langle\left(K_Y^\Gamma - \tfrac{\epsilon_1}{\epsilon_2}K_L^\Gamma\right) \phi^{\alpha}_2, \ \lambda^{\beta}_2 \right\rangle_{\Gamma}
 % &,&
-%\widetilde{V}_{\alpha \beta} = \left<\left(V_Y^\Gamma - V_L^\Gamma\right) \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
-%\widetilde{W}_{\alpha \beta} = \left<\left(W_Y^\Gamma - W_L^\Gamma\right) \phi^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma}
+%\widetilde{V}_{\alpha \beta} = \left\langle\left(V_Y^\Gamma - V_L^\Gamma\right) \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right\rangle_{\Gamma}, \\
+%\widetilde{W}_{\alpha \beta} = \left\langle\left(W_Y^\Gamma - W_L^\Gamma\right) \phi^{\alpha}_2, \ \phi^{\beta}_2 \right\rangle_{\Gamma}
 % &,&
-%\widetilde{K'}_{\alpha \beta} = \left<\left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right) \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right>_{\Gamma},
+%\widetilde{K'}_{\alpha \beta} = \left\langle\left(\tfrac{\epsilon_1}{\epsilon_2}K_Y^{\prime\Gamma} - K_L^{\prime\Gamma}\right) \lambda^{\alpha}_2, \ \phi^{\beta}_2 \right\rangle_{\Gamma},
 %\end{align*}
@@
 %\begin{align*}
-%\vec{f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},   \phi^{\beta}_1  \right>_{\Gamma} &,& \vec{\partial f}_{\beta} = \left< \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),   \phi^{\beta}_1  \right>_{\Gamma}.
+%\vec{f}_{\beta} = \left\langle \sum_{k=0}^{N_q}  \frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|},   \phi^{\beta}_1  \right\rangle_{\Gamma} &,& \vec{\partial f}_{\beta} = \left\langle \sum_{k=0}^{N_q}  \frac{\partial}{\partial\mathbf{n}_\mathbf{x}}\left(\frac{q_k}{4\pi\epsilon_2|\mathbf{x}_{\Gamma} - \mathbf{x}_k|}\right),   \phi^{\beta}_1  \right\rangle_{\Gamma}.
 %\end{align*}
@@
 
-Having computed the electrostatic potential with Eq.
-\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.
-\eqref{eq:dG} by subtracting out the Coulombic component out of $\phi_1$.
+Having computed the electrostatic potential with Eq.~\eqref{eq:lu}, we obtain the reaction potential ($\phi_r$) in Eq.~\eqref{eq:dG} by subtracting the Coulombic component from $\phi_1$.
 This gives\cite{CooperBardhanBarba2014}
@@
 \begin{align} \label{eq:phi_reac}
-\phi_{r}(\mathbf{r}) = - K_{L}^{\mathbf{r}} \phi_1 + V_{L}^{\mathbf{r}}  \lambda_1  ,
+\phi_{r}(\mathbf{r}) = - K_{L}^{\Gamma} \phi_1(\mathbf{r}) + V_{L}^{\Gamma}  \lambda_1(\mathbf{r}),
 \end{align}
 %
-where $\mathbf{r}\in\Omega_1$, and we can obtain $\phi_1$ and $\lambda_1$ from $\phi_2$ and $\lambda_2$ by applying the interface conditions from Eq. \eqref{eq:pbe}.
-This is valid as long as $\epsilon_1$ is a constant. We use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
+where $\mathbf{r}\in\Omega_1$, and we can obtain $\phi_2$ and $\lambda_2$ from $\phi_1$ and $\lambda_1$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
+This is valid as long as $\epsilon_1$ is a constant, so we use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
 
-\subsection*{\sffamily \large Novel numerical solution of the Poisson-Boltzmann equation}
+\subsection*{\sffamily \large Novel numerical solution of the Poisson--Boltzmann equation}
 
@@
 
-The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson-Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl.~\cite{search2022towards}.
-Its popularity comes because it reduces the dimension of the problem by using the boundary integral formulation.
-Unfortunately, this advantage comes at a cost: it requires a fundamental solution to be applied.
-There are many linear problems for which fundamental solutions are not known, for example, this is the case for the Poisson-Boltzmann equation with a heterogenous permittivity inside the molecule
+The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson--Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl\cite{search2022towards}.
+One strong advantage of BEM is that it reduces the dimension of the problem by using the boundary integral formulation.
+Unfortunately, this advantage comes at a cost: it requires a fundamental solution to be known in order for the method to be applied.
+There are many linear problems for which fundamental solutions are not known: this is the case for the Poisson-Boltzmann equation with a heterogenous permittivity inside the molecule, \emph{ie}.
 %
 \begin{align} \label{eq:pbe_vp}
-\nabla \cdot \left(\epsilon_1(\mathbf{x}) \nabla \phi_1(\mathbf{x})\right) &= \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) \quad  \mathbf{x} \in \Omega_1\nonumber\\
-\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 \quad\mathbf{x}\in\Omega_2\nonumber\\
-\phi_1(\mathbf{x})  = \phi_2(\mathbf{x}),  &\quad \epsilon_1(\mathbf{x})\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  = \epsilon_2(\mathbf{x})\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x})  \quad \mathbf{x}\in \Gamma.
+\nabla \cdot \left(\epsilon_1(\mathbf{x}) \nabla \phi_1(\mathbf{x})\right) &= \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k) &&\mathbf{x} \in \Omega_1,\nonumber\\
+\left(\nabla^2 - \kappa^2\right)\phi_2(\mathbf{x})  &= 0 &&\mathbf{x}\in\Omega_2,\nonumber\\
+\phi_1(\mathbf{x})  &= \phi_2(\mathbf{x}),&&\mathbf{x}\in \Gamma,\nonumber\\
+\epsilon_1(\mathbf{x})\frac{\partial\phi_1}{\partial\mathbf{n}}(\mathbf{x})  &= \epsilon_2\frac{\partial\phi_2}{\partial\mathbf{n}}(\mathbf{x}) &&\mathbf{x}\in \Gamma. 
 \end{align}
@@
 
-The coupling of finite element (FEM) and boundary element (BEM) methods is a widely used approach to solve multi-physical problems on unbounded domains [citation?], as it takes advantage of both methods.
-On one hand, the BEM satisfies the infinite boundary conditions exactly when they decay to zero, and only approximates boundary conditions on surfaces, hence, it is commonly used for problems involving infinite or semi-infinite domains.
+The coupling of FEM and BEM is an approach that can be used to solve a wide range of multiphysics problems on unbounded domains\cite{hiptmair2002,banjai2015}, as it takes advantage of both methods.
+On the one hand, the BEM satisfies the infinite boundary conditions exactly when they decay to zero, and only approximates boundary conditions on surfaces; hence, it is commonly used for problems involving infinite or semi-infinite domains.
 On the other hand, the FEM is known for its robustness and universal applicability, even for problems of inhomogeneous or non-linear nature.
-Here, we used the Johnson-N\'ed\'elec formulation,\cite{johnson1980coupling} which is the simplest form of FEM-BEM coupling, and we detail it next.
+Here, we use the Johnson--N\'ed\'elec formulation,\cite{johnson1980coupling} which is the simplest formulation of FEM-BEM coupling, and we detail it next.
 
-   We start with the variational formulation of the internal problem. Applying integration by parts for first equation of~\eqref{eq:pbe_vp} for every $v \in H_0^1(\Omega_1)$, we have
+We start with the variational formulation of the internal problem. Applying integration by parts to the first equation of~\eqref{eq:pbe_vp} we have, for every $v \in H_0^1(\Omega_1)$,
 % 
@@
 \label{eq:fem}
- \left( \epsilon_1 \nabla \phi_1, \nabla v \right)_{\Omega_1}  -  \left<  \epsilon_1\partial_n \phi_1, v \right>_\Gamma =  \left( \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v\right)_{\Omega_1},
+ \left\langle \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  -  \left\langle  \epsilon_1\partial_n \phi_1, v \right\rangle_\Gamma =  \left\langle \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v\right\rangle_{\Omega_1},
 \end{equation}
 %
-where $v$ is a test function, and $\left<\varphi,v\right>_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ and $\left(\varphi,v\right)_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})d\mathbf{x}$ are the inner products on the surface and domain, respectively.
+where $v$ is a test function, and $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})\overline{v(\mathbf{x})}\,\mathrm{d}\mathbf{x}$ and $\left\langle\varphi,v\right\rangle_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})\overline{v(\mathbf{x})}\,\mathrm{d}\mathbf{x}$ are the inner products on the surface and in the domain, respectively.
 For the external problem with BEM, we define the Dirichlet trace~\cite{MR2361676} 
@@
 % \label{eq:trace_map}
-\gamma:  H^1(\Omega_2) &\rightarrow H^{\frac{1}{2}}(\Gamma) & \gamma f(x) & := \lim_{\Omega_2 \ni y \rightarrow x \in \Gamma}  f(y),
+\gamma:  H^1(\Omega_2) &\rightarrow H^{\frac{1}{2}}(\Gamma), & \gamma f(x) & := \lim_{\Omega_2 \ni \mathbf{y} \rightarrow \mathbf{x} \in \Gamma}  f(\mathbf{y}),
 \end{align*}
@@
 \end{align*}
-$V$ and $K$ are the single-layer and double-layer operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
-These are defined in Equations~\eqref{eq:all_op} and~\eqref{eq:green_func}.
+$V$ and $K$ are the single-layer and double-layer operators as defined in Equation~\eqref{eq:all_op}.
 %as
@@
 
-Then, the coupling problem can be written as
-%
-\begin{center}
-  \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_2 \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$}
-\begin{equation} 
+Then, the coupling problem can be written as: \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_2 \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$},
+\begin{subequations}
 \label{eq:standard_fem_bem}
- \left\{
- \begin{array}{rcl}
- \left(  \epsilon_1 \nabla \phi_1, \nabla v \right)_{\Omega_1}  - \left< \epsilon_1 \lambda_2, v \right>_\Gamma &=&   \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right)_{\Omega_1} \\[3mm]
-  \left< \left(\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \gamma \phi_1, \zeta \right>_\Gamma + \tfrac{\epsilon_1}{\epsilon_2} \left< V_{Y}^{\Gamma} \lambda_2, \zeta \right>_\Gamma &=&0.
-  \end{array}
-  \right.
-\end{equation}
-\end{center}
+\begin{align} 
+ \left\langle  \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  - \left\langle \epsilon_1 \lambda_2, v \right\rangle_\Gamma &=   \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right\rangle_{\Omega_1}, \\[3mm]
+  \left\langle \left\langle\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \gamma \phi_1, \zeta \right\rangle_\Gamma + \tfrac{1}{\epsilon_2} \left\langle V_{Y}^{\Gamma}\epsilon_1\lambda_2, \zeta \right\rangle_\Gamma &=0.
+\end{align}
+\end{subequations}
+Note that in the case where $\epsilon_1$ is constant, then each $\epsilon_1$ can be moved outside of the inner product it is inside.
 
@@
 % \int_{\Omega_1} \epsilon_1 \nabla \phi_1 : \nabla v ~d\mathbf{x}  - \oint_\Gamma \epsilon_1\partial_n \phi_1 v ds &=   \int_{\Omega_1}  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k)  v ~d\mathbf{x} \\
-% \oint_\Gamma \tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left( \lambda_2^1 \right) & = 0
+% \oint_\Gamma \tfrac{\phi_1}{2} - K_{Y}^{\Gamma}(\phi_1) + \tfrac{\epsilon_1}{\epsilon_2}V_{Y}^{\Gamma} \left\langle \lambda_2^1 \right) & = 0
 %\end{align}
 
-This can also be written in matrix form. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
-functions of the finite element space $V_{h}^{j}$, %$\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis functions of $W_{h}^{k}$,  
-$\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ --- the vector of canonical basis
-functions of $\Lambda_{h}^{l}$. % and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis functions of  $M_{h}^{m}$
+When discretised, this can also be written in matrix form. Let $\vec{\phi}_1 := [\phi_1^1, \dots, \phi_1^j]^T$ be the vector of canonical basis
+functions of the finite element space $V_{h}^{j}\subset H^1(\Omega_1)$, %$\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis functions of $W_{h}^{k}$,  
+and let $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ be the vector of canonical basis
+functions of $\Lambda_{h}^{l}\subset H^{-\frac{1}{2}}(\Gamma)$.
+% and $\vec{\widetilde{\phi}} := [\widetilde{\phi}^1, \dots, \widetilde{\phi}^m]^T$ be the vector of canonical basis functions of  $M_{h}^{m}$
 % $T:\Omega_1 \rightarrow \Gamma$ and $E:\Gamma \rightarrow \Omega_1$ trace and extendable operators respectively.
-We define the following matrices associated with the corresponding bilinear forms
+We define the following matrices associated with the corresponding sesquilinear forms
 \begin{align*}
-A_{\alpha \beta} = \left(\nabla \phi_1^{\alpha}, \nabla \phi_1^{\beta} \right)_{\Omega_1}  
-&,&
-M_{\alpha \beta} = \left< \widetilde{\phi}^{\alpha}, \ \lambda^{\beta}_2 \right>_{\Gamma}, \\
-K_{\alpha \beta} = \left<K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \ \lambda^{\beta}_2 \right>_{\Gamma}
- &,&
-V_{\alpha \beta} = \left<V_{Y}^{\Gamma} \lambda^{\alpha}_2, \ \lambda^{\beta}_2 \right>_{\Gamma}, 
+A_{\alpha \beta} &= \left\langle\epsilon_1\nabla\phi_1^{\alpha}, \nabla \phi_1^{\beta} \right\rangle_{\Omega_1},&
+M_{\alpha \beta} &= \left\langle \epsilon_1\lambda^{\beta}_2,\phi_1^{\alpha}\right\rangle_{\Gamma},\\
+K_{\alpha \beta} &= \left\langle K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \lambda^{\beta}_2 \right\rangle_{\Gamma},&
+V_{\alpha \beta} &= \left\langle V_{Y}^{\Gamma} \epsilon_1\lambda^{\alpha}_2, \lambda^{\beta}_2 \right\rangle_{\Gamma},\\
+I_{\alpha \beta} &= \left\langle \gamma \phi^{\alpha}_1, \lambda^{\beta}_2 \right\rangle_{\Gamma},
 \end{align*}
+\mscomment{As $I$ is not equal to the identity matrix, we should maybe change the letter we use? I'd usually change it to $M$ but we've also already used that}
 and vector associated with the corresponding linear form
 \begin{equation*}
-\vec{f}_{\beta} := \left(  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  \phi_1^{\beta} \right)_{\Omega_1}.
+\vec{f}_{\beta} := \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  \phi_1^{\beta} \right\rangle_{\Omega_1}.
 \end{equation*}
-Using the above definition the discrete problem in Eq.~\eqref{eq:standard_fem_bem} can be written in the following matrix form
+Using the above definitions, the discrete problem in \eqref{eq:standard_fem_bem} can be written in the following blocked matrix form:
 \begin{align}\label{eq:fembem_matrix}
 \begin{bmatrix}
-\epsilon_1 A &  - \epsilon_1 M^T \\  
-\left(\tfrac12 I - K \right) \gamma &  \tfrac{\epsilon_1}{\epsilon_2} V 
+A & -M^T \\  
+\left(\tfrac12 I - K \right) \gamma &  \tfrac{1}{\epsilon_2} V 
 \end{bmatrix}

### 2023-05-03 results.tex
added info on GMRES and fmm vs dense

@@
 For $N$ surface elements this reduces the memory and computational complexity from $\mathcal{O}(N^2)$ in the dense assembly case to $\mathcal{O}(N)$ in the FMM case, making large boundary element problems tractable on standard workstations.
+In this work, we only use the FMM in the performance analysis for larger structures, as all other cases are small enough to run efficiently with a dense assembler.
 
@@
 FMM assembly fits automatically into this framework and can be enabled or disabled as a simple configuration option.
+Once the discrete block matrices in Eq.
+\eqref{eq:fembem_matrix} are built with Bempp-cl and FEniCSx, we assemble them into one matrix and solve the linear system with Scipy's\cite{2020SciPy-NMeth} GMRES, in this case, with a tolerance of 10$^{-5}$.
 

### 2023-05-03 conclusion.tex
results section

@@
-This paper presents the first implementation of a FEM-BEM coupling approach to solve the Poisson-Boltzmann equation for molecular electrostatics.
+This paper presents the first implementation of a FEM-BEM coupling approach to solve the Poisson--Boltzmann equation for molecular electrostatics.
 This brings the best of both worlds: the accuracy and efficiency of BEM to exactly enforce the boundary conditions at infinity, and the flexibility of FEM to account for space variations of the material properties and nonlinearities.
-After presenting verification results for a sphere and arginine with a constant permittivity inside the solute, we showcased our implementation with an advanced modeling technique that considers Gaussian-varying permittivities in a confined region, compared with the widely-used APBS software.
-The final scaling results for larger molecules start from protein G B1 (955 atoms) and go up to immunoglobulin G (20 148 atoms), proving the applicability of this approach for realistic problems.
-Even though our implementation was able to reach medium-to-large systems, we recongnize the need for further research towards optimizing the coupling technique, acceleration algorithms, and parallel execution, especially as we look towards much larger solutes, like viruses.
+After presenting verification results for a sphere and arginine with a constant permittivity inside the solute, we showcased our implementation with an advanced modeling technique that considers Gaussian-varying permittivities in a confined region, with the results validated against the widely-used APBS software.
+The final scaling results for larger molecules start from protein G B1 (955 atoms) and go up to immunoglobulin G (20\,148 atoms), proving the applicability of this approach for realistic problems.
+Even though our implementation was able to reach medium-to-large systems, we recongnize the need for further research towards better preconditioning of the linear system, optimizing the coupling technique, acceleration algorithms, and parallel execution, especially as we look towards much larger solutes, like viruses.
 We hope this proof-of-concept work will serve as motivation for future model development that considers space-varying permittivities and Debye lengths, and mixed linear-nonlinear techniques, especially for highly-charged systems, like nucleic acids.

### 2023-05-03 intro.tex
results section

@@
 This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in open source software libraries.
-In this work, we use the boundary element library Bempp-cl\cite{BetckeScroggs2021} and the finite element library FEniCSx\cite{BasixJoss,BasixDofTransformations,FEniCS}.
+In this work, we use the boundary element library Bempp-cl\cite{BetckeScroggs2021} and the finite element library FEniCSx\cite{BasixJoss,BasixDofTransformations}.
 These libraries are easy to use and their full functionalities may be accessed via their Python interfaces, making them ideal tools for easily implementing problems like this as well as for exploring computational efficiency and moving towards tackling large-scale problems, such as a full viral capsid.\cite{MartinezETal2019,wang2021high}

### 2023-05-03 results.tex
results section

--- 2023-05-02 results.tex
@@
-This section presents the verification and performance results of the presented FEM-BEM coupling schemes, for molecules modeled as cavities with constant and varying permittivity.
+This section presents the verification and performance results of the presented FEM-BEM coupling schemes for molecules modeled as cavities with constant and varying permittivity.
 With a constant permittivity inside the molecule, we tested convergence against an analytical expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
 We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
-The final tests show the scaling of the FEM-BEM coupling, as the molecule size grows.
+The final tests show the scaling of the FEM-BEM coupling as the molecule size grows.
 
@@
 
-For the finite element computations, we use the software package FEniCSx~\cite{BasixJoss} while for the boundary element computations, we use Bempp-cl~\cite{BetckeScroggs2021} together with Exafmm-t.
-FEniCSx is the successor of the widely used FEniCS finite element library.
-It provides a convenient Python interface, describing problems using Unified Form Language (UFL), a convenient domain-specific language specifically designed for finite element discretisations of partial differential equations.
-During assembly, the UFL description is transformed into efficient low-level C++ code and just-in-time compiled.
-Bempp-cl is a Python package that uses low-level OpenCL kernels written in C99 to provide optimised assembly routines.
+For the finite element computations, we use the software package FEniCSx~\cite{BasixJoss,BasixDofTransformations} while for the boundary element computations, we use Bempp-cl~\cite{BetckeScroggs2021} together with Exafmm-t~\cite{exafmm-t}.
+FEniCSx is the successor of the widely used FEniCS finite element library\cite{FEniCS,FEniCS-book}.
+It provides a convenient Python interface, describing problems using Unified Form Language (UFL)~\cite{UFL}, a convenient domain-specific language specifically designed for finite element discretisations of partial differential equations.
+During assembly, the UFL description is transformed into efficient low-level C++ code and just-in-time compiled~\cite{ffc1,ffc2}.
+Bempp-cl is a Python package that uses low-level OpenCL kernels written in C99 to provide optimised assembly routines~\cite{2021-cise}.
 The built-in dense assembly routines are highly efficient for moderate discretisation sizes up to a few ten thousand elements.
@@
 We then export the corresponding boundary mesh into Bempp-cl and assemble the boundary spaces there.
-Bempp-cl provides numerical trace operators that can translate from the degree of freedom (DOF) representation in FEniCSx to the dof representation in Bempp-cl.
+Bempp-cl provides numerical trace operators that can translate from the degree of freedom (DOF) representation in FEniCSx to the DOF representation in Bempp-cl.
 The corresponding translation work is handled opaquely and the user only needs to deal with high-level interfaces of FEniCSx operators, Bempp-cl operators, and trace operators.
@@
 
-Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used in this sections are simple Jupyter Notebooks that can be reproducibly executed in this provided Docker image.
+Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in this provided Docker image.
+The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.
+\mscomment{I need to make this Bempp-cl release!
+A lot has changed since the 0.2.4 release}
 
@@
 
-In implicit-solvent models, the molecule is usually considered as a region with constant permittivity, in this case, with $\epsilon_1=2$.
-In the solvent region, we used the permittivity of water ($\epsilon_2$=80) and an inverse of the Debye length of $\kappa=0.125$ \AA$^{-1}$.
-As in these cases, there is an analytical solution for $\phi_c$ in Eq.
-\eqref{eq:phic}, we compute $\phi_r$ with Eq.
-\eqref{eq:phi_reac} in both BEM-BEM and FEM-BEM coupling approaches.
-Then, for FEM-BEM, the integral over $\Gamma$ in Eq.
-\eqref{eq:phi_reac} corresponds to the trace of the solution vector from Eq.
-\eqref{eq:fembem_matrix}.
+In implicit-solvent models, the molecule is usually considered as a region with constant permittivity: in our computations, we use $\epsilon_1=2$.
+In the solvent region, we used the permittivity of water ($\epsilon_2=80$) and an inverse of the Debye length of $\kappa=0.125\,\text{\AA}^{-1}$.
+In this case, there is a known analytical solution for $\phi_c$ in Eq.~\eqref{eq:phic}, so it is enough to compute $\phi_r$.
+We do this using Eq.~\eqref{eq:phi_reac} with both BEM-BEM and FEM-BEM coupling approaches.
+For FEM-BEM, the integral over $\Gamma$ in Eq.~\eqref{eq:phi_reac} corresponds to the trace of the solution vector from Eq.~\eqref{eq:fembem_matrix}.
 
@@
 
-The Kirkwood sphere \cite{Kirkwood1934} is a standard benchmark test for the Poisson-Boltzmann equation in molecular electrostatics. 
-In this case, we considered a spherical cavity of radius $R=2$ \AA, with three charges ($q_1$=1, $q_2$=1, and $q_3$=0.75) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
-Figure \ref{fig:error_sphere} shows the error convergence of the FEM-BEM approaches, and a reference BEM implementation, to the analytical solution ($\Delta G_{solv}= -336.0396$ kcal/mol). 
+The Kirkwood sphere \cite{Kirkwood1934} is a standard benchmark test for the Poisson--Boltzmann equation in molecular electrostatics. 
+In this case, we considered a spherical cavity of radius $R=2\,\text{\AA}$, with three charges ($q_1=1$, $q_2=1$, and $q_3=0.75$) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
+Figure \ref{fig:error_sphere} shows the percentage error of the FEM-BEM approach, and a reference BEM-BEM implementation, compared to the analytical solution ($\Delta G_{\text{solv}}= -336.0396\,\text{kcal/mol}$).
 In these runs, the FEM mesh was generated using GMSH~\cite{geuzaine2009gmsh} 
@@
 with %1, 2, 4, and 8 
-2, 6, 21 and 83 vertices per \AA$^2$ on the SES, the surface mesh of this volume one was also used for the BEM runs. 
+2, 6, 21 and 83 vertices per $\text{\AA}^2$ on the SES. The trianglular mesh on the boundary surface of the FEM mesh was used for the BEM runs. 
 %For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
-The error in Figure \ref{fig:error_sphere} decays linearly with the surface area, which agrees with the expected convergence for P1 elements, indicating a correct implementation of the numerical scheme.
+The error in Figure \ref{fig:error_sphere} decays linearly with the number of vertices on the surface.
+This agrees with the expected convergence for P1 elements, indicating a correct implementation of the numerical scheme.
 %We can see that the purely BEM implementation outperforms (or not?) FEM-BEM coupling in terms of accuracy for equivalent meshes, and also that the hybrid approach does not (or does?) influence accuracy.
@@
 
-As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a purely BEM implementation for arginine.
+As a more realistic test, we assessed the performance of the FEM-BEM coupling technique against a BEM-BEM implementation for arginine.
 The structure of arginine was taken from the protein data bank, and parameterized with the Amber\cite{ponder2003force} force field. 
-We generated surface meshes containing 4.1, 6.7, 8.6, 17, and 24.5 vertices per \AA$^2$ with Nanoshaper.~\cite{decherchi2013general}
+We generated surface meshes containing 4.1, 6.7, 8.6, 17, and 24.5 vertices per $\text{\AA}^2$ with Nanoshaper.~\cite{decherchi2013general}
 These densities correspond to a grid-scale parameter in Nanoshaper equal to 1.6, 2.0, 2.4, 3.4, and 4.0, respectively, where the grid scale is the reciprocal of the average characteristic length of the triangles.
-The surface meshes were inputs to our purely BEM solver and to create the FEM mesh with pyGAMer,~\cite{lee2020open} which invoked TetGen\cite{hang2015tetgen} with a quality parameter (radius-edge ratio) of 1.0.
+For our BEM-BEM solver, we used these meshes directly.
+For the FEM-BEM solver, we created volume meshes from these using pyGAMer,~\cite{lee2020open} which invoked TetGen\cite{hang2015tetgen} with a quality parameter (radius-edge ratio) of 1.0.
 
@@
 However, if we look at the total time that solvers take to obtain the solution, we can see the advantage of using the FEM-BEM coupling.
-The higher computational cost is caused by the need of using a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM).
-Regardless, timings for the FEM-BEM coupling scale are much worse with size than its pure BEM counterpart, indicating that BEM-BEM coupling is better for larger problems.
+The higher computational cost is caused by the need to use a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM).
+The timings for the FEM-BEM coupling scale are a greater rate than the pure BEM counterpart, indicating that work on preconditioners and other acceleration methods will be required in order to make
+the FEM-BEM approach viable for large problems.
 %\textcolor{red}{Chris: I thought BEM-BEM outperformed FEM-BEM in total time.
@@
 A popular description of the molecule is to consider a permittivity that varies like a Gaussian around each atom,\cite{grant2001smooth} which has shown enhanced accuracy in some applications, like pKa calculations.\cite{li2013dielectric}
-In this setting, we define a density function $\rho$ depending on position $r$ as
+In this setting, we define a density function $\rho$ depending on the position $\mathbf{r}$ as
 %
 \begin{equation}
-\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|r-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right)
+\rho(r) := \prod_i \left(1 - \exp{\left(\frac{\|\mathbf{r}-\mathbf{x}_i\|}{\sigma^2 R_i^2}\right)}\right),
 \end{equation}
 %
-where the product runs over all the atoms of the solute, $R_i$ is the van der Waals radius of atom i, and we used $\sigma$=1. Then, we can compute the permittivity as
+where the product runs over all the atoms of the solute, $R_i$ is the van der Waals radius of atom $i$, and we used $\sigma=1$. Then, we can compute the permittivity as
 %
@@
 
-As $\epsilon$ is variable, Equation \eqref{eq:phic} does not have an analytical solution, and the electrostatic potential in the vacuum state has to be computed numerically.
-For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon_2$=2. 
+As $\epsilon$ is variable, Equation \eqref{eq:phic} does not have a known analytical solution, and the electrostatic potential in the vacuum state has to be computed numerically.
+For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon_2=2$. 
 Other implementations of Gaussian permittivities also modify the solute permittivity in vacuum calculations, according to a set cutoff.\cite{li2013dielectric} We did not consider a cutoff in our calculations.
@@
 
-Table \ref{table:arg_variable} shows a comparison of solvation energy computed with APBS and our FEM-BEM coupling approach.
-We can see that they are both converging to equivalent values, where the finest meshes agree up to 0.5\% (0.5 kcal/mol).
-The coarsest meshes used in both cases are within the recommended densities for accurate solvation energy simulations with constant permittivity.
-For example, a finite difference mesh with $h$=0.5 \AA~ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of subtracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per \AA$^2$ gives acceptable results when computing binding and solvation energies.
-We see a jump in the solvation energy for the FEM-BEM results going from 4.1 to 6.7 vertices per \AA$^2$, but later the energy monotonically decreases, converging to a solution.
+Table \ref{table:arg_variable} shows a comparison of the solvation energy computed with APBS and our FEM-BEM coupling approach.
+We can see that they are both converging to equivalent values, where the finest meshes agree to within 0.5\% (0.5 kcal/mol).
+The coarsest meshes used in both cases are within the recommended densities for accurate solvation energy simulations with constant permittivity: a finite difference mesh with $h=0.5\,\text{\AA}$ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of subtracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per $\text{\AA}^2$ gives acceptable results when computing binding and solvation energies.
+We see a jump in the solvation energy for the FEM-BEM results going from 4.1 to 6.7 vertices per $\text{\AA}^2$, but later the energy monotonically decreases, converging to a solution.
 This is an indication that mesh requirements for variable permittivities may be tighter than with a constant permittivity, even though the jump in dielectric constant across the molecular surface is usually smaller.
@@
 \centering
-\begin{tabular}{c|c|c|c}
-&Mesh size  & Grid points & $\Delta G_{solv}$\\
-&\AA       & &  kcal/mol \\
+\footnotesize
+\begin{tabular}{c|c|c}
+Mesh size (\AA)  & Grid points & \parbox{2cm}{\centering$\Delta G_{\text{solv}}$\\(kcal/mol)}\\
 \hline
-\multirow{4}{*}{APBS}& 0.52$\times$0.52$\times$0.52 & 97$\times$97$\times$97 & -107.6186 \\ 
-& 0.39$\times$0.39$\times$0.39 & 129$\times$129$\times$129 & -107.8752\\ 
-&0.26$\times$0.26$\times$0.26 & 193$\times$193$\times$193& -108.3378\\ 
-&0.195$\times$0.195$\times$0.195 & 257$\times$257$\times$257& -108.5837\\ 
-&0.098$\times$0.098$\times$0.098 & 513$\times$513$\times$513& -108.8844\\ 
-\hline
-&Mesh dens. & DOFs & $\Delta G_{solv}$\\
-&vert/\AA$^2$   &  &  kcal/mol \\
+$0.52\times0.52\times0.52$ & $97\times97\times97$ & $-107.6186$\\ 
+$0.39\times0.39\times0.39$ & $129\times129\times129$ & $-107.8752$\\ 
+$0.26\times0.26\times0.26$ & $193\times193\times193$ & $-108.3378$\\ 
+$0.195\times0.195\times0.195$ & $257\times257\times257$ & $-108.5837$\\ 
+$0.098\times0.098\times0.098$ & $513\times513\times513$ & $-108.8844$\\ 
+\end{tabular}%
+\hspace{3mm}%
+\begin{tabular}{c|c|c}
+\parbox{2.1cm}{\centering Mesh density\\(vert/$\text{\AA}^2$)}& DOFs & \parbox{2cm}{\centering$\Delta G_{\text{solv}}$\\(kcal/mol)}\\
 \hline
@@
 %\multirow{5}{*}{Standard FEM-BEM}& 2 & -36.239\\
-    & 4.1 & 3 491 & -109.931 \\
-FEM-BEM    & 6.7  & 5 787 & -110.237 \\
-coupling    & 8.57  & 8 844 & -109.661 \\
-    & 17 & 19 911 & -109.369 \\
-    & 24.5 & 32 302 & -109.315 \\
-\hline
+$4.1$ & $3\,491$ & $-109.931$ \\
+$6.7$ & $5\,787$ & $-110.237$ \\
+$8.6$ & $8\,844$ & $-109.661$ \\
+$17.0$ & $19\,911$ & $-109.369$ \\
+$24.5$ & $32\,302$ & $-109.315$ \\
 \end{tabular}
-\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using the FEM-BEM approach and APBS.
+\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using APBS(left) and the FEM-BEM approach (right).
 The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}
@@
 
-So far, we have only tested the FEM-BEM coupled approach with small structures.
-Here, we study its behaviour with larger structures to evaluate its applicability in more realistic settings, and in test cases where BEM-BEM coupling is not an alternative.
+In the experiments presented so far, we have only tested the FEM-BEM coupled approach with small structures.
+In this section, we study its behaviour with larger structures to evaluate its applicability in more realistic settings, and in test cases where BEM-BEM coupling is not an alternative.
 Using the same Gaussian permittivity field inside the molecule, we computed the solvation free energy of protein G B1 (955 atoms, PDB code 1pgb), lysozyme (1960 atoms, PDB code 1lyz), the barnase-barstar complex (9464 atoms, PDB code 1x1u), and immunoglobulin G (20148 atoms, PDB code 1igt).
-All structures were parameterized with the Amber\cite{Swanson05} force field using pdb2pqr.\cite{Dolinsky04} The surface was meshed with Nanoshaper\cite{decherchi2013general} considering a grid scale of 1.5, and then used to mesh the solute region with pyGAMer\cite{lee2020open} and TetGen\cite{hang2015tetgen} with a radius-edge ratio of 1.0.
-Solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}, showing that our FEM-BEM coupling method can reach medium-to-large-sized proteins on a workstation.
+All structures were parameterized with the Amber\cite{Swanson05} force field using pdb2pqr.\cite{Dolinsky04} The surfaces were meshed with Nanoshaper\cite{decherchi2013general} using a grid scale of 1.5, and then volume meshes were generated using pyGAMer\cite{lee2020open} and TetGen\cite{hang2015tetgen} with a radius-edge ratio of 1.0.
+The solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}.
+These results demonstrate that FEM-BEM coupling implementation can reach medium-to-large-sized proteins on a simgle workstation.
 For these larger structures, we enabled the FMM capabilities of Bempp-cl.
@@
 Table \ref{table:large_variable} shows that the iteration count increases with the problem size.
-This is expected for Johnson-N\'ed\'elec, which is the simplest coupling strategy.
-To isolate the effect of the increased iterations in the analysis, we separate timings in ``setup'' and ``solving'' time, where the ``setup'' time is independent of the number of iterations, and the ``solving'' time corresponds to the time spent in the GMRES solver.
-Then, the time-per-iteration in Table \ref{table:large_variable} only considers the ``solving'' time.
-Looking at the increase in degrees of freedom (DOFs), which grows equivalently for FEM and BEM, the ``setup'' time scales slightly worse than $\mathcal{O}(N^2)$, but represents the smaller fraction of the total time.
-On the other hand, the ``solving time per iteration'' scales closer to $\mathcal{O}(N)$, which is expected, as we are using an FMM for the BEM portion of the matrix.
-This is an indication that the high ``solving time'' is mainly due to the increase in iteration count, and having better-conditioned coupling methods, such as the so-called hybrid approach,\cite{betcke2022hybrid} can have a large impact on the time to solution.
+This is expected for Johnson--N\'ed\'elec coupling, which is the simplest coupling strategy.
+To isolate the effect of the increased iterations in the analysis, we separate timings into the setup and solving time, where the setup time is independent of the number of iterations, and the solving time corresponds to the time spent in the GMRES solver.
+The time-per-iteration is computed by dividing the solving time by the number of iterations.
+As we increase the number of degrees of freedom (DOFs), the setup time scales slightly worse than $\mathcal{O}(N^2)$ (where $N$ is the number of DOFs), but represents the smaller fraction of the total time.
+On the other hand, the time per iteration scales closer to $\mathcal{O}(N)$, which is expected as we are using FMM for the BEM portion of the matrix.
+This is an indication that the high solving time is mainly due to the increase in iteration count, and having better-conditioned coupling methods, such as the so-called hybrid approach\cite{betcke2022hybrid}, or more effective preconditioners for the blocked system would have a large impact on the time to solution.
 
@@
 %(\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}). 
-If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require to improve not only in the conditioning of the system but also in the optimization of our fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and parallelization.
+If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require the use of optimized fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and
+parellelization of the storage and solver, alongside the necessary improvements in the conditioning of the system.
 
@@
 \centering
-\resizebox{\textwidth}{!}{\begin{tabular}{c|c|c|c|c|c|c|c|c}
-Molecule & FEM  & BEM &  $\Delta G_{solv}$ & Iterations & Setup Time & Solving Time & Solv. time per & Total Time \\
-& DOFs & DOFs &  kcal/mol & & [sec] & [sec] & iter. [sec] & [sec] \\
+\footnotesize
+\begin{tabular}{c|c|c|c|c|c|c|c|c}
+Molecule & \parbox{1.1cm}{\centering FEM DOFs}  & \parbox{1.1cm}{\centering BEM DOFs} &  \parbox{1.8cm}{\centering $\Delta G_{\text{solv}}$ (kcal/mol)}& Iterations & \parbox{1.3cm}{\centering Setup time (s)} & \parbox{1.3cm}{\centering Solving time (s)} & \parbox{1.5cm}{\centering Time per iter.
+(s)} & \parbox{1.4cm}{\centering Total time (s)} \\[3mm]
 \hline
@@
 % \hline
-  1pgb  & 29 434 &  10 058 &  -300.888 & 703 & 86 & 472 & 0.67 & 789  \\
- 1lyz  & 56 114 & 18 606 &  -599.310 & 1 073 & 336 & 1 350  & 1.26 & 1 686   \\
- 1x1u & 263 181 & 81 258 & -1 982.085 & 2 791 & 8 340 & 11 000 & 3.94 & 19 340  \\
- 1igt & 597 575 & 187 712 &  -3 294.0157 & 5 366 & 41 998 & 40 100 &  7.47 & 82 098    \\
- \hline
-\end{tabular}}
+  1pgb  & $29\,434$ &  $10\,058$ &  $-300.888$ & $703$ & $86$ & $472$ & $0.67$ & $789$  \\
+ 1lyz  & $56\,114$ & $18\,606$ &  $-599.310$ & $1\,073$ & $336$ & $1\,350$  & $1.26$ & $1\,686$   \\
+ 1x1u & $263\,181$ & $81\,258$ & $-1\,982.085$ & $2\,7914$ & $8\,340$ & $11\,000$ & $3.94$ & $19\,340$  \\
+ 1igt & $597\,575$ & $187\,712$ &  $-3\,294.0157$ & $5 366$ & $41\,998$ & $40\,100$ &  $7.47$ & $82\,098$    \\
+\end{tabular}
 \caption{Results for larger structures with a variable permittivity.}

### 2023-05-03 main.tex
acknowledgements

@@
 MB acknowledges the support from Kingston University through First Kingston University Grant. \\
-CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.
+CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
+MS needs to look up the grant he has to put here. \\
+We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.
 %((Place Acknowledgments here))
@@
 \subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
-All codes to reproduce the results of this manuscript can be found in the Github repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}
+All codes to reproduce the results of this manuscript can be found in the Github repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}, alongside links to Docker images
+that include the codes alongside installations of appropriate versions of Bempp-cl and FEniCSx. \mscomment{I'll make this docker image once this paper is ready to submit}
 

### 2023-05-03 results.tex
acknowledgements

@@
 
-Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in this provided Docker image.
+Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment.
 The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.

### 2023-05-03 methods.tex
let latex put the figure where it wants
green's functions are real, so conjugates not needed

@@
 
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 %
-where $v$ is a test function, and $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})\overline{v(\mathbf{x})}\,\mathrm{d}\mathbf{x}$ and $\left\langle\varphi,v\right\rangle_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})\overline{v(\mathbf{x})}\,\mathrm{d}\mathbf{x}$ are the inner products on the surface and in the domain, respectively.
+where $v$ is a test function, and $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ and $\left\langle\varphi,v\right\rangle_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ are the inner products on the surface and in the domain, respectively.
 For the external problem with BEM, we define the Dirichlet trace~\cite{MR2361676} 
@@
 % $T:\Omega_1 \rightarrow \Gamma$ and $E:\Gamma \rightarrow \Omega_1$ trace and extendable operators respectively.
-We define the following matrices associated with the corresponding sesquilinear forms
+We define the following matrices associated with the corresponding bilinear forms
 \begin{align*}

### 2023-05-03 results.tex
remove my comments, I'll make them on GitHub instead
Update results.tex

@@
 The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.
-\mscomment{I need to make this Bempp-cl release!
-A lot has changed since the 0.2.4 release}
 
@@
 \end{tabular}
-\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using APBS(left) and the FEM-BEM approach (right).
+\caption{Solvation energy of arginine with a Gaussian-like permittivity, computed using APBS (left) and the FEM-BEM approach (right).
 The mesh density for FEM-BEM corresponds to the vertex density of the surface mesh used to generate the volumetric mesh.}

### 2023-05-03 results.tex
formatting tweak

--- 2023-05-03 results.tex
@@
 FMM assembly fits automatically into this framework and can be enabled or disabled as a simple configuration option.
+Once the discrete block matrices in Eq.~\eqref{eq:fembem_matrix} are built with Bempp-cl and FEniCSx, we assemble them into one matrix and solve the linear system with Scipy's\cite{2020SciPy-NMeth} GMRES, in this case, with a tolerance of $10^{-5}$.
 

### 2023-05-05 main.tex
remove my comments, I'll make them on GitHub instead
Changes discussed on 5/05

--- 2023-05-02 main.tex
@@
 \usepackage{hyperref}
-
-\newcommand{\mscomment}[1]{\textbf{\color{red}[Matthew: #1]}}
 
@@
 % makes references listed with 1., 2., etc.  
-0  \makeatletter
+\makeatletter
   \renewcommand\@biblabel[1]{#1.}
@@
 MB acknowledges the support from Kingston University through First Kingston University Grant. \\
-CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.
+CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
+MS needs to look up the grant he has to put here. \\
+EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1 \\
+We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.
 %((Place Acknowledgments here))
@@
 \subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
-All codes to reproduce the results of this manuscript can be found in the Github repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}
+All codes to reproduce the results of this manuscript can be found in the GitHub repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}, alongside links to Docker images
+that include the codes alongside installations of appropriate versions of Bempp-cl and FEniCSx.
 

### 2023-05-05 methods.tex
remove my comments, I'll make them on GitHub instead
Changes discussed on 5/05

@@
 and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Neumann trace).
-Note that we could use equations \eqref{eq:pbe3} and \eqref{eq:pbe4} to rewrite Equation \eqref{eq:lu} in terms of the interior traces $\phi_1$ and $\lambda_1$.
+Note that we can obtain $\phi_1$ and $\lambda_1$ from $\phi_2$ and $\lambda_2$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
 The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
@@
 %
-where $\mathbf{r}\in\Omega_1$, and we can obtain $\phi_2$ and $\lambda_2$ from $\phi_1$ and $\lambda_1$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
+where $\mathbf{r}\in\Omega_1$.
 This is valid as long as $\epsilon_1$ is a constant, so we use Eq.~\eqref{eq:phi_reac} for both BEM-BEM and FEM-BEM coupling simulations with constant $\epsilon_1$.
@@
 where $v$ is a test function, and $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ and $\left\langle\varphi,v\right\rangle_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ are the inner products on the surface and in the domain, respectively.
+To ensure clarity, we use a shorthand notation for the right-hand side where $\left\langle \cdot, \cdot \right\rangle_{\Omega_1}$ denotes duality paring.
 For the external problem with BEM, we define the Dirichlet trace~\cite{MR2361676} 
@@
 
-Then, the coupling problem can be written as: \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_2 \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$},
+Then, the coupling problem can be written as: \textit{Find $ \phi_1 \in H^1(\Omega_1)$ and $\lambda_1 \in H^{-\frac{1}{2}}(\Gamma)$ such that for all $v \in H^1(\Omega_1)$ and $\zeta \in H^{-\frac{1}{2}}(\Gamma)$},
 \begin{subequations}
@@
 \begin{align} 
- \left\langle  \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  - \left\langle \epsilon_1 \lambda_2, v \right\rangle_\Gamma &=   \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right\rangle_{\Omega_1}, \\[3mm]
-  \left\langle \left\langle\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \gamma \phi_1, \zeta \right\rangle_\Gamma + \tfrac{1}{\epsilon_2} \left\langle V_{Y}^{\Gamma}\epsilon_1\lambda_2, \zeta \right\rangle_\Gamma &=0.
+ \left\langle  \epsilon_1 \nabla \phi_1, \nabla v \right\rangle_{\Omega_1}  - \left\langle \epsilon_1 \lambda_1, v \right\rangle_\Gamma &=   \left\langle  \sum_{k=1}^{N_q} q_k\delta(\mathbf{x},\mathbf{x}_k),  v \right\rangle_{\Omega_1}, \\[3mm]
+  \left\langle \left\langle\tfrac{1}{2} I - K_{Y}^{\Gamma}\right) \gamma \phi_1, \zeta \right\rangle_\Gamma + \tfrac{1}{\epsilon_2} \left\langle V_{Y}^{\Gamma}\epsilon_1\lambda_1, \zeta \right\rangle_\Gamma &=0.
 \end{align}
@@
 functions of the finite element space $V_{h}^{j}\subset H^1(\Omega_1)$, %$\vec{\phi}_2 := [\phi_2^1, \dots, \phi_2^k]^T$ - the vector of canonical basis functions of $W_{h}^{k}$,  
-and let $\vec{\lambda}_2 := [\lambda_2^1, \dots, \lambda_2^l]^T$ be the vector of canonical basis
+and let $\vec{\lambda}_1 := [\lambda_1^1, \dots, \lambda_1^l]^T$ be the vector of canonical basis
 functions of $\Lambda_{h}^{l}\subset H^{-\frac{1}{2}}(\Gamma)$.
@@
 A_{\alpha \beta} &= \left\langle\epsilon_1\nabla\phi_1^{\alpha}, \nabla \phi_1^{\beta} \right\rangle_{\Omega_1},&
-M_{\alpha \beta} &= \left\langle \epsilon_1\lambda^{\beta}_2,\phi_1^{\alpha}\right\rangle_{\Gamma},\\
-K_{\alpha \beta} &= \left\langle K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \lambda^{\beta}_2 \right\rangle_{\Gamma},&
-V_{\alpha \beta} &= \left\langle V_{Y}^{\Gamma} \epsilon_1\lambda^{\alpha}_2, \lambda^{\beta}_2 \right\rangle_{\Gamma},\\
-I_{\alpha \beta} &= \left\langle \gamma \phi^{\alpha}_1, \lambda^{\beta}_2 \right\rangle_{\Gamma},
+\tilde{M}_{\alpha \beta} &= \left\langle \epsilon_1\lambda^{\beta}_1, \gamma \phi_1^{\alpha}\right\rangle_{\Gamma},\\
+K_{\alpha \beta} &= \left\langle K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \lambda^{\beta}_1 \right\rangle_{\Gamma},&
+V_{\alpha \beta} &= \left\langle V_{Y}^{\Gamma} \epsilon_1\lambda^{\alpha}_1, \lambda^{\beta}_1 \right\rangle_{\Gamma},\\
+M_{\alpha \beta} &= \left\langle \gamma \phi^{\alpha}_1, \lambda^{\beta}_1 \right\rangle_{\Gamma},
 \end{align*}
-\mscomment{As $I$ is not equal to the identity matrix, we should maybe change the letter we use? I'd usually change it to $M$ but we've also already used that}
 and vector associated with the corresponding linear form
@@
 \begin{bmatrix}
-A & -M^T \\  
-\left(\tfrac12 I - K \right) \gamma &  \tfrac{1}{\epsilon_2} V 
+A & -\tilde{M}^T \\  
+\left(\tfrac12 M - K \right) &  \tfrac{1}{\epsilon_2} V 
 \end{bmatrix}
@@
 \vec{\phi}_1 \\  
-\vec{\lambda}_2
+\vec{\lambda}_1
 \end{bmatrix}

### 2023-05-05 results.tex
Changes discussed on 5/05

@@
 The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.
+All codes to reproduce the results of this manuscript can be found in the GitHub repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}.
 
@@
 with %1, 2, 4, and 8 
-2, 6, 21 and 83 vertices per $\text{\AA}^2$ on the SES. The trianglular mesh on the boundary surface of the FEM mesh was used for the BEM runs. 
+2, 6, 21 and 83 vertices per $\text{\AA}^2$ on the SES. The triangular mesh on the boundary surface of the FEM mesh was used for the BEM runs. 
 %For the hybrid FEM-BEM coupling approach, we used $\tau$=5.
@@
 The higher computational cost is caused by the need to use a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM).
-The timings for the FEM-BEM coupling scale are a greater rate than the pure BEM counterpart, indicating that work on preconditioners and other acceleration methods will be required in order to make
+The timings for the FEM-BEM coupling scale are at a greater rate than the pure BEM counterpart, indicating that work on preconditioners and other acceleration methods will be required in order to make
 the FEM-BEM approach viable for large problems.
@@
 Table \ref{table:arg_variable} shows a comparison of the solvation energy computed with APBS and our FEM-BEM coupling approach.
-We can see that they are both converging to equivalent values, where the finest meshes agree to within 0.5\% (0.5 kcal/mol).
+We can see that they are both converging to equivalent values, where the solutions on the finest meshes agree to within 0.5\% (0.5 kcal/mol).
 The coarsest meshes used in both cases are within the recommended densities for accurate solvation energy simulations with constant permittivity: a finite difference mesh with $h=0.5\,\text{\AA}$ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of subtracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per $\text{\AA}^2$ gives acceptable results when computing binding and solvation energies.
@@
 The solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}.
-These results demonstrate that FEM-BEM coupling implementation can reach medium-to-large-sized proteins on a simgle workstation.
+These results demonstrate that FEM-BEM coupling implementation can reach medium-to-large-sized proteins on a simple workstation.
 For these larger structures, we enabled the FMM capabilities of Bempp-cl.
@@
 The time-per-iteration is computed by dividing the solving time by the number of iterations.
-As we increase the number of degrees of freedom (DOFs), the setup time scales slightly worse than $\mathcal{O}(N^2)$ (where $N$ is the number of DOFs), but represents the smaller fraction of the total time.
+As we increase the number of degrees of freedom (DOFs), the setup time scales slightly worse than $\mathcal{O}(N^2)$ (where $N$ is the number of DOFs) but represents the smaller fraction of the total time.
 On the other hand, the time per iteration scales closer to $\mathcal{O}(N)$, which is expected as we are using FMM for the BEM portion of the matrix.

### 2023-05-05 results.tex
Typo in the last table

@@
 
-Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href{https://bempp.com/installation.html}{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment.
+Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available ( \url{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment.
 The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.
@@
  1lyz  & $56\,114$ & $18\,606$ &  $-599.310$ & $1\,073$ & $336$ & $1\,350$  & $1.26$ & $1\,686$   \\
- 1x1u & $263\,181$ & $81\,258$ & $-1\,982.085$ & $2\,7914$ & $8\,340$ & $11\,000$ & $3.94$ & $19\,340$  \\
- 1igt & $597\,575$ & $187\,712$ &  $-3\,294.0157$ & $5 366$ & $41\,998$ & $40\,100$ &  $7.47$ & $82\,098$    \\
+ 1x1u & $263\,181$ & $81\,258$ & $-1\,982.085$ & $2\,791$ & $8\,340$ & $11\,000$ & $3.94$ & $19\,340$  \\
+ 1igt & $597\,575$ & $187\,712$ &  $-3\,294.0157$ & $5\, 366$ & $41\,998$ & $40\,100$ &  $7.47$ & $82\,098$    \\
 \end{tabular}

### 2023-05-05 main.tex
small tweaks

@@
 \subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
-All codes to reproduce the results of this manuscript can be found in the GitHub repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}, alongside links to Docker images
+All codes to reproduce the results of this manuscript can be found in the GitHub repository \href[https://github.com/MichalBosy/FEM_BEM_coupling/]{github.com/MichalBosy/FEM_BEM_coupling}, alongside links to Docker images
 that include the codes alongside installations of appropriate versions of Bempp-cl and FEniCSx.

### 2023-05-05 results.tex
small tweaks

@@
 
-Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available ( \url{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment.
+Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\href[https://bempp.com/installation.html]{bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment.
 The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.
-All codes to reproduce the results of this manuscript can be found in the GitHub repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}.
+All codes to reproduce the results of this manuscript can be found in the GitHub repository \href[https://github.com/MichalBosy/FEM_BEM_coupling/]{github.com/MichalBosy/FEM_BEM_coupling}.
 
@@
 The solvation free energy and timings for these runs are presented in Table \ref{table:large_variable}.
-These results demonstrate that FEM-BEM coupling implementation can reach medium-to-large-sized proteins on a simple workstation.
+These results demonstrate that our FEM-BEM coupling implementation can reach medium-to-large-sized proteins on a simple workstation.
 For these larger structures, we enabled the FMM capabilities of Bempp-cl.

### 2023-05-05 main.tex
add coupling grant

@@
 CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
-MS needs to look up the grant he has to put here. \\
+MS acknowledges support from EPSRC grant EP/W007460/1 \\
 EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1 \\

### 2023-05-05 results.tex
url not href

--- 2023-05-05 results.tex
@@
 
-Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available ( \url{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment.
+Docker images containing FEniCSx, Bempp-cl, and Exafmm-t are publicly available (\url{https://bempp.com/installation.html}), and all codes used to generate the results in this section are available as Jupyter Notebooks that can be reproducibly executed in an appropriate environment.
 The results in this section were obtained using version 0.6.0 of FEniCSx and version 0.3.0 of Bempp-cl.

### 2023-05-05 main.tex
modified graphical abstract

@@
 \begin{minipage}{1.0\textwidth}
-\includegraphics[width=50mm,height=50mm]{graphical_abstract_fem-bem.png} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
+\includegraphics[width=50mm,height=50mm]{graphical_abstract_fem-bem2.png} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
 %\includegraphics[width=110mm,height=20mm]{cc.eps}

### 2023-05-09 main.tex
TB acknowledgement

@@
 MB acknowledges the support from Kingston University through First Kingston University Grant. \\
+MS acknowledges support from EPSRC grant EP/W007460/1 \\
+TB acknowledges support from EPSRC grants EP/W007460/1 and EP/W026260/1. \\
+EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1. \\
 CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
-MS acknowledges support from EPSRC grant EP/W007460/1 \\
-EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1 \\
 We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.

### 2023-05-10 intro.tex
added Nakov reference

@@
 
-The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
+The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010,nakov2021argos}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
 In particular, the boundary element method (BEM) has proven to be very efficient for high-accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.

### 2023-05-10 main.tex
added orcids

@@
 \title{Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation}
-\author{Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK}, 
-    Matthew W. Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
-    Timo Betcke\footnotemark[2],~\\%\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
-    Erik Burman\footnotemark[2],~%\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
-    Christopher D. Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile}}
+\author{Micha\l{} Bosy\thanks{School of Computer Science and Mathematics, Kingston University London, Penrhyn Road, Kingston upon Thames, KT1 2EE, UK} \thanks{ORCID: 0000-0003-2723-6913}, 
+    Matthew W. Scroggs\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK} \thanks{ORCID: 0000-0002-4658-2443}, 
+    Timo Betcke\footnotemark[2] \thanks{ORCID: 0000-0002-3323-2110},~\\%\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
+    Erik Burman\footnotemark[2] \thanks{ORCID: 0000-0003-4287-7241},~%\thanks{Department of Mathematics, University College London, 25 Gordon Street, WC1H 0AY London, UK}, 
+    Christopher D.
+Cooper\thanks{Department of Mechanical Engineering and Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso 2390123, Chile} \thanks{ORCID: 0000-0003-0282-8998}}
 

### 2023-09-08 results.tex
added binding energy results

@@
 \section*{\sffamily \Large Results with variable permittivity}
+
+\subsection*{\sffamily \large Note on modeling differences between finite difference and finite/boundary element methods}
+
+To facilitate verification, we conducted a comparative analysis between our FEM-BEM approach and established Poisson-Boltzmann solvers, including APBS,\cite{BakerETal2001} MIBPB,\cite{geng2007treatment} CPB,\cite{boschitsch2011fast} PBSA,\cite{XX}, and Delphi.\cite{rocchia2001extending}
+These benchmarks primarily employ finite difference approximations, setting the stage for inherent modeling disparities with respect to our FEM-BEM method, making this comparison a difficult task.
+Firstly, it naturally enforces the decay of the electrostatic potential to zero at infinity in the exterior domain through the boundary integral formulation, while finite difference-based solvers necessitate the imposition of effective boundary conditions along the mesh periphery.
+This boundary condition critically influences the electrostatic potential and may deviate from the true solution if the size of the mesh box is insufficient. 
+Secondly, the definition of the molecular surface differs slightly across software.
+Our FEM-BEM approach employs a triangulation of the solvent-excluded surface, ensuring exact enforcement of interface conditions.
+In contrast, finite difference meshes inherently produce a staircase representation of this surface. 
+While the matched interface technique in MIBPB\cite{geng2007treatment} addresses this discrepancy, it does not fully align with our triangulation-based molecular surface representation.
+
+\subsection*{\sffamily \large Binding energy calculations for a large data set}
+
+The binding energy of two molecules in a complex is 
+%
+\begin{equation}
+\Delta G_{bind} = \Delta G_{solv, complex} - \Delta G_{solv,1} - \Delta G_{solv, 2} + \Delta G_{coul}
+\end{equation}
+%
+where $\Delta G_{solv, complex}$ is the solvation energy of the complex, $\Delta G_{solv, 1}$ and $\Delta G_{solv, 2}$ are the solvation energies of the two compounds, and $\Delta G_{coul}$ is the difference in Coulomb energy between bound and unbound states.
+This calculation presents a major challenge, as small errors in solvation energy may result in large errors in binding energy, making accuracy crucial.
+
+Folllowing the data set proposed by Fenley and co-workers,\cite{HarrisBoschitcshFenley2013} available in \url{http://www.sb.fsu.edu/~mfenley/convergence/downloads/convergence_pqr_sets.tar.gz}, and later used by Wei {\it et al.}\cite{} to assess the accuracy of different Poisson-Boltzmann solvers, we performed a comparison with binding energies computed using our method.
+We first performed a mesh refinement study with the structure of 1biv, available in that same data set, to decide on an appropriate mesh density.
+Table XX shows that finite element grids generated from a surface mesh with 12, 17 and 24 vertices per \AA$^2$ are within the convergence region ({\it ie.} the observed order of convergence agrees with the theoretical order of the method).\cite{Roache1998,CooperBardhanBarba2014}
+In all cases, we used TetGen with a quality parameter of 1.1.
+From this result, we performed Richardson extrapolation to get an approximate true solution, and found that the mesh with 24 vertices per \AA$^2$ was XX\% away, which we chose for the remaining of this test.
+
+Even though we used a constant permittivity inside the molecular region, in several cases there were voids where a water molecule fits. 
+In a finite difference description, these voids are naturally considered as pockets of solvent, with the permittivity of water ($\epsilon=\epsilon_2$).
+Regardless if this is an appropriate physical model, we also considered cavities that way for comparison purposes.
+This meant that had to detect the cavities and use a piece-wise constant description of the permittivity inside the molecular region, further supporting the applicability of FEM in this domain.
+
+Figures \ref{fig:dna_drug,fig:barnase_barstar,fig:rna_peptide} show the binding energies of structures of a DNA-drug complex, the barnase-barstar complex, and a RNA-peptide complex, respectively, presented in Fenley's data set.\cite{HarrisBoschitcshFenley2013} The data for CPB\cite{HarrisBoschitcshFenley2013} and MIBPB, Delphi, APBS and PBSA where taken from the literature,\cite{Nguyen} for the finest mesh reported.
+From Figures \ref{fig:dna_drug,fig:barnase_barstar,fig:rna_peptide} it is evident that our FEM-BEM approach gives results that are within the range of the other software.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{binding_energy_dna-drug.pdf}
+\caption{Binding energies for structures corresponding to a DNA-drug complex}
+\label{fig:dna_drug}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{binding_energy_barnase-barstar.pdf}
+\caption{Binding energies for structures corresponding to the barnase-barstar complex}
+\label{fig:barnase_barstar}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{binding_energy_rna-peptide.pdf}
+\caption{Binding energies for structures corresponding to a RNA-peptide complex}
+\label{fig:rna_peptide}
+\end{figure}
 

### 2023-09-11 results.tex
edits to new results

--- 2023-05-05 results.tex
@@
 
-\subsection*{\sffamily \large Motivation: modeling the solute with a Gaussian-based variable permittivity}
+\subsection*{\sffamily \large Note on modeling differences between finite difference and finite/boundary element methods}
+
+To facilitate verification, we conducted a comparative analysis between our FEM-BEM approach and established Poisson-Boltzmann solvers, including APBS,\cite{BakerETal2001} MIBPB,\cite{geng2007treatment,chen2011mibpb} CPB,\cite{boschitsch2011fast} PBSA,\cite{wang2008poisson,cai2010performance} and Delphi.\cite{rocchia2001extending}
+These benchmarks primarily employ finite difference approximations, setting the stage for inherent modeling disparities with respect to our FEM-BEM method, and making this comparison a difficult task.
+Firstly, the boundary integral formulation in the external domain naturally enforces the decay of the electrostatic potential to zero at infinity, while finite difference-based solvers necessitate the imposition of effective boundary conditions along the mesh periphery.
+This boundary condition critically influences the electrostatic potential and may deviate from the true solution if the size of the mesh box is insufficient. 
+Secondly, the definition of the molecular surface differs slightly across software, resulting in different domain geomteries. 
+Our FEM-BEM approach employs a triangulation of the solvent-excluded surface (based on NanoShaper\cite{decherchi2013general}), while finite difference meshes produce a staircase representation of this surface.
+This discrepancy is addressed by the matched interface technique in MIBPB,\cite{geng2007treatment,chen2011mibpb} however, the resulting surface does not exactly match NanoShaper's triangulation.
+
+\subsection*{\sffamily \large Binding energy calculations for a large data set}
+
+The binding energy of two molecules in a complex is 
+%
+\begin{equation}
+\Delta G_{bind} = \Delta G_{solv, complex} - \Delta G_{solv,1} - \Delta G_{solv, 2} + \Delta G_{coul}
+\end{equation}
+%
+where $\Delta G_{solv, complex}$ is the solvation energy of the complex, $\Delta G_{solv, 1}$ and $\Delta G_{solv, 2}$ are the solvation energies of the two compounds, and $\Delta G_{coul}$ is the difference in Coulomb energy between bound and unbound states.
+This calculation presents a major challenge, as small errors in solvation energy may have a large impact result in in binding energy, making accuracy crucial.
+
+Folllowing the data set proposed by Fenley and co-workers,\cite{HarrisBoschitcshFenley2013} available in \url{http://www.sb.fsu.edu/~mfenley/convergence/downloads/convergence_pqr_sets.tar.gz}, and later used by Wei {\it et al.}\cite{nguyen2017accurate} to assess the accuracy of different Poisson-Boltzmann solvers, we tested our method by computing binding energies.
+We first performed a mesh refinement study with the structure of 1biv, available in that same data set, to decide on an appropriate mesh density.
+Table XX shows that finite element grids generated from a surface mesh with 12, 17 and 24 vertices per \AA$^2$, and a quality parameter of 1.1 in TetGen, are within the convergence region ({\it ie.} the observed order of convergence agrees with the theoretical order of the method).\cite{roache1998verification,CooperBardhanBarba2014}
+From this result, we performed Richardson extrapolation to get an approximate true solution, and found that the mesh with 24 vertices per \AA$^2$ was XX\% away, which we chose for the remaining of this test.
+
+Several structure in the data base contained voids inside the molecular region where a water molecule fits. 
+In a finite difference description, these voids are naturally considered as pockets of solvent, with the permittivity of water ($\epsilon=\epsilon_2$).
+Regardless if this is an appropriate physical model, we also placed the permittivity of bulk water inside cavities for comparison purposes.
+In the FEM formalism, we had to detect the elements contained by cavities and use a piece-wise constant varying description of the permittivity inside the molecular region, which can be done without any modification in the formulation.
+A BEM-BEM formulation can also account for cavities this way,\cite{AltmanBardhanWhiteTidor09,CooperBardhanBarba2014} but involves certain adjustments in the stiffness matrix.
+
+Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} show the binding energies of structures of a DNA-drug complex, the barnase-barstar complex, and a RNA-peptide complex, respectively, presented in Fenley's data set.\cite{HarrisBoschitcshFenley2013} The data for CPB\cite{HarrisBoschitcshFenley2013} and MIBPB, Delphi, APBS and PBSA where taken from the literature,\cite{nguyen2017accurate} for the finest mesh reported.
+From Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} it is evident that our FEM-BEM approach gives results that are within the range of the other software.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{binding_energy_dna-drug.pdf}
+\caption{Binding energies for structures corresponding to a DNA-drug complex}
+\label{fig:dna_drug}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{binding_energy_barnase-barstar.pdf}
+\caption{Binding energies for structures corresponding to the barnase-barstar complex}
+\label{fig:barnase_barstar}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{binding_energy_rna-peptide.pdf}
+\caption{Binding energies for structures corresponding to a RNA-peptide complex}
+\label{fig:rna_peptide}
+\end{figure}
+
+\subsection*{\sffamily \large Modeling the solute with a Gaussian-based variable permittivity}
 
@@
 
-\subsection*{\sffamily \large Convergence for arginine with APBS}
+\subsubsection*{\sffamily \normalsize Convergence for arginine with APBS}
 

### 2023-09-11 conclusion.tex
edits to new results

@@
 This brings the best of both worlds: the accuracy and efficiency of BEM to exactly enforce the boundary conditions at infinity, and the flexibility of FEM to account for space variations of the material properties and nonlinearities.
-After presenting verification results for a sphere and arginine with a constant permittivity inside the solute, we showcased our implementation with an advanced modeling technique that considers Gaussian-varying permittivities in a confined region, with the results validated against the widely-used APBS software.
+After presenting verification results of solvation energy for a sphere and arginine with a constant permittivity inside the solute, and binding energy  for an extensive data set, we showcased our implementation with an advanced modeling technique that considers Gaussian-varying permittivities in a confined region, with the results validated against the widely-used APBS software.
 The final scaling results for larger molecules start from protein G B1 (955 atoms) and go up to immunoglobulin G (20\,148 atoms), proving the applicability of this approach for realistic problems.

### 2023-09-11 main.tex
edits to new results

@@
 We showcase our implementation by computing the polar component of the solvation free energy of a set of molecules using a constant and a Gaussian-varying permittivity.
-We validate our implementation against the finite difference code APBS (to 0.5\%), and show scaling from protein G B1 (955 atoms) up to immunoglobulin G (20\,148 atoms).
+As validation, we compare against well-established finite difference solvers for an extensive binding energy data set, and with the finite difference code APBS (to 0.5\%) for Gaussian permittivities.
+We also show scaling results from protein G B1 (955 atoms) up to immunoglobulin G (20\,148 atoms).
 For small problems, the coupled method was efficient, outperforming a purely boundary integral approach.

### 2023-09-11 results.tex
edits to new results

@@
 Folllowing the data set proposed by Fenley and co-workers,\cite{HarrisBoschitcshFenley2013} available in \url{http://www.sb.fsu.edu/~mfenley/convergence/downloads/convergence_pqr_sets.tar.gz}, and later used by Wei {\it et al.}\cite{nguyen2017accurate} to assess the accuracy of different Poisson-Boltzmann solvers, we tested our method by computing binding energies.
-We first performed a mesh refinement study with the structure of 1biv, available in that same data set, to decide on an appropriate mesh density.
-Table XX shows that finite element grids generated from a surface mesh with 12, 17 and 24 vertices per \AA$^2$, and a quality parameter of 1.1 in TetGen, are within the convergence region ({\it ie.} the observed order of convergence agrees with the theoretical order of the method).\cite{roache1998verification,CooperBardhanBarba2014}
-From this result, we performed Richardson extrapolation to get an approximate true solution, and found that the mesh with 24 vertices per \AA$^2$ was XX\% away, which we chose for the remaining of this test.
+This data set consists of three family of structures: DNA-drug complexes, different versions of the barnase-barstar complex, and RNA-peptide complexes.
+
+According to the arginine results in Figure \ref{fig:arg_constant_energy}, a mesh density of 24 vertices per \AA$^2$ gives a solvation energy that is close to the true solution for a realistic geometry.
+In that case, the difference in solvation energy between calculations using finite element grids generated from a surface mesh of 8.6 and 24.5 vertices per \AA$^2$ (a 3$\times$ refinement) is less than 1\%.
+Then, we used surface meshes with 24 vertices per \AA$^2$ and a quality parameter of 1.1 in TetGen to generate the meshes used to compute binding energies in Fenley's data base.
 
@@
 
-Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} show the binding energies of structures of a DNA-drug complex, the barnase-barstar complex, and a RNA-peptide complex, respectively, presented in Fenley's data set.\cite{HarrisBoschitcshFenley2013} The data for CPB\cite{HarrisBoschitcshFenley2013} and MIBPB, Delphi, APBS and PBSA where taken from the literature,\cite{nguyen2017accurate} for the finest mesh reported.
+Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} show the binding energies of structures of DNA-drug complexes, barnase-barstar complexes, and RNA-peptide complexes, respectively, presented in Fenley's data set.\cite{HarrisBoschitcshFenley2013} The data for CPB\cite{HarrisBoschitcshFenley2013} and MIBPB, Delphi, APBS and PBSA where taken from the literature,\cite{nguyen2017accurate} for the finest mesh reported.
 From Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} it is evident that our FEM-BEM approach gives results that are within the range of the other software.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{binding_energy_dna-drug.pdf}
-\caption{Binding energies for structures corresponding to a DNA-drug complex}
+\includegraphics[width=\textwidth]{binding_energy_dna-drug.pdf}
+\caption{Binding energies for structures corresponding to DNA-drug complexes.}
 \label{fig:dna_drug}
@@
 \centering
-\includegraphics[width=\textwidth]{binding_energy_barnase-barstar.pdf}
-\caption{Binding energies for structures corresponding to the barnase-barstar complex}
+\includegraphics[width=0.7\textwidth]{binding_energy_barnase-barstar.pdf}
+\caption{Binding energies for structures corresponding to the barnase-barstar complex.}
 \label{fig:barnase_barstar}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{binding_energy_rna-peptide.pdf}
-\caption{Binding energies for structures corresponding to a RNA-peptide complex}
+\includegraphics[width=0.7\textwidth]{binding_energy_rna-peptide.pdf}
+\caption{Binding energies for structures corresponding to RNA-peptide complexes.}
 \label{fig:rna_peptide}

### 2023-09-12 results.tex
Updated results

@@
 
-Folllowing the data set proposed by Fenley and co-workers,\cite{HarrisBoschitcshFenley2013} available in \url{http://www.sb.fsu.edu/~mfenley/convergence/downloads/convergence_pqr_sets.tar.gz}, and later used by Wei {\it et al.}\cite{nguyen2017accurate} to assess the accuracy of different Poisson-Boltzmann solvers, we tested our method by computing binding energies.
-This data set consists of three family of structures: DNA-drug complexes, different versions of the barnase-barstar complex, and RNA-peptide complexes.
+Following the data set proposed by Fenley and co-workers,\cite{HarrisBoschitcshFenley2013} available in \url{http://www.sb.fsu.edu/~mfenley/convergence/downloads/convergence_pqr_sets.tar.gz}, and later used by Wei {\it et al.}\cite{nguyen2017accurate} to assess the accuracy of different Poisson-Boltzmann solvers, we tested our method by computing binding energies.
+This data set consists of three families of structures: DNA-drug complexes, different versions of the barnase-barstar complex, and RNA-peptide complexes.
+Following the problem setting for these data sets, we use $\epsilon_1=1$, $\epsilon_2=80$ and an inverse of the Debye length of $\kappa=0.10265\,\text{\AA}^{-1}$.
 
@@
 In that case, the difference in solvation energy between calculations using finite element grids generated from a surface mesh of 8.6 and 24.5 vertices per \AA$^2$ (a 3$\times$ refinement) is less than 1\%.
-Then, we used surface meshes with 24 vertices per \AA$^2$ and a quality parameter of 1.1 in TetGen to generate the meshes used to compute binding energies in Fenley's data base.
+Then, we used surface meshes with 24 vertices per \AA$^2$ and a quality parameter of 1.1 in TetGen to generate the meshes used to compute binding energies in Fenley's database.
 
-Several structure in the data base contained voids inside the molecular region where a water molecule fits. 
+Several structures in the database contained voids inside the molecular region where a water molecule fits. 
 In a finite difference description, these voids are naturally considered as pockets of solvent, with the permittivity of water ($\epsilon=\epsilon_2$).
@@
 
-Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} show the binding energies of structures of DNA-drug complexes, barnase-barstar complexes, and RNA-peptide complexes, respectively, presented in Fenley's data set.\cite{HarrisBoschitcshFenley2013} The data for CPB\cite{HarrisBoschitcshFenley2013} and MIBPB, Delphi, APBS and PBSA where taken from the literature,\cite{nguyen2017accurate} for the finest mesh reported.
+Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} show the binding energies of structures of DNA-drug complexes, barnase-barstar complexes, and RNA-peptide complexes, respectively, presented in Fenley's data set.\cite{HarrisBoschitcshFenley2013} The data for CPB\cite{HarrisBoschitcshFenley2013} and MIBPB, Delphi, APBS and PBSA were taken from the literature,\cite{nguyen2017accurate} for the finest mesh reported.
 From Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} it is evident that our FEM-BEM approach gives results that are within the range of the other software.
@@
 %(\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}). 
-If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require the use of optimized fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and
+If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require the use of optimised fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and
 parellelization of the storage and solver, alongside the necessary improvements in the conditioning of the system.

### 2023-09-13 conclusion.tex
Updating according to Reviewers

--- 2023-05-03 conclusion.tex
@@
 This brings the best of both worlds: the accuracy and efficiency of BEM to exactly enforce the boundary conditions at infinity, and the flexibility of FEM to account for space variations of the material properties and nonlinearities.
-After presenting verification results for a sphere and arginine with a constant permittivity inside the solute, we showcased our implementation with an advanced modeling technique that considers Gaussian-varying permittivities in a confined region, with the results validated against the widely-used APBS software.
+After presenting verification results of solvation energy for a sphere and arginine with a constant permittivity inside the solute, and binding energy for an extensive data set, we showcased our implementation with an advanced modelling technique that considers Gaussian-varying permittivities in a confined region, with the results validated against the widely-used APBS software.
 The final scaling results for larger molecules start from protein G B1 (955 atoms) and go up to immunoglobulin G (20\,148 atoms), proving the applicability of this approach for realistic problems.
-Even though our implementation was able to reach medium-to-large systems, we recongnize the need for further research towards better preconditioning of the linear system, optimizing the coupling technique, acceleration algorithms, and parallel execution, especially as we look towards much larger solutes, like viruses.
+Even though our implementation was able to reach medium-to-large systems, we recognise the need for further research towards better preconditioning of the linear system, optimising the coupling technique, acceleration algorithms, and parallel execution, especially as we look towards much larger solutes, like viruses.
 We hope this proof-of-concept work will serve as motivation for future model development that considers space-varying permittivities and Debye lengths, and mixed linear-nonlinear techniques, especially for highly-charged systems, like nucleic acids.

### 2023-09-13 intro.tex
Updating according to Reviewers

--- 2023-05-03 intro.tex
@@
 Highly detailed models consider every water molecule and salt ion explicitly.
-For solutions with large numbers of molecules, however, these models can be very compuationally expensive, so implicit-solvent models---approximated models that use continuum theory to represent the ionic solution---are often used instead.\cite{RouxSimonson1999,DecherchiETal2015}
+For solutions with large numbers of molecules, however, these models can be very computationally expensive, so implicit-solvent models---approximated models that use continuum theory to represent the ionic solution---are often used instead.\cite{RouxSimonson1999,DecherchiETal2015}
 In the case of electrostatics, the implicit-solvent model is mathematically characterized by the Poisson--Boltzmann equation (PBE)\cite{Baker2004,Bardhan2012}, which is widely used to compute solvation free energies and mean-field potentials.
@@
 The implicit-solvent model for electrostatics describes the dissolved molecule as an infinite medium with a low-dielectric solute-shaped cavity, which contains a charge distribution from the partial charges---usually a sum of Dirac deltas at the atom's locations.
-The outer solvent region is represented with a high dielectric constant, and considers the presence of salt.
+The outer solvent region is represented with a high dielectric constant and considers the presence of salt.
 These two regions are interfaced by the molecular surface where the continuity of the electrostatic potential and electric displacement are enforced.
@@
 
-The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytical\cite{YapHeadgordon2010,FelbergETal2017} methods.
+The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010,nakov2021argos}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytic\cite{YapHeadgordon2010,FelbergETal2017} methods.
 In particular, the boundary element method (BEM) has proven to be very efficient for high-accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.
@@
 FEM-BEM coupling is a popular technique in the context of mixed linear-nonlinear models,\cite{carstensen1995coupling,aurada2013classical} fracture mechanics,\cite{aour2007coupled} fluid-structure interaction,\cite{estorff1991fem} acoustics,\cite{hiptmair2006stabilized} and electromagnetics.\cite{matsuoka1988calculation,hiptmair2008stabilized,bruckner20123d}
-On the other hand, the PBE has been solved with hybrid numerical methods in the past: for example, by coupling finite differences with boundary elements\cite{boschitsch2004hybrid} or finite elements\cite{xie2016new,ying2018hybrid} to solve the nonlinear PBE in a specific region, and to implement modifications to the PBE model ({\it ie.} the size-modified PBE).
+On the other hand, the PBE has been solved with hybrid numerical methods in the past: for example, by coupling finite differences with boundary elements\cite{boschitsch2004hybrid} or finite elements\cite{xie2016new,ying2018hybrid} to solve the nonlinear PBE in a specific region, and to implement modifications to the PBE model (i.e.
+the size-modified PBE).
 To the best of our knowledge, this is the first time finite and boundary elements have been combined in this application.
 
-In this paper, we prototype this principle with the simplest implementation possible: a Johnson--N\'ed\'elec\cite{johnson1980coupling} coupling, where we solve using mass-matrix and diagonal preconditioning and whithout distributed memory execution.
-This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in open source software libraries.
+In this paper, we prototype this principle with the simplest implementation possible: a Johnson--N\'ed\'elec\cite{johnson1980coupling} coupling, where we solve using mass-matrix and diagonal preconditioning and without distributed memory execution.
+This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in open-source software libraries.
 In this work, we use the boundary element library Bempp-cl\cite{BetckeScroggs2021} and the finite element library FEniCSx\cite{BasixJoss,BasixDofTransformations}.

### 2023-09-13 main.tex
Updating according to Reviewers

@@
 However, the boundary element method is limited to linear equations and piecewise constant variations of the material properties.
-In this work, we present a scheme that couples finite and boundary elements for the Poisson--Boltzmann equation, where the finite element method is applied in a confined {\it solute} region, and the boundary element method in the external {\it solvent} region.
+In this work, we present a scheme that couples finite and boundary elements for the Poisson--Boltzmann equation, where the finite element method is applied in a confined {\it solute} region and the boundary element method in the external {\it solvent} region.
 As a proof-of-concept exercise, we use the simplest methods available: Johnson--N\'ed\'elec coupling with mass matrix and diagonal preconditioning, implemented using the Bempp-cl and FEniCSx libraries via their Python interfaces.
@@
 For small problems, the coupled method was efficient, outperforming a purely boundary integral approach.
-For Gaussian-varying permittivities, which are beyond the applicability of boundary elements alone, we were able to run medium to large sized problems on a single workstation.
-Development of better preconditioning techniques and the use of distributed memory parallelism for larger systems remains an area for future work.
+For Gaussian-varying permittivities, which are beyond the applicability of boundary elements alone, we were able to run medium to large-sized problems on a single workstation.
+The development of better preconditioning techniques and the use of distributed memory parallelism for larger systems remains an area for future work.
 We hope this work will serve as inspiration for future developments that consider space-varying field parameters, and mixed linear-nonlinear schemes for molecular electrostatics with implicit solvent models.
@@
 %((Main text paragraphs should be 12 point font, double-spaced.
-Reviews are comprehensive survey of recent progress in a topic of broad interest in quantum chemistry, providing the readership with an appreciation of the importance of the work, a summary of recent developments, and a guide to the relevant literature.
+Reviews are a comprehensive survey of recent progress in a topic of broad interest in quantum chemistry, providing the readership with an appreciation of the importance of the work, a summary of recent developments, and a guide to the relevant literature.
 Perspective are short discussions of an important emerging topics in quantum chemistry, usually focused on no more than a few recently published papers, and including the authors' vision for the future of the topics, identifying important problems that should be addressed next.
@@
 \subsection*{\sffamily \large ACKNOWLEDGMENTS}
-MB acknowledges the support from Kingston University through First Kingston University Grant. \\
+MB acknowledges the support from Kingston University through the First Kingston University Grant. \\
 MS acknowledges support from EPSRC grant EP/W007460/1 \\

### 2023-09-13 methods.tex
Typo in the last table
small tweaks
the
Updating according to Reviewers

@@
 
-The implicit solvent model\cite{RouxSimonson1999,DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson--Boltzmann equation governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson equation govnerns in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}).
+The implicit solvent model\cite{RouxSimonson1999, DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson--Boltzmann equation governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson equation governs in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}).
 These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous across the surface.
@@
 Physically, $\phi_c$ can be interpreted as the Coulomb-type potential from the point charges, whereas $\phi_r$, also known as reaction potential, is originated by the polarization of the solvent and reorganization of the free ions.
-Usually, $\epsilon_1$ is considered a constant value, yielding an analytical expression for $\phi_c$. However, this is not the general case.
+Usually, $\epsilon_1$ is considered a constant value, yielding an analytic expression for $\phi_c$. However, this is not the general case.
 
-Regularized versions of the equations in \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008,LeeGengZhao2021} are widely used to numerically solve the Poisson--Boltzmann equation with finite element or finite difference methods, and have recently been extended to super-Gaussian permittivities in the solute.\cite{wang2022regularization} However, here we use the standard formulation in \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permittivities, beyond super-Gaussian descriptions.
+Regularized versions of the equations in \eqref{eq:pbe} \cite{LuZhouHolstMcCammon2008, LeeGengZhao2021} are widely used to numerically solve the Poisson--Boltzmann equation with finite element or finite difference methods, and have recently been extended to super-Gaussian permittivities in the solute.\cite{wang2022regularization} However, here we use the standard formulation in \eqref{eq:pbe}, as it offers more flexibility when dealing with, for example, variable permittivities, beyond super-Gaussian descriptions.
 
@@
 However, the resulting system is usually ill-conditioned.
-Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006,LuETal2009,debuhr2016dashmm} which reads
+Here, we use the better-conditioned formulation presented by Lu and co-workers,~\cite{LuETal2006, LuETal2009,debuhr2016dashmm} which reads
 %
@@
 where $v$ is a test function, and $\left\langle\varphi,v\right\rangle_\Gamma = \int_\Gamma \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ and $\left\langle\varphi,v\right\rangle_{\Omega_1} = \int_{\Omega_1} \varphi(\mathbf{x})v(\mathbf{x})\,\mathrm{d}\mathbf{x}$ are the inner products on the surface and in the domain, respectively.
-To ensure clarity, we use a shorthand notation for the right-hand side where $\left\langle \cdot, \cdot \right\rangle_{\Omega_1}$ denotes duality paring.
+Slightly abusing notation, the product $\left\langle \cdot, \cdot \right\rangle_{\Omega_1}$ on the right-hand side denotes the duality pairing.
 For the external problem with BEM, we define the Dirichlet trace~\cite{MR2361676} 
@@
 A_{\alpha \beta} &= \left\langle\epsilon_1\nabla\phi_1^{\alpha}, \nabla \phi_1^{\beta} \right\rangle_{\Omega_1},&
-\tilde{M}_{\alpha \beta} &= \left\langle \epsilon_1\lambda^{\beta}_1, \gamma \phi_1^{\alpha}\right\rangle_{\Gamma},\\
+\widetilde{M}_{\alpha \beta} &= \left\langle \epsilon_1\lambda^{\beta}_1, \gamma \phi_1^{\alpha}\right\rangle_{\Gamma},\\
 K_{\alpha \beta} &= \left\langle K_{Y}^{\Gamma} \gamma \phi^{\alpha}_1, \lambda^{\beta}_1 \right\rangle_{\Gamma},&
@@
 \begin{bmatrix}
-A & -\tilde{M}^T \\  
-\left(\tfrac12 M - K \right) &  \tfrac{1}{\epsilon_2} V 
+A & -\widetilde{M}^T \\  
+\tfrac12 M - K &  \tfrac{1}{\epsilon_2} V 
 \end{bmatrix}

### 2023-09-13 results.tex
Updating according to Reviewers

@@
-This section presents the verification and performance results of the presented FEM-BEM coupling schemes for molecules modeled as cavities with constant and varying permittivity.
-With a constant permittivity inside the molecule, we tested convergence against an analytical expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
+This section presents the verification and performance results of the presented FEM-BEM coupling schemes for molecules modelled as cavities with constant and varying permittivity.
+With a constant permittivity inside the molecule, we tested convergence against an analytic expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
 We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.
@@
 
-For the finite element computations, we use the software package FEniCSx~\cite{BasixJoss,BasixDofTransformations} while for the boundary element computations, we use Bempp-cl~\cite{BetckeScroggs2021} together with Exafmm-t~\cite{exafmm-t}.
-FEniCSx is the successor of the widely used FEniCS finite element library\cite{FEniCS,FEniCS-book}.
+For the finite element computations, we use the software package FEniCSx~\cite{BasixJoss, BasixDofTransformations} while for the boundary element computations, we use Bempp-cl~\cite{BetckeScroggs2021} together with Exafmm-t~\cite{exafmm-t}.
+FEniCSx is the successor of the widely used FEniCS finite element library\cite{FEniCS, FEniCS-book}.
 It provides a convenient Python interface, describing problems using Unified Form Language (UFL)~\cite{UFL}, a convenient domain-specific language specifically designed for finite element discretisations of partial differential equations.
@@
 In the solvent region, we used the permittivity of water ($\epsilon_2=80$) and an inverse of the Debye length of $\kappa=0.125\,\text{\AA}^{-1}$.
-In this case, there is a known analytical solution for $\phi_c$ in Eq.~\eqref{eq:phic}, so it is enough to compute $\phi_r$.
+In this case, there is a known analytic solution for $\phi_c$ in Eq.~\eqref{eq:phic}, so it is enough to compute $\phi_r$.
 We do this using Eq.~\eqref{eq:phi_reac} with both BEM-BEM and FEM-BEM coupling approaches.
@@
 In this case, we considered a spherical cavity of radius $R=2\,\text{\AA}$, with three charges ($q_1=1$, $q_2=1$, and $q_3=0.75$) placed at $\mathbf{x}_1=(1,0,0)$, $\mathbf{x}_2=(0.7,0.7,0)$, and $\mathbf{x}_3=(-0.5,-0.5,0)$.
-Figure \ref{fig:error_sphere} shows the percentage error of the FEM-BEM approach, and a reference BEM-BEM implementation, compared to the analytical solution ($\Delta G_{\text{solv}}= -336.0396\,\text{kcal/mol}$).
+Figure \ref{fig:error_sphere} shows the percentage error of the FEM-BEM approach, and a reference BEM-BEM implementation, compared to the analytic solution ($\Delta G_{\text{solv}}= -336.0396\,\text{kcal/mol}$).
 In these runs, the FEM mesh was generated using GMSH~\cite{geuzaine2009gmsh} 
@@
 However, if we look at the total time that solvers take to obtain the solution, we can see the advantage of using the FEM-BEM coupling.
-The higher computational cost is caused by the need to use a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method ($ie.$ FMM).
+The higher computational cost is caused by the need to use a hypersingular operator in the BEM formulation, and the fact that we are not using any acceleration method (i.e.
+FMM).
 The timings for the FEM-BEM coupling scale are at a greater rate than the pure BEM counterpart, indicating that work on preconditioners and other acceleration methods will be required in order to make
@@
 
-\subsection*{\sffamily \large Note on modeling differences between finite difference and finite/boundary element methods}
+\subsection*{\sffamily \large Note on modelling differences between finite difference and finite/boundary element methods}
 
 To facilitate verification, we conducted a comparative analysis between our FEM-BEM approach and established Poisson-Boltzmann solvers, including APBS,\cite{BakerETal2001} MIBPB,\cite{geng2007treatment,chen2011mibpb} CPB,\cite{boschitsch2011fast} PBSA,\cite{wang2008poisson,cai2010performance} and Delphi.\cite{rocchia2001extending}
-These benchmarks primarily employ finite difference approximations, setting the stage for inherent modeling disparities with respect to our FEM-BEM method, and making this comparison a difficult task.
+These benchmarks primarily employ finite difference approximations, setting the stage for inherent modelling disparities with respect to our FEM-BEM method, and making this comparison a difficult task.
 Firstly, the boundary integral formulation in the external domain naturally enforces the decay of the electrostatic potential to zero at infinity, while finite difference-based solvers necessitate the imposition of effective boundary conditions along the mesh periphery.
 This boundary condition critically influences the electrostatic potential and may deviate from the true solution if the size of the mesh box is insufficient. 
-Secondly, the definition of the molecular surface differs slightly across software, resulting in different domain geomteries. 
+Secondly, the definition of the molecular surface differs slightly across software, resulting in different domain geometries. 
 Our FEM-BEM approach employs a triangulation of the solvent-excluded surface (based on NanoShaper\cite{decherchi2013general}), while finite difference meshes produce a staircase representation of this surface.
@@
 In the FEM formalism, we had to detect the elements contained by cavities and use a piece-wise constant varying description of the permittivity inside the molecular region, which can be done without any modification in the formulation.
-A BEM-BEM formulation can also account for cavities this way,\cite{AltmanBardhanWhiteTidor09,CooperBardhanBarba2014} but involves certain adjustments in the stiffness matrix.
+A BEM-BEM formulation can also account for cavities this way,\cite{AltmanBardhanWhiteTidor09, CooperBardhanBarba2014} but involves certain adjustments in the stiffness matrix.
 
@@
 
-As $\epsilon$ is variable, Equation \eqref{eq:phic} does not have a known analytical solution, and the electrostatic potential in the vacuum state has to be computed numerically.
+As $\epsilon$ is variable, Equation \eqref{eq:phic} does not have a known analytic solution, and the electrostatic potential in the vacuum state has to be computed numerically.
 For vacuum calculations, we considered the same distribution of $\epsilon$ inside the molecule as in the solvated case, but the solvent permittivity was set to $\epsilon_2=2$. 
@@
 We can see that they are both converging to equivalent values, where the solutions on the finest meshes agree to within 0.5\% (0.5 kcal/mol).
-The coarsest meshes used in both cases are within the recommended densities for accurate solvation energy simulations with constant permittivity: a finite difference mesh with $h=0.5\,\text{\AA}$ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of subtracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per $\text{\AA}^2$ gives acceptable results when computing binding and solvation energies.
+The coarsest meshes used in both cases are within the recommended densities for accurate solvation energy simulations with constant permittivity: a finite difference meshes with $h=0.5\,\text{\AA}$ or less is recommended for binding energy calculations\cite{sorensen2015comprehensive} (the result of subtracting two solvation energies), and a similar study with BEM\cite{CooperBardhanBarba2014} showed that a mesh with 2 vertices per $\text{\AA}^2$ gives acceptable results when computing binding and solvation energies.
 We see a jump in the solvation energy for the FEM-BEM results going from 4.1 to 6.7 vertices per $\text{\AA}^2$, but later the energy monotonically decreases, converging to a solution.
@@
 
-Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up 30\% of the available RAM memory.
+Even though this scheme is capable of calculating the electrostatic potential in medium-to-large proteins, the largest test case in Table \ref{table:large_variable} (1igt) used up 30\% of the available RAM.
 %(\textcolor{red}{check and rewrite \textcolor{blue}{we are using around 50\% of memory}}). 
 If we were aiming at larger structures, such as full viruses,\cite{MartinezETal2019,wang2021high} we would require the use of optimised fast algorithms\cite{wang2021exafmm,kailasa2023pyexafmm} and
-parellelization of the storage and solver, alongside the necessary improvements in the conditioning of the system.
+parallelisation of the storage and solver, alongside the necessary improvements in the conditioning of the system.
 

### 2023-09-16 reply_to_referees.txt
added reply to referees file

Reviewer: 1

Preamble: 
As the authors have noted, the solution of the Poisson–Boltzmann (PB) model is a long-standing problem. There are three major approaches in the field: the finite difference method (FDM), the finite element method (FEM), and the boundary element method (BEM). It is well-known that each approach has its own advantages and disadvantages. In addition to the efforts made by the computational biophysical community, mathematicians have also developed numerous methods, often emphasizing convergent orders, even when dealing with poorly defined protein surfaces as characterized by the solvent excluded surface (SES) model.

The authors propose a combination of FEM and BEM (FEM-BEM) to leverage the advantages of both methods. This approach shows promise and could be valuable if a robust software package is developed. However, significant changes are required for this work to meet the standard in the field. My concerns are outlined below.

Reply:
We thank this reviewer for the careful revision. We are glad to see that this reviewer appreciates the potential of our work, and we hope that the substantial changes of this new version satisfy his/her concerns.

Comment 1: 
A comparison of the Kirkwood sphere can be found in the following reference: 'Treatment of charge singularities in implicit solvent models', The Journal of Chemical Physics, 127, 114106, 2007. In this work, four different cases were studied, involving up to six charges, and convergence orders were reported almost 20 years ago.

Reply:
As the reviewer points out, in that reference there is a comparison with the Kirkwood sphere for various charge distributions (with up to 6 charges). In the original version of the manuscript we also included this test case, however, considering four rather than six charges. In this test case, one of the charges was placed 1 Å away from the surface, which, according to that same reference, is a challenging setup, and showed the correct order of convergence. We don't think that performing a study similar to the cited paper would add more information to the reader.

However, we thank the reviewer for pointing us to this reference, and we apologize for missing it in the original manuscript. We have added it in the new version.

Modifications:
None required

Comment 2:
APBS is indeed a widely used Poisson-Boltzmann (PB) model. However, it is worth noting that APBS is designed for first-order convergence, which can be affected by surface irregularities in the solvent-excluded surface (SES) model for biomolecules. Therefore, a direct comparison with APBS may not be sufficient to establish the superiority of the proposed method.

Reply:
As the reviewer points out, APBS converges as first order. Even though this is not the fastest converging method, compared to, for example, MIBPB's second order convergence, it does converge to the correct solution. The goal of the result highlighted by the reviewer was to ensure that our code converged to that same answer, and thus verify code correctness. However, we do agree with the reviewer that comparison with APBS only may not be enough evidence to make our point compelling. This is why we added results showing a thorough comparison of binding energy calculations with several well-established Poisson-Boltzmann codes.

Modifications:
We added extensive tests of binding energy calculations, and compared them to several well-established codes.

Comment 3:
Furthermore, the comparison conducted in the study involved only four proteins, which might not provide a comprehensive evaluation. It would be beneficial for the authors to extend their comparison to include a larger dataset. In this regard, I suggest the authors consider comparing their FEM-BEM method with an older MIBPB method, as mentioned in the above-mentioned reference. This previous work utilized 24 proteins, and analytical solutions were generated for the protein surfaces using a standard mathematical approach. By including a larger protein dataset and considering the comparison with an older MIBPB method, the authors can enhance the robustness and validity of their study.

Examining the consistency over different mesh sizes is also a standard approach in the field. For many poorly designed methods, this poses a severe challenge, and many researchers simply refuse to engage in this pursuit, ultimately making no progress in solving the PB problem despite years of struggle. I suggest the authors examine the proposed FEM-BEM method using a set of 153 biomolecules, as was done in the study titled 'Accurate, Robust, and Reliable Calculations of Poisson-Boltzmann Binding Energies' published in the Journal of Computational Chemistry, 2017, 38, 941–948. In fact, Fenley and coworkers initially proposed this challenge. It is interesting for the authors to compare the performance of their method with that of the aforementioned JCC paper.

Reply:
We thank the reviewer for this comment, and his/her concern to enhance the robustness of our work. As suggested by the reviewer, we examined the JCC paper, and went on to perform the calculations for the 153 structures, with the corresponding binding energy results. Biding energies are extremely challenging, as they are small differences between much larger solvation energies, making accuracy key. Inspired by a previous result reported the original manuscript,we chose a mesh refinement with low enough error in the solvation energy to perform the binding energy calculations on the data set. We extracted the results from the JCC paper suggested by the reviewer, and a previous JCTC paper by Harris, Boschitsch, and Fenley (9, 3677, 2013) that runs the same data set, to compare our results against APBS, MIBPB, CPB, PBSA, and Delphi. We saw that in all cases our results where within the range of the other software, evidencing code correctness.

Modifications:
We added extensive tests of binding energy calculations, and compared them to several well-established codes.

Reviewer: 2

Preamble:
This paper presents a novel FEM-BEM method for approximating the solution to the linearized Poisson-Boltzmann equation.  The authors provide a good overview of their methodology with useful comparisons to results obtained with the APBS software package.  The paper is a useful contribution, but should be revised before it is published.

Reply:
We truly appreciate the work by the reviewer, and are happy to see he/she considers it a useful contribution.

Comment 1:
1) It should be more clear that the methodology presented in this paper is for the linearised Poisson-Boltzmann equation (LPBE) that results from approximating sinh(x) with x.  The Poisson-Boltzmann equation (PBE) can be found in many of the cited papers, including https://doi.org/10.1073/pnas.181342398

Reply:
The reviewer is completely correct, and we apologize for not making this point clearer in the original manuscript. We have edited accordingly.

Modifications:
XXXXXXXXX

Comment 2:
2) That said, providing a fast method for solving the LPBE is still very useful for many reasons including: (a) Newton-based solvers for the PBE solve the LPBE at each step, (b) for many problems approximating sinh(x) by x does not introduce a large error.  However, the authors should still be clear that they are solving the LPBE and not the PBE, and/or they should extend the discussion/algorithm/results to include the PBE.

Reply:
Although we agree with the reviewer that we were not clear enough that the linear version was being solved and that solving the nonlinear PBE is extremely important, we believe that adding results that include the nonlinear PBE is out of scope of the current manuscript. In fact, this was the original motivation behind developing our FEM-BEM coupled approach, as BEM cannot solve the nonlinear equation, which is why we mention this in the introduction. However, in the development process we realized there are several milestones that need to be reached before coupling FEM and BEM for the nonlinear problem, and this work is a first step that will take us there. Then, this comment is pointing at future directions of development.

Modifications:
None required.

Minor comments:
3) There are numerous typos in the manuscript, many of which could have been found using a simple spellchecker.  For example "whithout", "govnerns", "heterogenous", "permitivitty", "parellelization", "recongnize", ...

4) ie. -> i.e.

5) There is no number for the Nakov Sobakinskaya, Renger, Kraus reference, which is probably the cause for the citation error for "finite element" in the introduction.

6) analytical methods -> analytic methods, analytical expression -> analytic expression, analytical solution -> analytic solution

Reply:
Thank you very much for reading our manuscript carefully. We have edited accordingly.

### 2023-09-18 reply_to_referees.txt
Update reply_to_referees.txt
Just proofreading.

@@
 We thank this reviewer for the careful revision.
-We are glad to see that this reviewer appreciates the potential of our work, and we hope that the substantial changes of this new version satisfy his/her concerns.
+We are glad to see that this reviewer appreciates the potential of our work, and we hope that the substantial changes in this new version satisfy his/her concerns.
 
@@
 Reply:
-As the reviewer points out, in that reference there is a comparison with the Kirkwood sphere for various charge distributions (with up to 6 charges).
+As the reviewer points out, in that reference, there is a comparison with the Kirkwood sphere for various charge distributions (with up to 6 charges).
 In the original version of the manuscript we also included this test case, however, considering four rather than six charges.
@@
 
-However, we thank the reviewer for pointing us to this reference, and we apologize for missing it in the original manuscript. We have added it in the new version.
+However, we thank the reviewer for pointing us to this reference, and we apologise for missing it in the original manuscript. We have added it to the new version.
 
@@
 As the reviewer points out, APBS converges as first order.
-Even though this is not the fastest converging method, compared to, for example, MIBPB's second order convergence, it does converge to the correct solution.
+Even though this is not the fastest converging method, compared to, for example, MIBPB's second-order convergence, it does converge to the correct solution.
 The goal of the result highlighted by the reviewer was to ensure that our code converged to that same answer, and thus verify code correctness.
@@
 Modifications:
-We added extensive tests of binding energy calculations, and compared them to several well-established codes.
+We added extensive tests of binding energy calculations and compared them to several well-established codes.
 
@@
 We thank the reviewer for this comment, and his/her concern to enhance the robustness of our work.
-As suggested by the reviewer, we examined the JCC paper, and went on to perform the calculations for the 153 structures, with the corresponding binding energy results.
-Biding energies are extremely challenging, as they are small differences between much larger solvation energies, making accuracy key.
-Inspired by a previous result reported the original manuscript,we chose a mesh refinement with low enough error in the solvation energy to perform the binding energy calculations on the data set.
+As suggested by the reviewer, we examined the JCC paper and went on to perform the calculations for the 153 structures, with the corresponding binding energy results.
+Biding energies are extremely challenging, as there are small differences between much larger solvation energies, making accuracy key.
+Inspired by a previous result reported in the original manuscript, we chose a mesh refinement with low enough error in the solvation energy to perform the binding energy calculations on the data set.
 We extracted the results from the JCC paper suggested by the reviewer, and a previous JCTC paper by Harris, Boschitsch, and Fenley (9, 3677, 2013) that runs the same data set, to compare our results against APBS, MIBPB, CPB, PBSA, and Delphi.
-We saw that in all cases our results where within the range of the other software, evidencing code correctness.
+We saw that in all cases our results were within the range of the other software, evidencing code correctness.
 
 Modifications:
-We added extensive tests of binding energy calculations, and compared them to several well-established codes.
+We added extensive tests of binding energy calculations and compared them to several well-established codes.
 
@@
 Reply:
-We truly appreciate the work by the reviewer, and are happy to see he/she considers it a useful contribution.
+We truly appreciate the work of the reviewer and are happy to see he/she considers it a useful contribution.
 
@@
 Reply:
-The reviewer is completely correct, and we apologize for not making this point clearer in the original manuscript. We have edited accordingly.
+The reviewer is completely correct, and we apologise for not making this point clearer in the original manuscript. We have edited it accordingly.
 
@@
 Reply:
-Although we agree with the reviewer that we were not clear enough that the linear version was being solved and that solving the nonlinear PBE is extremely important, we believe that adding results that include the nonlinear PBE is out of scope of the current manuscript.
+Although we agree with the reviewer that we were not clear enough that the linear version was being solved and that solving the nonlinear PBE is extremely important, we believe that adding results that include the nonlinear PBE is out of the scope of the current manuscript.
 In fact, this was the original motivation behind developing our FEM-BEM coupled approach, as BEM cannot solve the nonlinear equation, which is why we mention this in the introduction.
-However, in the development process we realized there are several milestones that need to be reached before coupling FEM and BEM for the nonlinear problem, and this work is a first step that will take us there.
-Then, this comment is pointing at future directions of development.
+However, in the development process, we realised there are several milestones that need to be reached before coupling FEM and BEM for the nonlinear problem, and this work is the first step that will take us there.
+Then, this comment points to future directions of development.
 
@@
 Reply:
-Thank you very much for reading our manuscript carefully. We have edited accordingly.
+Thank you very much for reading our manuscript carefully. We have edited it accordingly.

### 2023-09-19 reply_to_referees.txt
Linear PBE - comment
Changes to clarify that we consider linearised version of PBE.

@@
 Modifications:
-XXXXXXXXX
+We have added linearised phrase in the abstract, a sentence in 'We are proposing a coupling scheme for the linear Poisson-Boltzmann equation.' in the introduction and a sentence ' The linearised Poisson-Boltzmann equation that results from approximating $\sinh(x)$ with $x$ follows' in the methodology to clarify the equation considered.
 

### 2023-09-19 main.tex
Linear PBE - comment
Changes to clarify that we consider linearised version of PBE.

@@
 However, the boundary element method is limited to linear equations and piecewise constant variations of the material properties.
-In this work, we present a scheme that couples finite and boundary elements for the Poisson--Boltzmann equation, where the finite element method is applied in a confined {\it solute} region and the boundary element method in the external {\it solvent} region.
+In this work, we present a scheme that couples finite and boundary elements for the linearised Poisson--Boltzmann equation, where the finite element method is applied in a confined {\it solute} region and the boundary element method in the external {\it solvent} region.
 As a proof-of-concept exercise, we use the simplest methods available: Johnson--N\'ed\'elec coupling with mass matrix and diagonal preconditioning, implemented using the Bempp-cl and FEniCSx libraries via their Python interfaces.

### 2023-09-19 methods.tex
Linear PBE - comment
Changes to clarify that we consider linearised version of PBE.

@@
 These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous across the surface.
+The linearised Poisson-Boltzmann equation that results from approximating $\sinh(x)$ with $x$ follows
 %
@@
 
-The boundary element method (BEM) is a standard tool for the numerical solution of the Poisson--Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl\cite{search2022towards}.
+The boundary element method (BEM) is a standard tool for the numerical solution of the linear version of the Poisson--Boltzmann equation in molecular electrostatics.~\cite{ZauharMorgan1985, Shaw1985} This was implemented in numerous codes, such as AFMPB,~\cite{LuETal2006} TABI,~\cite{GengKrasny2013} PyGBe,~\cite{CooperBardhanBarba2014,cooper2016pygbe} and more recently, with Bempp-cl\cite{search2022towards}.
 One strong advantage of BEM is that it reduces the dimension of the problem by using the boundary integral formulation.

### 2023-09-20 reply_to_referees.txt
small edits

@@
 Reply:
-As the reviewer points out, in that reference, there is a comparison with the Kirkwood sphere for various charge distributions (with up to 6 charges).
+As the reviewer points out, in that reference there is a comparison with the Kirkwood sphere for various charge distributions (with up to 6 charges).
 In the original version of the manuscript we also included this test case, however, considering four rather than six charges.
@@
 
-However, we thank the reviewer for pointing us to this reference, and we apologise for missing it in the original manuscript. We have added it to the new version.
+However, we thank the reviewer for pointing us to this reference, and we apologize for missing it in the original manuscript. We have added it to the new version.
 
@@
 
+We would like to note that some of the 153 structures of the data set had cavities where water molecules can fit.
+In a finite difference description, these regions are naturally considered as having the bulk water permittivity.
+Then, we had to consider them accordingly to make an appropriate comparison with the other codes.
+This meant that we had a variable permittivity inside the molecular region, which is one of the motivations behind this work, making our point of using FEM in the molecule more compelling.
+
 Modifications:
@@
 Reply:
-The reviewer is completely correct, and we apologise for not making this point clearer in the original manuscript. We have edited it accordingly.
+The reviewer is completely correct, and we apologize for not making this point clearer in the original manuscript. We have edited it accordingly.
 
@@
 In fact, this was the original motivation behind developing our FEM-BEM coupled approach, as BEM cannot solve the nonlinear equation, which is why we mention this in the introduction.
-However, in the development process, we realised there are several milestones that need to be reached before coupling FEM and BEM for the nonlinear problem, and this work is the first step that will take us there.
+However, in the development process, we realied there are several milestones that need to be reached before coupling FEM and BEM for the nonlinear problem, and this work is the first step that will take us there.
 Then, this comment points to future directions of development.

### 2023-09-20 intro.tex
Linear PBE - comment
Changes to clarify that we consider linearised version of PBE.
small edits

@@
 the size-modified PBE).
-To the best of our knowledge, this is the first time finite and boundary elements have been combined in this application.
+To the best of our knowledge, this is the first time finite and boundary elements have been combined in this application. We are proposing a coupling scheme for the linear Poisson-Boltzmann equation.
 
-In this paper, we prototype this principle with the simplest implementation possible: a Johnson--N\'ed\'elec\cite{johnson1980coupling} coupling, where we solve using mass-matrix and diagonal preconditioning and without distributed memory execution.
+In this paper, we prototype this principle with the simplest implementation possible: a Johnson--N\'ed\'elec\cite{johnson1980coupling} coupling, where we solve using mass-matrix and diagonal preconditioning, and without distributed memory execution.
 This limits the size of problems we can access currently, however, it sets the basis for future developments that use more elaborate formulations and algorithms that are readily available in open-source software libraries.

### 2023-09-20 main.tex
small edits

@@
 EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1. \\
-CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
+CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004 and Universidad T\'ecnica Federico Santa Mar\'ia through Proyectos Internos USM 2023 PI-LIR-23-03.\\
 We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.

### 2023-09-20 methods.tex
small edits

@@
 
-A common quantity of interest in implicit solvent models is the solvation free energy, which is the change in Gibbs free energy as the molecule moves from the vacuum into the solvent.
+A common quantity of interest in implicit solvent models is the polar component of the solvation free energy, which is the change in Gibbs free energy as the molecule charges move from vacuum into a solute-shaped cavity inside the solvent.
 Considering the charge distribution $\rho$ consists of point charges, this can be calculated as
@@
 \end{align}
-where $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Dirichlet trace),
-and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it ie.} the exterior Neumann trace).
+where $\phi_2 = \phi_2(\mathbf{x}_\Gamma)$ is the potential on $\Gamma$ as we approach from $\Omega_2$ ({\it i.e.} the exterior Dirichlet trace),
+and $\lambda_2 = \frac{\partial}{\partial \mathbf{n}}\phi_2$ is the normal derivative $\Gamma$ as we approach from $\Omega_2$ ({\it i.e.} the exterior Neumann trace).
 Note that we can obtain $\phi_1$ and $\lambda_1$ from $\phi_2$ and $\lambda_2$ by applying the interface conditions \eqref{eq:pbe3} and \eqref{eq:pbe4}.
-The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
+The operators $V$, $K$, $K^{\prime}$, and $W$ that appear in Equation \eqref{eq:lu} are the single-layer, double-layer, adjoint double-layer, and hypersingular operators, respectively, for the Laplace (subscript $L$) and Yukawa (subscript $Y$, also known as modified Helmholtz) kernels.
 These are defined %in Equation~\eqref{eq:single_double} and
@@
 Unfortunately, this advantage comes at a cost: it requires a fundamental solution to be known in order for the method to be applied.
-There are many linear problems for which fundamental solutions are not known: this is the case for the Poisson-Boltzmann equation with a heterogenous permittivity inside the molecule, \emph{ie}.
+There are many linear problems for which fundamental solutions are not known: this is the case for the Poisson-Boltzmann equation with a heterogeneous permittivity inside the molecule, \emph{i.e.}
 %

### 2023-09-20 results.tex
small edits

@@
-This section presents the verification and performance results of the presented FEM-BEM coupling schemes for molecules modelled as cavities with constant and varying permittivity.
+This section presents the verification and performance results of the presented FEM-BEM coupling scheme for molecules modelled as cavities with constant and varying permittivity.
 With a constant permittivity inside the molecule, we tested convergence against an analytic expression of the solvation energy of a sphere \cite{Kirkwood1934}, and then compared a more realistic geometry (arginine) with a purely BEM implementation.
+Then, as a more challenging test, we performed binding energy calculations from a set of 153 structures,\cite{HarrisBoschitcshFenley2013} and compared them to well-established codes. 
 We also considered a Gaussian-varying permittivity\cite{grant2001smooth,li2013dielectric} inside the molecular cavity of arginine, and used APBS \cite{BakerETal2001} to verify our results.

### 2023-09-20 methods.tex
flipped names of equations in methods

@@
 
-The implicit solvent model\cite{RouxSimonson1999, DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson--Boltzmann equation governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson equation governs in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}).
+The implicit solvent model\cite{RouxSimonson1999, DecherchiETal2015} can be described mathematically as a coupled system of partial differential equations, where the Poisson equation governs in the solvent region ($\Omega_1$ in Figure \ref{fig:implicit_molecule}), and the Poisson--Boltzmann equation governs in the solute region ($\Omega_2$ in Figure \ref{fig:implicit_molecule}).
 These regions are interfaced by the molecular surface ($\Gamma$), where the potential ($\phi$) and electric displacement ($\epsilon\partial\phi/\partial\mathbf{n}$) are continuous across the surface.

### 2023-09-21 intro.tex
added citations to Stamm and a couple of sentences in results

@@
 
-The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010,nakov2021argos}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytic\cite{YapHeadgordon2010,FelbergETal2017} methods.
+The PBE has been solved numerically with finite difference\cite{BakerETal2001,GilsonETal1985,JurrusETal2018,LiETal2019}, finite element\cite{HolstETal2012,BondEtal2010,nakov2021argos}, boundary element\cite{boschitsch2002fast,LuETal2006,AltmanBardhanWhiteTidor09,bajaj2011efficient,GengKrasny2013,CooperBardhanBarba2014}, and analytic\cite{YapHeadgordon2010,FelbergETal2017,quan2019domain,siryk2022arbitrary,jha2023domain} methods.
 In particular, the boundary element method (BEM) has proven to be very efficient for high-accuracy calculations \cite{GengKrasny2013,CooperBardhanBarba2014}, mainly due to the precise description of the molecular surface and point charges.

### 2023-09-21 results.tex
added citations to Stamm and a couple of sentences in results

@@
 Following the data set proposed by Fenley and co-workers,\cite{HarrisBoschitcshFenley2013} available in \url{http://www.sb.fsu.edu/~mfenley/convergence/downloads/convergence_pqr_sets.tar.gz}, and later used by Wei {\it et al.}\cite{nguyen2017accurate} to assess the accuracy of different Poisson-Boltzmann solvers, we tested our method by computing binding energies.
-This data set consists of three families of structures: DNA-drug complexes, different versions of the barnase-barstar complex, and RNA-peptide complexes.
+This data set consists of 51 complexes, totalling 153 structures, separated in three families: DNA-drug complexes, different versions of the barnase-barstar complex, and RNA-peptide complexes.
 Following the problem setting for these data sets, we use $\epsilon_1=1$, $\epsilon_2=80$ and an inverse of the Debye length of $\kappa=0.10265\,\text{\AA}^{-1}$.
@@
 In the FEM formalism, we had to detect the elements contained by cavities and use a piece-wise constant varying description of the permittivity inside the molecular region, which can be done without any modification in the formulation.
-A BEM-BEM formulation can also account for cavities this way,\cite{AltmanBardhanWhiteTidor09, CooperBardhanBarba2014} but involves certain adjustments in the stiffness matrix.
+A BEM-BEM formulation can also account for cavities as regions with water's bulk permittivity,\cite{AltmanBardhanWhiteTidor09, CooperBardhanBarba2014} but involves certain adjustments in the stiffness matrix.
 
 Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} show the binding energies of structures of DNA-drug complexes, barnase-barstar complexes, and RNA-peptide complexes, respectively, presented in Fenley's data set.\cite{HarrisBoschitcshFenley2013} The data for CPB\cite{HarrisBoschitcshFenley2013} and MIBPB, Delphi, APBS and PBSA were taken from the literature,\cite{nguyen2017accurate} for the finest mesh reported.
-From Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} it is evident that our FEM-BEM approach gives results that are within the range of the other software.
+From Figures \ref{fig:dna_drug}, \ref{fig:barnase_barstar}, and \ref{fig:rna_peptide} it is evident that our FEM-BEM approach gives results that are within the range of the difference between other software for all 51 complexes.
+Given the challenging nature of binding energy calculations, and that our results are consistently comparable to other widely-trusted solvers that use a different numerical scheme for all 51 complexes, we can positively conclude on the correctness of our code.
 
